### 2018-07-02 Paper/mnras_template.tex
asd

% mnras_template.tex
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[a4paper,fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{subfig}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Title]{The expected shape of the Milky Way's Dark Matter halo}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[Jesus Prada,  Jaime E. Forero-Romero, Volker Springel ]{
Jesus Prada,$^{1}$\thanks{E-mail: jd.prada1760@uniandes.edu.co}
Jaime E. Forero-Romero,$^{1}$
Volker Springel$^{2}$
\\
% List of institutions
$^{1}$Departamento de Física, Universidad de los Andes, Cra. 1 No.
18A-10, Edificio Ip, Bogotá, Colombia.\\
$^{2}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg
Germany.\\
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2018}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
keyword1 -- keyword2 -- keyword3
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction}

This is a simple template for authors to write new MNRAS papers.
See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
for a full user guide.

All papers should start with an Introduction section, which sets the work
in context, cites relevant earlier studies in the field by \citet{Others2013},
and describes the problem the authors aim to solve \citep[e.g.][]{Author2012}.

\section{Numerical Simulations}
Auriga simulations.

\section{Determining the halo shape}

%\subsection{The solid ellipsoid method}

\section{Results}
Here we present our principal results blah blah blah.

\subsection{The radial tendency of axial ratios}
First, it is important to verify that halos are rounder at larger radii, for both MHD and DM simulations.

\begin{figure}
  \centering
  \subfloat[halo 27 DM shape at small radius]{\includegraphics[width=0.5\columnwidth]{./pics/MHD_Vs_DM/level4_DM_halo_27_inner.png}}
  \hfill
  \subfloat[halo 27 DM shape at big radius]{\includegraphics[width=0.5\columnwidth]{./pics/MHD_Vs_DM/level4_DM_halo_27_outter.png}}
  \hfill
  \subfloat[halo 27 MHD shape at small radius]{\includegraphics[width=0.5\columnwidth]{./pics/MHD_Vs_DM/level4_MHD_halo_27_inner.png}}
  \hfill
  \subfloat[halo 27 MHD shape at big radius]{\includegraphics[width=0.5\columnwidth]{./pics/MHD_Vs_DM/level4_MHD_halo_27_outter.png}}
  \caption{DM density for inner (left) and outer (right) parts of the halo 27. We present both versions of the halo: DM (up) \& MHD (down). The horizontal (vertical) axes are aligned to the major (medium) axes. (optimaze space and description) }
  \label{fig:slices}
\end{figure}

\begin{figure}
\centering
\subfloat[halo 16]{\includegraphics[width=0.5\columnwidth]{./pics/halo16.png}}
  \hfill
  \subfloat[halo 27]{\includegraphics[width=0.5\columnwidth]{./pics/halo27.png}}
\caption{Radial profile for axial ratios and the triaxiality parameter $T=\frac{1-b/a}{1-c/a}$ from halo 27 and halo 16. These halos have a clear radial tendence towards sphericity (for smaller radii until $\approx 3$Kpc), which can be confirmed with the triaxiality parameter. (Merged Column)}
\label{fig:DM_MHD}
\end{figure}

\begin{figure}
  \centering
  \subfloat[Level4 DM inner Vs outer regions]{\includegraphics[width=0.5\columnwidth]{./pics/Triaxial_Plane/Triaxiality_DM_lvl4.png}}
  \hfill
  \subfloat[Level4 MHD inner Vs outer regions]{\includegraphics[width=0.5\columnwidth]{./pics/Triaxial_Plane/Triaxiality_MHD_lvl4.png}}
  \hfill
  \caption{General tendency on the triaxial plane $c/a$ Vs $b/a$. Some observational constraints are plotted alongside our results (Optimize space. caption replaces title.  Present constraints representation of density)}
  \label{fig:Triaxiality_DM_MHD}
\end{figure}

\subsection{The rounding effect of baryons}
Here we discuss the rounding effect of baryons. We quantify this rounding effect and look for correlations with important baryonic properties of the galaxy.

\begin{figure}
  \centering
  \subfloat[Level4 MHD Vs DM at inner regions]{\includegraphics[width=0.5\columnwidth]{./pics/Triaxial_Plane/Triaxiality_Inner_lvl4.png}}
  \hfill
  \subfloat[Level4 MHD Vs DM at outer regions]{\includegraphics[width=0.5\columnwidth]{./pics/Triaxial_Plane/Triaxiality_Outter_lvl4.png}}
  \hfill
  \caption{Axial ratios as shown on $c/a$ Vs $b/a$. Each dot represents a halo shape at some radius. Some observational constraints are plotted alongside our results. Here, dots are clustered, proving the general tendence of halos to get rounder on the outer parts.(Optimize space. caption replaces title.  Present constraints representation of density)}
  \label{fig:Triaxiality_Inner_Outer}
\end{figure}

\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{./pics/Delta asphericity Vs Star Density.png}
    \caption{Difference in asphericities between MHD and DM shapes Vs Star Density of the simulation.}
    \label{fig:Star_Density_effect}
\end{figure}

\subsection{The historical shape}
Here we study the memory shape and how it can be deduced from the historic radial shapes. Also why it is lost for MHD even when radial profiles have the same historic tendencies.

\begin{figure}
  \centering
  \subfloat[halo 16 DM]{\includegraphics[width=0.5\columnwidth]{./pics/Redshift/halo_16_level3_DM_Z.png}}
  \hfill
  \subfloat[halo 16 MHD]{\includegraphics[width=0.5\columnwidth]{./pics/Redshift/halo_16_level3_MHD_Z.png}}
  \caption{Radial profile (comoving) of axial ratios for halo 16 in terms of redshift (color). This halo maintains its shape until $z\approx 1$ obviating the systematic rounding effect in time from asymmetric potentials. }
  \label{fig:RedshiftGood}
\end{figure}

\subsection{The orientation of the principa axes}
This is an important result of our study. We study the radial evolution of the principal axes, compared also to the angular momentum vector from the disk. We found that while the angular momentum tend to be aligned with the minor axis of the ellipsoid, this may not be the case all times. When there is an alignment it is usually within 20 degrees. When there is not an alignment, then there is no simple way to determine toward which axis it is oriented. Furthermore, the principal axes alignment usually change with radius (rotation, swap). This really questions the strong constrains on the MW DM halo models.

\section{Conclusions}

The last numbered section should briefly summarise what has been done, and describe
the final conclusions which the authors draw from their work.

\section{Discussion}

\section*{Acknowledgements}

The Acknowledgements section is not numbered. Here you can thank helpful
colleagues, acknowledge funding agencies, telescopes and facilities used etc.
Try to keep it short.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

%\bibliographystyle{mnras}
%\bibliography{example} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references
\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
Others S., 2012, Journal of Interesting Stuff, 17, 198
\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Some extra material}

If you want to present additional material which would interrupt the flow of the main paper,
it can be placed in an Appendix which appears after the list of references.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

### 2018-07-02 Code/Convergence_Analysis.py

@@ -79,7 +79,7 @@ with PdfPages("../Plots/Convergence_lvl34_"+sys.argv[1]+".pdf") as pdf:
 
         # Graphics
         ylabel = ['b/a','c/a','c/b']
-        fig, axs = plt.subplots(figsize=(10,10),nrows=len(yvals3))
+        fig, axs = plt.subplots(figsize=(10,15),nrows=len(yvals3))
         for ax,yval3,yval4,ylab,delta,indi in zip(axs,yvals3,yvals4,ylabel,diff.T,range(3)):
             
             yrand = []
@@ -162,7 +162,7 @@ with PdfPages("../Plots/Convergence_lvl34_"+sys.argv[1]+".pdf") as pdf:
         axs[-1].yaxis.set_major_formatter(FormatStrFormatter('%.1f'))
         plt.setp( axs[-1].get_xticklabels(), visible=True)                
         axs[0].set_title(halo)        
-        pdf.savefig(fig)
+        pdf.savefig(fig, bbox_inches='tight')
         plt.close()
 
 

### 2018-07-02 Code/Jobs/job1.sh

@@ -12,5 +12,6 @@
 # Redshift dependence of semiaxes at virial radius (each redshift)
 source /home/pradajs/Heidelberg/HITS_Project/Code/Jobs/bashrc
 #python ./Z_axes.py level3_MHD 63
-python get_Axes.py level3_MHD 6
+python Z_axes.py level3_MHD 63
+python Z_axes.py level3_DM 127
 

### 2018-07-02 Code/Py_Libs/plots.py

@@ -1,92 +1,0 @@
-import matplotlib
-matplotlib.use('Agg')
-
-from arepo import *
-from shape import loadSim
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib.ticker import FormatStrFormatter
-
-from matplotlib.backends.backend_pdf import PdfPages
-import matplotlib.pyplot as plt
-
-def fun1():
-    lvlDM,lvlMHD = 'level4_DM','level4_MHD'
-    lvl = 'level4_MHD'
-    with PdfPages('../Plots/'+lvl+'/AxialRatios.pdf') as pdf:
-        #arr = [1,2,3,4,5,7,8,10]
-        arr = range(1,31)
-        for j in arr:
-            halo = 'halo_'+str(j)
-            print(halo)
-            path = "../Plots/"+lvl+"/"+halo+"/"+"abc_"+lvl+"_"+halo+".txt"
-            a,b,c = np.loadtxt(path,delimiter = ',').T
-            snapnum = 127
-            pos,rvir = loadSim(lvl,halo,snapnum)
-            fig, ax1= plt.subplots(nrows=1, figsize=(15,7))
-            yvals = np.array([b/a,c/a,c/b,(a**2-b**2)/(a**2-c**2)])
-            ylabel = ['b/a','c/a','c/b','T']
-            xvals = (a*b*c)**(1./3.)
-            marks = ['-','-','-','--']
-            #colors = ['r','g','b']
-            for y,ylab,mark in zip(yvals,ylabel,marks):
-                ax1.plot(xvals,y,mark,label =ylab )
-            ax1.plot([rvir,rvir],[0,1])
-            ax1.set_xscale('log')
-            # Plotting ratios
-            ax1.set_ylim(0,1.01)
-            # Valid for all Milkyway-like galaxies
-            ax1.set_xlim(0.1,2*rvir)
-            ax1.xaxis.set_major_formatter(FormatStrFormatter('%.1f'))
-            ax1.set_xlabel("log(R(kpc/h))")
-            ax1.legend()
-            ax1.set_title(halo)
-            pdf.savefig(fig)
-            plt.close()
-
-
-def fun2():
-    lvlDM,lvlMHD = 'level4_DM','level4_MHD'
-    print(lvlDM,lvlMHD)
-    # lvl = 'level4_MHD'
-    with PdfPages('../Plots/lvl4_DM_MHD_Comp.pdf') as pdf:
-        #arr = [1,2,3,4,5,7,8,10]
[…]

### 2018-07-02 Code/Py_Libs/shape.py

@@ -32,7 +32,7 @@ def loadSim(lvl,halo,snapnum):
 
     # Loads the simulation
     #sn = Snapshot(path+snap, parttype=[1], filter=filterr, combineFiles=True, verbose=True)
-    sn = Snapshot(path,snapnum, parttype=[1], combineFiles=True, verbose=True)
+    sn = Snapshot(path,snapnum, parttype=[1], combineFiles=True, verbose=False)
     
     # DM Mass
     DMass = sn.MassTable[1]
@@ -40,7 +40,8 @@ def loadSim(lvl,halo,snapnum):
     # r the radius of the halo (R_mean200)*1000 to obtain it in kpc
     radiii = 1000.*subSn.group.Group_R_TopHat200[0]
     rad = 1000.*subSn.group.Group_R_Crit500[0]
-    print("Rad_Crit_500 Vs Rad_Top_200: " + str(rad)+"   "+str(radiii))
+    rad2 = 1000.*subSn.group.Group_R_Crit200[0]
+    print("Rad_Crit_500 Vs Rad_Top_200 Vs Rad_Crit_200: " + str(rad)+"   "+str(radiii)+"   "+str(rad2))
     # Some galactic disk properties of the principal subhalo
     diskrads = 1000*subSn.SubhaloHalfmassRadType[0]
     
@@ -73,7 +74,7 @@ def loadSim(lvl,halo,snapnum):
     dictio['rad_bh'] = diskrads[5]
   
     
-    return pos,rad,dictio
+    return pos,rad2,dictio
 
 
 # Gets semiaxes given eigenvalues of Inertia and a radius

### 2018-07-02 Code/Triaxiality.py

@@ -177,9 +177,9 @@ plt.rc('axes', titlesize=MEDIUM_SIZE)     # fontsize of the axes title
 plt.rc('axes', labelsize=MEDIUM_SIZE)    # fontsize of the x and y labels
 plt.rc('xtick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
 plt.rc('ytick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
-plt.rc('figure', figsize=(7, 10))
+plt.rc('figure', figsize=(12, 10))
 
-plt.figure(figsize=(7, 10))
+plt.figure(figsize=(12, 10))
 # Plots axial ratios c/a Vs b/a for R = 0.01Rvir 
 plt.plot(axes1[:,1]/axes1[:,0],axes1[:,2]/axes1[:,0], marker = 's',
  c = 'r',markersize =12, alpha = 0.8, linewidth = 0, label = r"$(OUR) R_{MHD} = 0.01R_{200}$" )
@@ -215,9 +215,9 @@ plt.rc('axes', titlesize=MEDIUM_SIZE)     # fontsize of the axes title
 plt.rc('axes', labelsize=MEDIUM_SIZE)    # fontsize of the x and y labels
 plt.rc('xtick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
 plt.rc('ytick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
-plt.rc('figure', figsize=(7, 10))
+plt.rc('figure', figsize=(12, 10))
 
-plt.figure(figsize=(7, 10))
+plt.figure(figsize=(12, 10))
 # Plots axial ratios c/a Vs b/a for R = Rvir 
 plt.plot(axes2[:,1]/axes2[:,0],axes2[:,2]/axes2[:,0], marker = 's', 
  c = 'red',markersize =12, alpha = 0.8, linewidth = 0, label = r"$(OUR) R_{MHD} = R_{200}$" )
@@ -235,7 +235,7 @@ plt.xlim(-0.05,1.05)
 plt.ylim(-0.05,1.05)
 plt.xlabel("b/a")
 plt.ylabel("c/a")
-plt.title("Level 4 Innerskirts DM vs MHD")
+plt.title("Level 4 Outerskirts DM vs MHD")
 plt.legend(loc = 0)
[…]

### 2018-07-02 Code/ZTriax.py

@@ -1,140 +1,0 @@
-import matplotlib
-matplotlib.use('Agg')
-
-# Python
-from arepo import *
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib.ticker import FormatStrFormatter
-from matplotlib.backends.backend_pdf import PdfPages
-from matplotlib.ticker import FormatStrFormatter
-import matplotlib as mpl
-import matplotlib.cm as cm
-import matplotlib.colors as colors
-import os
-
-# Simiulation specs
-lvl3 = 'level3_DM'
-#lvl = 'level3_DM'
-#halonums = range(1,31)
-halonums = [6,16]
-
-# Keeps semiaxes and eigenvecs
-with PdfPages("../Plots/ZTriax_lvl3_DM.pdf") as pdf:
-
-    for j in halonums:
-    
-        # Halo name        
-        halo = "halo_"+str(j)     
-        print("------------------------------------"+halo)   
-    
-        # Paths to files
-        path = "../Plots/"+lvl3+"/"+halo
-        
-        # List of directories
-        listdir = next(os.walk(path))[1]
-        if 'rand_sample' in listdir:
-            listdir.remove('rand_sample')
-        def getkey(l):
-            return int(l.split("_")[1])
-        listdir.sort(key=getkey)
-
-        # Plots    
-        fig, axs = plt.subplots(figsize=(10,10))
-        
-        # Plots last snapshot in terms of radius
-        arr = np.loadtxt(path+"/"+"abc_"+lvl3+"_"+halo+".txt", delimiter = ",")
-        a,b,c = (arr)[:-1].T
-        xvals = (a*b*c)**(1./3.)
-        # Axial ratios and radii (including rvir)
-        a,b,c = (arr[xvals>=9])[:-1].T
-        
-        # Radius at which comparison is performed (in kpc)
-        radius = 50
-        axs.plot(b/a,c/a, color = 'black', linewidth=1, alpha = 1)
-       
-        # Color settings
-        my_norm = colors.Normalize(0,1)
-        mapa = cm.ScalarMappable(norm=my_norm, cmap='hsv')
-        
-        for direc in listdir:
-            
-            # Semiaxes
-            arr = np.loadtxt(path+"/"+direc+"/s"+direc.split("_")[1]+".txt", delimiter = ",")
-            print(direc)
-            
-            # Loads information dictionary
[…]

### 2018-07-02 Code/Z_Convergence.py

@@ -49,11 +49,11 @@ with PdfPages("../Plots/Redshift_"+lvl3+".pdf") as pdf:
             
         # Plots    
         ylabel = ['b/a','c/a','c/b']
-        fig, axs = plt.subplots(figsize=(10,10),nrows=3)
+        fig, axs = plt.subplots(figsize=(10,15),nrows=3)
        
         # Color settings
-        my_norm = colors.Normalize(0.2,1)
-        mapa = cm.ScalarMappable(norm=my_norm, cmap='hsv')
+        my_norm = colors.Normalize(0.0,0.8)
+        mapa = cm.ScalarMappable(norm=my_norm, cmap="CMRmap")
         
         for direc in listdir:
             
@@ -77,7 +77,7 @@ with PdfPages("../Plots/Redshift_"+lvl3+".pdf") as pdf:
             for ax,yval,ylab in zip(axs,yvals,ylabel):
                 
                 
-                my_col = mapa.to_rgba((1.0/(1.0+redshift)))
+                my_col = mapa.to_rgba(1.-(1.0/(1.0+redshift)))
                 if(redshift < 1e-6):
                     mappable = ax.plot(xvals,yval, color = my_col, linewidth=1, label = "Radial shape", alpha = 1,zorder=10)
                     ax.plot([rvir,rvir],[0,0.5], color = my_col, linestyle = '-.',label = r"$R_{500}$",zorder =1)
@@ -118,11 +118,11 @@ with PdfPages("../Plots/Redshift_"+lvl3+".pdf") as pdf:
         #axs[0].legend(loc='upper left', bbox_to_anchor=(1, 0.5))  
         
         xticks = [0, 0.5, 1, 2]
-        yticks = [1.0/(1.0+x) for x in xticks]
+        yticks = [1.- 1.0/(1.0+x) for x in xticks]
         
         # Colorbar ax
         cbaxes = fig.add_axes([0.95, 0.1, 0.02, 0.8]) 
-        cbar = mpl.colorbar.ColorbarBase(cbaxes, cmap = "hsv", norm = my_norm, orientation = 'vertical', ticks = yticks )  
+        cbar = mpl.colorbar.ColorbarBase(cbaxes, cmap = "CMRmap", norm = my_norm, orientation = 'vertical', ticks = yticks )  
         cbar.ax.set_yticklabels(xticks)
         cbar.set_label('$Redshift$', fontsize=30 )
 

### 2018-07-02 Code/Z_Triax.py

@@ -49,8 +49,8 @@ with PdfPages("../Plots/"+lvl+"/"+"Z_Triax_"+lvl+".pdf") as pdf:
         fig, axs = plt.subplots(figsize=(10,10))
         
         # Color settings
-        my_norm = colors.Normalize(0.2,1)
-        mapa = cm.ScalarMappable(norm=my_norm, cmap='hsv')      
+        my_norm = colors.Normalize(0.0,0.8)
+        mapa = cm.ScalarMappable(norm=my_norm, cmap='CMRmap')      
         
         for j in range(len(a)):
             
@@ -59,7 +59,7 @@ with PdfPages("../Plots/"+lvl+"/"+"Z_Triax_"+lvl+".pdf") as pdf:
                 continue
             print("Redshift: "+str(redshift[j]))
             # Plot scatter point
-            my_col = mapa.to_rgba((1.0/(1.0+redshift[j])))
+            my_col = mapa.to_rgba(1-(1.0/(1.0+redshift[j])))
             if redshift[j] < 1e-6:
             
                 axs.scatter(b[j]/a[j],c[j]/a[j], color = my_col, s=90, alpha = 1, zorder = len(a)-j,label = r"Historical shape $R_{500}$")
@@ -113,13 +113,13 @@ with PdfPages("../Plots/"+lvl+"/"+"Z_Triax_"+lvl+".pdf") as pdf:
         
         # Colorbar
         xticks = [0, 0.5, 1,2]
-        yticks = [1.0/(1.0+x) for x in xticks]
+        yticks = [1.- 1.0/(1.0+x) for x in xticks]
         
         # Colorbar ax
         cbaxes = fig.add_axes([0.95, 0.1, 0.02, 0.8]) 
         
         axs.legend(loc=0)
-        cbar = mpl.colorbar.ColorbarBase(cbaxes, cmap = "hsv", norm = my_norm, orientation = 'vertical', ticks = yticks )  
+        cbar = mpl.colorbar.ColorbarBase(cbaxes, cmap = "CMRmap", norm = my_norm, orientation = 'vertical', ticks = yticks )  
         cbar.ax.set_yticklabels(xticks)
         cbar.set_label('$Redshift$', fontsize=30 )
         

### 2018-07-02 Code/Z_axes.py

@@ -68,17 +68,17 @@ for j in halonums:
     semmiaxes = []
     axes_vecs = []
     
-    pos,rvirrr,info = loadSim(lvl,halo,63)
+    pos,rvirrr,info = loadSim(lvl,halo,int(sys.argv[2]))
     while(boole):
         
         # Loads particles positions, virial radius and other important info
         pos,rvir,info = loadSim(lvl,halo,snapnum)
         # We need the virial radius in physical coordinates
-        rvir = rvirrr*info["Scale factor"]
+        rvir = rvir#*info["Scale factor"]
         pos = np.array(pos,dtype = np.float)
         
         # Stops if 
-        if (rvir < 10) : 
+        if (info['Redshift'] > 5) : 
             boole = False
         
         #print("---------------------------------------------------------------------------------")
@@ -101,11 +101,11 @@ for j in halonums:
             inertia.get_shape(ct.c_void_p(pos.ctypes.data),ct.c_int(len(pos)), ct.c_void_p(vecs.ctypes.data), ct.c_void_p(axes.ctypes.data))
             rad = (abs(axes[0]*axes[1]*axes[2]))**(1./3.)
             # Advance
-            if axes[0] < 0:
+            if axes[0] <= 0:
                 break
             elif abs(rad-rvir)/rvir > 0.01 :
-                axes = (axes[0]+0.5*(rvir-rad))*axes/axes[0]
-		axes_vecs.append(np.copy(vecs).flatten())
+                axes = (axes[0]+1.5*(rvir-rad))*axes/axes[0]
+                axes_vecs.append(np.copy(vecs).flatten())
             else:
                 break
                 

### 2018-07-02 Code/effect_of_gas.py

@@ -16,11 +16,11 @@ import os
 
 #########################################################################################################
 
-lvl = 'level4_'# level of the simullation
-nhalos = 30 # number of halos
+#lvl = 'level4_'# level of the simullation
+#nhalos = 30 # number of halos
 
-#lvl = 'level3_'# level of the simullation
-#nhalos = 6 # number of halos
+lvl = 'level3_'# level of the simullation
+nhalos = 6 # number of halos
 
 folder = '../Plots/' # The folder containing all files
 
@@ -84,9 +84,9 @@ def main():
     axesDM = axes[1::2]
     
     # Isopotential and Isodensity axes
-    tmp,axes = read_csv(folder+fn_denaxes, skip_header = 0) # Isodensity (den)
+    tmp,axes = read_csv(folder+fn_denaxes) # Isodensity (den)
     axesDen = np.reshape(axes,(nhalos,5,3)) # contains only MHD (nhalos) axes (3) sampled at (5) radii
-    tmp,axes = read_csv(folder+fn_potaxes, skip_header = 0) # Isopotential (pot)
+    tmp,axes = read_csv(folder+fn_potaxes) # Isopotential (pot)
     axesPot = np.reshape(axes,(nhalos,5,3))
     
     #print axesMHD
@@ -119,9 +119,9 @@ def main():
     vecsDM = vecs[1::2]
     
     # Isopotential and Isodensity axes
-    tmp,vecs = read_csv(folder+fn_denvecs, skip_header = 0) #skipHeader:Little error of unified notation (no problem,to fix later)
+    tmp,vecs = read_csv(folder+fn_denvecs) 
     vecsDen = np.reshape(vecs,(nhalos,5,3,3))
-    tmp,vecs = read_csv(folder+fn_potvecs, skip_header = 0)
+    tmp,vecs = read_csv(folder+fn_potvecs)
     vecsPot = np.reshape(vecs,(nhalos,5,3,3))
 
     ####################
@@ -133,9 +133,9 @@ def main():
     
     
     import matplotlib.pyplot as plt
-    plt.plot(axesMHD[:,0,1]/axesMHD[:,0,0],axesMHD[:,0,2]/axesMHD[:,0,0], 'ro' )
[…]

### 2018-07-02 Code/format.py

@@ -22,7 +22,7 @@ import ctypes as ct
 inertia = ct.cdll.LoadLibrary('./C_Libs/inertia.so')
 
 def main():
-
+    '''
     lvl = 'level3_'
     snapnum = 63 # MHD snapshot
     snapnumDM = 127 # DM snapshot
@@ -33,7 +33,7 @@ def main():
     snapnum = 127 # MHD snapshot
     snapnumDM = 127 # DM snapshot
     halo_nums = range(1,31)
-    '''
+    
 
     # The corresponding list and their filenames
     params = []

### 2018-07-02 Code/get_info.py

@@ -1,0 +1,50 @@
+from arepo import *
+
+def loadSim(lvl,halo,snapnumDM,snapnumMHD):
+    
+    # Path of the simulation
+    pathDM = "/hits/universe/GigaGalaxy/"+lvl+"_DM"+"/"+halo+"/output" 
+    pathMHD = "/hits/universe/GigaGalaxy/"+lvl+"_MHD"+"/"+halo+"/output"
+    # Loads groups to select the principal halo
+    subSnDM = Subfind(pathDM,snapnumDM)
+    subSnMHD = Subfind(pathMHD,snapnumMHD)
+
+    # Loads the simulation
+    snDM = Snapshot(pathDM,snapnumDM, parttype=[1], combineFiles=True, verbose=False)
+    snMHD = Snapshot(pathMHD,snapnumMHD, parttype=[1], combineFiles=True, verbose=False)
+    
+    # DM Mass
+    DMassDM = snDM.MassTable[1]
+    DMassMHD = snMHD.MassTable[1]
+    
+    # r the radius of the halo (R_mean200)*1000 to obtain it in kpc
+    rvirDM = 1000.*subSnDM.group.Group_R_TopHat200[0]
+    rvirMHD = 1000.*subSnMHD.group.Group_R_TopHat200[0]
+    
+    MvirDM = 1000.*subSnDM.group.Group_M_TopHat200[0]
+    MvirMHD = 1000.*subSnMHD.group.Group_M_TopHat200[0]
+    
+    
+    # Gets the length of the main structure particles /// 0 - Principal halo, 1 - DM
+    subCutDM = subSnDM.subhalo.SubhaloLenType[0,1]
+    subCutMHD = subSnMHD.subhalo.SubhaloLenType[0,1]
+    
+    lista = [subCutDM/1e+6,subCutMHD/1e+6, DMassDM/1e-5, DMassMHD/1e-5,rvirDM,rvirMHD,MvirDM/1e+4,MvirMHD/1e+4]
+    stri = halo+"&"
+    for el in lista[:-1]:
+        stri += '{:.3f}'.format(float(el)) +"&"
+    stri += '{:.3f}'.format(float(lista[-1]))+"\\\\"    
+    
+    print stri
+
+#lvl = 'level4'
+lvl = 'level3'
+
+for i in [6,16,21,23,24,27]:#range(1,31):
+    
+    halo = 'halo_'+str(i)    
+    loadSim(lvl,halo,127,63)
+    
+    
+    
+    

### 2018-07-02 Code/plots.py

@@ -55,7 +55,7 @@ def fun1():
             ax1.set_xlabel("R(Kpc/h)")
             ax1.legend()
             ax1.set_title(halo)
-            pdf.savefig(fig)
+            pdf.savefig(fig,bbox_inches='tight')
             plt.close()
 
 
@@ -154,7 +154,7 @@ def fun2():
             axs[-1].set_xlabel("R(Kpc/h)")
             axs[0].set_title(halo)
             
-            pdf.savefig(fig)
+            pdf.savefig(fig,bbox_inches='tight')
             plt.close()
             
             

### 2018-07-02 Code/redshift.py

@@ -1,104 +1,0 @@
-import matplotlib
-matplotlib.use('Agg')
-
-# Python
-from arepo import *
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib.backends.backend_pdf import PdfPages
-from matplotlib.ticker import FormatStrFormatter
-import matplotlib as mpl
-import matplotlib.cm as cm
-import matplotlib.colors as colors
-import os
-
-
-# Simiulation specs
-lvl3 = "level3_DM"
-halonums = np.array([6,16,21])
-
-#halonums = [24]
-with PdfPages("../Plots/Redshift_lvl3DM.pdf") as pdf:
-
-    for j in halonums:
-    
-        # Halo name        
-        halo = "halo_"+str(j)     
-        print("------------------------------------"+halo)   
-    
-        # Paths to files
-        path = "../Plots/"+lvl3+"/"+halo
-        
-        # List of directories
-        listdir = next(os.walk(path))[1]
-        if 'rand_sample' in listdir:
-            listdir.remove('rand_sample')
-        def getkey(l):
-            return int(l.split("_")[1])
-        listdir.sort(key=getkey)
-
-            
-        # Plots    
-        ylabel = ['b/a','c/a','c/b']
-        fig, axs = plt.subplots(figsize=(10,10),nrows=3)
-       
-        # Color settings
-        my_norm = colors.Normalize(0,1)
-        mapa = cm.ScalarMappable(norm=my_norm, cmap='hsv')
-        
-        for direc in listdir:
-            
-            # Semiaxes
-            arr = np.loadtxt(path+"/"+direc+"/s"+direc.split("_")[1]+".txt", delimiter = ",")
-            print(direc)
-            
-            # Loads information dictionary
-            d = np.load(path+"/"+direc+"/info.npy")
-            redshift = d.item().get('Redshift')
-            print("Redshift: "+str(redshift))
-            if redshift > 2:
-                continue
-           
-            # Axial ratios and radii (including rvir)
-            a,b,c = arr[:-1].T
-            xvals = (a*b*c)**(1./3.)
-            yvals = np.array([b/a,c/a,c/b])
-            rvir = arr[-1][0]
-            mappable = 0
-            for ax,yval,ylab in zip(axs,yvals,ylabel):
-                
-                
[…]

### 2018-07-02 Code/simple_Convergence.py

@@ -50,7 +50,7 @@ with PdfPages("../Plots/Simple_Convergence_lvl34_"+sys.argv[1]+".pdf") as pdf:
 
         # Graphics
         ylabel = ['b/a','c/a','c/b']
-        fig, axs = plt.subplots(figsize=(10,10),nrows=len(yvals3))
+        fig, axs = plt.subplots(figsize=(10,15),nrows=len(yvals3))
         for ax,yval3,yval4,ylab,indi in zip(axs,yvals3,yvals4,ylabel,range(3)):
             
             # Hide axes
@@ -108,5 +108,5 @@ with PdfPages("../Plots/Simple_Convergence_lvl34_"+sys.argv[1]+".pdf") as pdf:
         axs[-1].yaxis.set_major_formatter(FormatStrFormatter('%.1f'))
         plt.setp( axs[-1].get_xticklabels(), visible=True)                
         axs[0].set_title(halo)        
-        pdf.savefig(fig)
+        pdf.savefig(fig,bbox_inches='tight')
         plt.close()

### 2018-07-02 Paper/mnras_template.tex
filling some spaces, not editing yet. Next step: intro

@@
 \section{Numerical Simulations}
-Auriga simulations.
+In this work we use the results of the state-of-the art Auriga simulations \cite{auriga}.
+It selected a set of 30 isolated halos from the Evolution and Assembly of GaLaxies and their Environments (EAGLE) project \cite{Eagle}.
+Each halo was identified with the algorithm "Friend of Friends" (FOF) \cite{Davis_et_al._1985}, that recursively links particles if they are closer than some distance threshold referred as linking length.
+EAGLE follows the evolution of fixed-mass particles of $m_{\text{DM}} = 1.15\cdot 10^7\text{M}_{\odot}$ from $z=127$ to $z=0$, adopting the $\Lambda$CDM model from the \cite[Planck Collaboration et al.
+(2014)]{Planck_Collaboration_2014}, which is characterized by the parameters: $\Omega_\Lambda=0.693$, $\Omega_\text{m}=0.307$, $\Omega_\text{b}=0.048$ \& $\text{H}_0=67.77\text{kms} ^{-1}\text{Mpc}^{-1}$.
+
+These halos were randomly selected from a sample of the most isolated quartile of halos whose virial mass $M_{200}$ varied between $10^{12}M_\odot$ and $2\cdot 10^{12}M_\odot$.
+\textbf{This mass is defined as the mass enclosed within the virial radius $R_{200}$ at which the density becomes 200 times the critical density of the universe.
+\huge FOOTNOTE \normalsize}.
+These halos were re-simulated with the (AREPOOO HERE) by increasing the mass resolution of the particles belonging to them and diminishing the resolution of the rest of the particles.
+This would efficiently simulate external gravitational effects over the studied structure while focusing on a high-resolution version of it.\\
+
+Various versions of the same halo were simulated for different degrees of realism.
+All 30 halos were simulated within a level-4-degree of resolution defined for Aquarius simulations corresponding to $\tilde 3\cdot 10^6$ high resolution particles of $\tilde 2.5 \cdot 10^5 M_\odot$.
+The principal details of each of these halos are consigned on the table \ref{tab:level4}.
+From these halos, 6 of them where re-simulated at level 3 (higher) resolution taking into account a spatial factor of 2 in each dimension.
+For more information about level 3 halos, their details are printed on table \ref{tab:level3}.
+Furthermore, fore each halo in each level of resolution there are two versions of the simulation.
+One of tracks the evolution of DM-only particles while the remaining one evolves DM and baryions with magneto-hydrodynamical (MHD) physics, including DM.\\
 
@@
 %\subsection{The solid ellipsoid method}
+
+The discretization of the DM density field into particles makes it difficult  to perform some calculations that would require a more continuous distribution.
+Therefore, there is no trivial way to calculate the DM halo shape at a determined radius.
+There are different approaches \textbf{ \large ISODENSITY, ISOPOTENTIAL, potential gets rounder, cite binney \normalsize }
+\textbf{\large Talk about difference between volume method and isodensity contour at least for DM halos \normalsize} \cite{Vera-Ciro_et_al._2011}.
+In this work we follow the guidelines by \cite[Vera-Ciro et al.
+2011]{Vera-Ciro_et_al._2011} which includes the use of the shape method proposed by \cite[Allgood et al.
+2006]{Allgood_et_al._2006}.\\
+
+To calculate the DM halo shape, we initially consider particles enclosed within a sphere of radius $r$. We calculate the reduced inertia tensor:
+
+\begin{equation}
+I_{ij} = \sum_k \frac{x_k^{(i)}x_k^{(j)}}{d^2_k},
+\label{eq:inertia}
+\end{equation}
+
+whose components are weighted by the distance $d^2=x^2+y^2+z^2$, so that each particle contribute with same importance to the sum regardless of their radius from the center.\\
+
+The diagonalization of this tensor yields the principal axes of the structure, as well as the eigen-quantities which are proportional to the squared principal axes $a>b>c$.
+\textbf{\large SUMARIZE \normalsize} However, if we characterize an ellipsoid taking into account only particles enclosed within a sphere, we are effectively miscalculating its triaxiality \cite{Allgood_et_al._2006}.
+For this reason, we iteratively recalculate the inertia tensor taking into account the previously characterized ellipsoid.\\
+
+AllGood et al.
+propose to use the eigenvalues $a>b>c$ and their respective eigen-axes $v_a,v_b,v_c$ to recalculate the inertia tensor over the particles enclosed by the ellipsoid with principal axes (along the respective eigenvectors) equal to $r,r/q,r/s$, where ere $q = b/a$ and $s=c/a$ are the axial ratios.
+In other words, we repeat the process of calculating the inertia matrix by taking into account particles within an ellipsoid with axial ratios given by the previous diagonalization.
+In this case, as the constant of proportionality is a free parameter, we choose to hold the size (not the direction) of the principal axis constant.\\
+
+This method looks reliable and it would eventually converge to a more accurate characterization of the halo ellipsoid.
+However, we are computing the reduced inertia tensor by weighting the contributions with the spherical-metric distance $d^2=x^2+y^2+z^2$, where particles within the same spherical surface are given the same importance.
+This means we are again introducing some error in the triaxiality of the structure.
+For this reason, on each iteration we must calculate the inertia tensor taking into account an elliptic metric: $\bar{d}^2 = x^2+y^2/q^2+z^2/s^2$, assuming $x,y,z$ are the corresponding principal axes.\\
+
+In case this concept of an elliptic metric is difficult to grasp, let us consider that, instead of converting the initial enclosing sphere to the halo ellipse, we are converting the halo ellipsoid into a sphere by performing scale transforms along the respective eigen-axes.
+From this point of view, we start our first-guess calculation of the ellipsoid by computing the reduced inertia tensor \eqref{eq:inertia} for particles enclosed within a sphere of radius $r$.
+Then with the results of this first guess, we perform the following scale transform:
+
+\begin{align}
+(x,y,z) &\rightarrow (x',y',z')=(x,y/q,z/s) \label{eq:scale}\\
+q &=  b/a \nonumber \\
+s &= c/a \nonumber ,
+\end{align}
+
+where we assumed the unit vectors $\hat{x},\hat{y},\hat{z}$ are oriented at the principal elliptic axes.
+We then repeat the process of calculating the reduced inertia tensor and performing the scale transformation until we achieve a certain convergence criterion.
+We stop this iterative process when the sum of the fractional change in axes is less than $10^{-6}$.
+Finally, we obtain the shape of the halo at the geometric mean radius $(abc)^{1/3}$, which is not much different from the initial radius.\\
+
+Notice that, for diagonalization purposes, calculating the inertia tensor with the scaled coordinates $x',y',z'$ is equivalent to calculating it with the un-scaled coordinates $x,y,z$, using the elliptic-metric distance $\bar{d}^2 = x^2+y^2/q^2+z^2/s^2$.\\
 
@@
 
+\begin{figure}
+  \centering
+  \subfloat[Aligned Axes]{\includegraphics[width=1\columnwidth]{./pics/well_axes.png}}
+  \hfill
+  \subfloat[Rotating Axes]{\includegraphics[width=1\columnwidth]{./pics/rotating_axes.png}}
+  \hfill
+  \subfloat[Chaotic Axes]{\includegraphics[width=1\columnwidth]{./pics/chaotic_axes.png}}
+  \hfill
+  \caption{Description of axes alignments }
+  \label{fig:slices}
+\end{figure}
+
 \section{Conclusions}

### 2018-07-16 Paper/mnras_template.tex
Paper avances

--- 2018-07-02 Paper/mnras_template.tex
@@
 % List of institutions
-$^{1}$Departamento de Física, Universidad de los Andes, Cra. 1 No.
-18A-10, Edificio Ip, Bogotá, Colombia.\\
+$^{1}$Departamento de F\'sica, Universidad de los Andes, Cra. 1 No.
+18A-10, Edificio Ip, Bogot\', Colombia.\\
 $^{2}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg
@@
 It should be a single paragraph not more than 250 words (200 words for Letters).
-No references should appear in the abstract.
+No references should appear in the abstract.This is a simple template for authors to write new MNRAS papers.
+The abstract should briefly describe the aims, methods, and main results of the paper.
+It should be a single paragraph not more than 250 words (200 words for Letters).
+No references should appear in the abstractThis is a simple template for authors to write new MNRAS papers.
+The abstract should briefly describe the aims, methods, and main results of the paper.
+It should be a single paragraph not more than 250 words (200 words for Letters).
+No references should appear in the abstract
 \end{abstract}
@@
 
-This is a simple template for authors to write new MNRAS papers.
-See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
-for a full user guide.
+%This is a simple template for authors to write new MNRAS papers.
+%See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
+%for a full user guide.
 
@@
 in context, cites relevant earlier studies in the field by \citet{Others2013},
-and describes the problem the authors aim to solve \citep[e.g.][]{Author2012}.
+and describes the problem the authors aim to solve \citep[e.g.][]{Author2012}.\\
+
+Introduce/ Motivation simulations, sphereical top hat collapse.\\
+
+One of the principal predictions of the CDM model is that DM halos are ellipsoidal and very well characterized by the principal axes $a>b>c$.
+This is due, among other causes, to the anisotropical and clumpy accretion of matter influenced by environmental structures \citep[see?][]{environment-shape}.
+The general concensus in numerical simulations \citep[e.g.][]{TriaxialHalos1,TriaxialHalos2,etc} is that halos tend to be prolate with axial ratios b/a ~ \textit{number}, c/a ~ \textit{number} and small differences may arise by the use different methods in numerical recipies for the simulations and the shape-calculation methods  \citep[see][]{Allgood et al.
+2006}.
+Some studies have gone a step further as for analyzing the dependence of shape of the DM halo on the radius and redshift \citep[e.g.][]{Shape-radius-papers, including Allgood}, generally finding that halos are rounder at the outerskirts and at lower redshift.\\
+
+Due to the evasive nature of DM, properly constraining the shape of DM halos is a very difficult endeavour.\\
+
+Better connector with observations of distant galaxies.
+Gravitational lensing and star tracers.
+(Talk about discrepancy with simulations, perhaps later) and state that the preference for axisymmetrical shapes may arise from the observational restrictions (projection) look for citations about this .\\
+
+In the case of the Milky Way, where we have a three-dimensional view from the inside, there seems to be a general agreement for oblate (i.e.
+a=b>c) configurations at small distances around \~ <20kpc \citep[see][]{LM10,Bovy2016,Loebman,Vera-Ciro, RobOllingMerrifield,Bovy,BanerjeeChanda}, and more triaxial and prolate configurations on the outter distances \~>20kpc \citep[see][]{Vera-Ciro,LMJ09,Deg,BanerjeeChanda}.
+However, some studies are inclined towards prolate configurations even at the inner parts of the halo \citep[see][]{BowdenEvansWilliams,Findothers}, and although it previously seemed that a triaxial DM halo on the outerskirts would be necessary to fully explain the characterization of the Sagittarius stream \citep[see][]{LMJ09}, more recent studies put into doubt (question) this claim by reporting inconsistencies with narrow stellar streams \citet{PearsonKupperJohtnston, MoreLikeThis} or finding that the relaxation of other constraints may make this claim unnecessary (wording) \citet{IbataLewisMartin}.\\
+
+Although observations predict more symmetric halos than DM-only simulations, this may be an effect of not taking into account the gravitational effects of baryonic matter.
+The collapse of baryonic matter generate denser structures than those of DM only, whose potential may affect the kinematics that give shape to DM halos by making them more axisymmetrical.
+Regarding the specifics of this rounding effect and stability, there is much to be known as the simulation of baryonic dynamics in the whole cosmological context to galactic-scale resolution is not a trivial task and is usually subject to simplifications to analyze extreme cases as boundary constrains.
+Simple study the adiabatical growth of a disk potential in DM halos of different triaxiality and in different orientations \cite{Debattista-Moore,Debattista-Roskar}.
+While these studies are elucidating about dynamical aspects that may play important roles in the shape rounding, they neglect some important galactic properties that may also contribute to this rounding that can be only analyzed with more sophisticated hydrodynamical simulations with restricted models of feedback \cite{Abadi-Navarro,Bryan-Kay}.
+In this way, it can be demonstrated that the galaxy formation efficiency \cite{Abadi} and the history of formation may also determine the extent of this rounding.\\
+
+In this work, we analyze the Auriga simulations wich etc, where we can analyze the effect of dynamical properties of baryons together with galactic features, that are involved in the shaping of the DM halo shape of realistic MW-like galaxies.
 
 \section{Numerical Simulations}
-Auriga simulations.
+In this work we use the results of the state-of-the art Auriga simulations \cite{auriga}.
+It selected a set of 30 isolated halos from the Evolution and Assembly of GaLaxies and their Environments (EAGLE) project \cite{Eagle}.
+Each halo was identified with the algorithm "Friend of Friends" (FOF) \cite{Davis_et_al._1985}, which recursively links particles if they are closer than some threshold distance referred as linking length.
+EAGLE follows the evolution of fixed-mass particles of $m_{\text{DM}} = 1.15\cdot 10^7\text{M}_{\odot}$ from $z=127$ to $z=0$, adopting the $\Lambda$CDM model from the \cite[Planck Collaboration et al.
+(2014)]{Planck_Collaboration_2014}, which is characterized by $\Omega_\Lambda=0.693$, $\Omega_\text{m}=0.307$, $\Omega_\text{b}=0.048$ \& $\text{H}_0=67.77\text{kms} ^{-1}\text{Mpc}^{-1}$.
+
+These halos were randomly selected from a sample of the most isolated quartile of halos whose virial mass $M_{200}$ varied between $10^{12}M_\odot$ and $2\cdot 10^{12}M_\odot$.
+\textbf{\tiny This mass is defined as the mass enclosed within the virial radius $R_{200}$ at which the density becomes 200 times the critical density of the universe.
+\huge FOOTNOTE \normalsize}.
+These halos were re-simulated with the (AREPOOO HERE) by increasing the mass resolution of the particles belonging to them and diminishing the resolution of the rest of the particles.\\
+
+Various versions of each halo were modelled with different degrees of realism.
+All 30 halos were simulated within a level-4-degree of resolution defined for Aquarius simulations corresponding to $\tilde 3\cdot 10^6$ high resolution particles of $\tilde 2.5 \cdot 10^5 M_\odot$.
+The principal details of each of these halos are consigned on the table \ref{tab:level4}.
+From these halos, 6 of them where re-simulated at level 3 (higher) resolution taking into account a spatial factor of 2 in each dimension.
+For more information about level 3 halos, their details are printed on table \ref{tab:level3}.
+Furthermore, fore each halo in each level of resolution there are two versions of the simulation.
+One of tracks the evolution of DM-only particles while the remaining one evolves DM and baryions with magneto-hydrodynamical (MHD) physics, including DM.\\
 
@@
 %\subsection{The solid ellipsoid method}
+
+There is no trivial way to calculate the DM halo shape at a determined radius due to the discretization of particles.
+For practical effects, observational models focus on the shape of the DM isopotential \cite{isopotential} or isodensity \cite{isodensity} contours.
+In cosmological simulations, it is preferred to work with the isodensity contours which is directly calculated from particle positions.
+However, these density contours are not smooth and are very sensitive to the presence of small satelites \cite{Springel Isodensity}.
+For this reason we determine the shape taking into account volume-enclosed particles, rather than shell-enclosed.
+While this approach allows the cumulative influence of outter shells on the outter shapes, it has been demonstrated for DM-only simulations that this effect becomes important only for big radii \cite{vera-Ciro aquarius}.
+We therefore follow the method of \cite[Allgood et al.
+2006]{Allgood_et_al._2006} that consits in the use of the reduced inertia tensor,   \\
+
+\begin{equation}
+I_{ij} = \sum_k \frac{x_k^{(i)}x_k^{(j)}}{d^2_k},
+\label{eq:inertia}
+\end{equation}
+
+with components weighted by the k-th particle distance $d^2=x^2+y^2+z^2$.\\
+
+The diagonalization of this tensor yields the principal axes of the structure as well as the eigen-quantities which are proportional to the squared principal axes $a>b>c$.
+We start our calculations taking into account particles within a sphere of radius $R$ and then recharacterize the triaxial parameters by taking into account particles within an ellipsoid of semi-axes $r,r/q,r/s$ and weighted distance $d^2=x^2+(y/q)^2+(z/s)^2$, where ere $q = b/a$ and $s=c/a$ are the previously calculated axial ratios.
+We repeat this process until the average deviation of semi-axes is less than $10^{-6}$.\\
 

### 2018-07-16 Code/effect_of_gas.py
Linear model MCMC correlations

@@ -1,3 +1,6 @@
+#import matplotlib
+#matplotlib.use('Agg')
+
 ########################################################################################################
 ##### THIS SCRITP IS FOR READING THE SUMARY OF IMPORTANT QUANTITIES FOR DM HALO SHAPE               ####
 ##### READS:                                                                                        ####
@@ -60,12 +63,26 @@ def main():
     # Important quantities (normalized)
     GasDiskRad = par['GasDiskRad']               # halfmass radius of gas
     StarDiskRad = par['StellarDiskRad']          # Same for stellar mass     
-    SFRD = par['SFR']/(StarDiskRad**2)           # Star formation ratio density
-    gas_den = par['MassGas']/(GasDiskRad**2)     # Mass densities
-    star_den = par['MassStars']/(StarDiskRad**2)
-    BH_den = par['MassBH']/(StarDiskRad**2)
-    bar_frac = (par['MassGas']+par['MassStars'])/par['MassDM'] # The baryonic fraction
+    gas_den = par['MassGas']#/(GasDiskRad**2)     # Mass densities
+    star_den = par['MassStars']#/(StarDiskRad**2)
+    BH_den = par['MassBH']#/(StarDiskRad**2)
+    bar_frac = (par['MassGas']+par['MassStars'])/(par['MassDM']+par['MassGas']+par['MassStars']) # The baryonic fraction
     
+    '''
+    import matplotlib.pyplot as plt
+    
+    plt.plot(StarDiskRad,bar_frac, 'ro')
+    plt.xlabel('Star Rad')
+    plt.ylabel('Baryonic Fraction')
+    plt.savefig('./pics/Baryons_plots/StarRad_barfrac.png')
+    plt.close()
+    
+    plt.plot(np.log10(star_den+gas_den),bar_frac, 'ro')
+    plt.xlabel('Star mass')
+    plt.ylabel('Baryonic Fraction')
+    plt.savefig('./pics/Baryons_plots/StarMass_barfrac.png')
+    plt.close()
+    '''
     # The disk directions 
     disk_vec = params.T[-3:].T
 
@@ -128,34 +145,173 @@ def main():
     # Defines Sphericity
     asph_MHD = asphericity(axesMHD) #shape: (nhalos,5)
     asph_DM  = asphericity(axesDM)
[…]

### 2018-07-18 Paper/mnras_template.tex
Add files via upload
New Table sumarizing results and a clean triaxiality plot

@@
 \section{Results}
-Here we present our principal results blah blah blah.
+For convergence reasons and seeking to make our results observation-comparable, we restrict the sampling of the ellipsoidal parameters to radii between $10\% and 100\%$ of the virial radius $R_500$, defined as the (DEFINITION OF VIRIAL RADIUS).
+All our results make use of this reference radius unless stritically stated otherwise.\\
 
 \subsection{The radial tendency of axial ratios}
-First, it is important to verify that halos are rounder at larger radii, for both MHD and DM simulations.
+To have a more complete picture about the effect of baryons on the DM halo shape, we begin by verifying/understanding the radial evolution (dependence?) of the shape.
+In the case of DM-only simulations, it is expected that halos get monotonically rounder at larger radii due to the gravitational effect of inner shells \citep{Vera-Ciro et al.
+2012}.
+A graphic example of this rounding can be checked on figure \ref{fig:DM_MHD}, where we plot the a projection of a DM-only halo aligned with the calculated minor axis at two different radius together with the estimated projected ellipsoidal.
+Formally, this effect is reflected in the axial ratios $b/a,c/a$, which tend to unity on the outerskirts of the halo.
+As a representative sample of this relations, we show on figure \ref{fig:DM relation} the evolution of the axial ratios $b/a,c/a$ and the triaxiality parameter $T=\frac{a^2-b^2}{a^2-c^2}$ in a wide range of radii.\\
+
+In general, we find that DM-only halos are shaped with parameters in table \ref{table:DM-only parameters}.
+To show this relation is real and not a result of strong peculiarities of particular DM halos, we resume the results of the 30 auriga simulations on the figure \ref{fig: triaxial plane} where each shape represents a point in the triaxiality plane $c/a Vs b/a$.
+Check Vera-ciro onthis.\\
 
@@
   \hfill
-  \subfloat[halo 27 MHD shape at small radius]{\includegraphics[width=0.5\columnwidth]{./pics/MHD_Vs_DM/level4_MHD_halo_27_inner.png}}
-  \hfill
-  \subfloat[halo 27 MHD shape at big radius]{\includegraphics[width=0.5\columnwidth]{./pics/MHD_Vs_DM/level4_MHD_halo_27_outter.png}}
-  \caption{DM density for inner (left) and outer (right) parts of the halo 27.
-We present both versions of the halo: DM (up) \& MHD (down).
-The horizontal (vertical) axes are aligned to the major (medium) axes.
-(optimaze space and description) }
+  \caption{DM density for inner (outer) parts of the halo 27 on the left (right) part. The horizontal (vertical) axes are aligned to the major (medium) axes. (optimaze space and description) }
   \label{fig:slices}
 \end{figure}
+
+\begin{table}
+\begin{tabular}{l|cccc}
+Measure / Radius& $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R$\\
+\hline \hline
+$\bar{q}$&$0.57^{+0.09}_{-0.08}$&$0.61^{+0.15}_{-0.08}$&$0.65^{+0.18}_{-0.10}$&$0.70^{+0.13}_{-0.10}$ \\ [0.1cm]
+$\bar{s}$&$0.45^{+0.11}_{-0.04}$&$0.49^{+0.09}_{-0.05}$&$0.52^{+0.10}_{-0.05}$&$0.56^{+0.10}_{-0.05}$ \\ [0.1cm]
+$\bar{T}$&$0.88^{+0.04}_{-0.12}$&$0.84^{+0.08}_{-0.23}$&$0.81^{+0.08}_{-0.29}$&$0.75^{+0.14}_{-0.25}$ \\
+
+\hline
+\end{tabular}
+\caption{Median values of axial ratios $q,s$ and triaxiality parameter $T$ for DM halos in DM-only simulations at different radii (columns). }
+\label{tabe:DM table}
+\end{table}
+
+Concerning MHD halos, the expected tendency is not clear.
+Some studies claim that the DM halo must be oblate, at least in the vicinities of the disk, to ensure its stability.
+However, not much is said about its dependence with radius as these studies focus rather on the effects of baryons on the dynamics of the halo.
+Taking a look at some representative graphics similar to those presented before, \ref{fig:,fig:}, some things are noticeable: first, the halo is almost perfectly oblate around $\approx 10-30$Kpc and secong: its axial ratios start decreasing very slowly after $50$Kpce.
+Overall, our results are sumarized on table \ref{table:MHD}, where we included some extra measurement at twice the size of the stelar disk HalfRad.\\
+
+If we compare with obervational values, we must at least take isodensity contours (). We present this comparison  at two different radii for MHD simulations on figure \ref{fig:}. \\
+
+Little discussion: Are our results congruent with observations? at which radii, does the DM halo shape vary that much?.\\
 
@@
   \centering
-  \subfloat[Level4 DM inner Vs outer regions]{\includegraphics[width=0.5\columnwidth]{./pics/Triaxial_Plane/Triaxiality_DM_lvl4.png}}
+ \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_DM.png}
+
   \hfill
-  \subfloat[Level4 MHD inner Vs outer regions]{\includegraphics[width=0.5\columnwidth]{./pics/Triaxial_Plane/Triaxiality_MHD_lvl4.png}}
-  \hfill
-  \caption{General tendency on the triaxial plane $c/a$ Vs $b/a$.
-Some observational constraints are plotted alongside our results (Optimize space.
-caption replaces title.
-Present constraints representation of density)}
-  \label{fig:Triaxiality_DM_MHD}
+  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. Errorbar shows median and errors for each sampled radii. }
+  \label{fig:Triax_DM}
 \end{figure}
@@
 \subsection{The rounding effect of baryons}
-Here we discuss the rounding effect of baryons. We quantify this rounding effect and look for correlations with important baryonic properties of the galaxy.
+Now that we have characterize the shapes of DM-only and MHD halos at different radii
 

### 2018-07-19 Code/effect_of_gas.py
sadas

@@ -113,6 +113,9 @@ def main():
     T_MHD = get_T(axesMHD) #shape: (nhalos,5)
     T_DM  = get_T(axesDM)
     
+    Table(axesDM[:,:-1,:],"./pics/Triax_DM.png")
+    
+    
     # Define deviation from sphericity 
     
     
@@ -145,10 +148,10 @@ def main():
     # Defines Sphericity
     asph_MHD = asphericity(axesMHD) #shape: (nhalos,5)
     asph_DM  = asphericity(axesDM)
-    #y = (asph_MHD - 0*asph_DM)[:,1] # 0 -> only calculated at 0.125 Rvir
+    y = (asph_MHD - 0*asph_DM)[:,1] # 0 -> only calculated at 0.125 Rvir
     
     #y1 = axesMHD[:,0,1]/axesMHD[:,0,0] # this is b/a MHD for all haloes
-    y = ((axesMHD[:,0,2]/axesMHD[:,0,0]))**(-1) #- (axesDM[:,0,2]/axesDM[:,0,0])) # c/a MHD
+    #y = ((axesMHD[:,0,2]/axesMHD[:,0,0]))**(-1) #- (axesDM[:,0,2]/axesDM[:,0,0])) # c/a MHD
 
     # Just to see if the increase is related to the unperturbed state of the halo
     x1 = axesDM[:,0,1]/axesDM[:,0,0] #b/a DM (q)
@@ -178,29 +181,89 @@ def main():
     sigmaX = np.std(X, axis = 0)
     
     #X = ((X-meanX)/sigmaX)
+    
 
 
-    MCMC(X,y,X_names=Xnames)
+    #MCMC(X,y,X_names=Xnames)
+
+
+def Table(axes,plot_name):
+
+    import matplotlib.pyplot as plt
+    plt.rc('text', usetex=True)
+    plt.rc('font', family='serif')
+
+    # for the table (PAPER)
+    T = get_T(axes)
+    summary = np.array([axes[:,:,1]/axes[:,:,0], axes[:,:,2]/axes[:,:,0],T])
+    mean = np.percentile(summary,50,axis=1)
+    std1  = np.percentile(summary,84,axis=1)-mean
+    std2  = mean - np.percentile(summary,16,axis=1)
+    nmean = ['$\\bar{q}$','$\\bar{s}$','$\\bar{T}$']
+    nstd = ['$\\sigma_{q}$','$\\sigma_{s}$','$\\sigma_{T}$']  
[…]

### 2018-07-28 Paper/mnras_template.tex
Changes

@@
 \section{Results}
-For convergence reasons and seeking to make our results observation-comparable, we restrict the sampling of the ellipsoidal parameters to radii between $10\% and 100\%$ of the virial radius $R_500$, defined as the (DEFINITION OF VIRIAL RADIUS).
-All our results make use of this reference radius unless stritically stated otherwise.\\
+For convergence reasons and seeking to make our results observation-comparable, we restrict the sampling of the ellipsoidal parameters to radii between $1/16 R_{vir} and 2R_{vir}$ of the virial radius $R_{500}$, defined as the (DEFINITION OF VIRIAL RADIUS).
+All our results make use of this reference radius unless strictly stated otherwise.\\
 
@@
 
-In general, we find that DM-only halos are shaped with parameters in table \ref{table:DM-only parameters}.
+In general, we find that DM-only halos are shaped with parameters in table \ref{table:DM table}.
 To show this relation is real and not a result of strong peculiarities of particular DM halos, we resume the results of the 30 auriga simulations on the figure \ref{fig: triaxial plane} where each shape represents a point in the triaxiality plane $c/a Vs b/a$.
@@
 \begin{table}
-\begin{tabular}{l|cccc}
-Measure / Radius& $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R$\\
+\setlength{\tabcolsep}{3pt}
+\begin{tabular}{l|cccccc}
+ &$R_{1/16}$& $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R_1$ & $R_2$\\
 \hline \hline
-$\bar{q}$&$0.57^{+0.09}_{-0.08}$&$0.61^{+0.15}_{-0.08}$&$0.65^{+0.18}_{-0.10}$&$0.70^{+0.13}_{-0.10}$ \\ [0.1cm]
-$\bar{s}$&$0.45^{+0.11}_{-0.04}$&$0.49^{+0.09}_{-0.05}$&$0.52^{+0.10}_{-0.05}$&$0.56^{+0.10}_{-0.05}$ \\ [0.1cm]
-$\bar{T}$&$0.88^{+0.04}_{-0.12}$&$0.84^{+0.08}_{-0.23}$&$0.81^{+0.08}_{-0.29}$&$0.75^{+0.14}_{-0.25}$ \\
+$\bar{q}$&$0.55^{+0.07}_{-0.07}$&$0.57^{+0.09}_{-0.08}$&$0.61^{+0.15}_{-0.08}$&$0.65^{+0.18}_{-0.10}$&$0.70^{+0.13}_{-0.10}$&$0.75^{+0.10}_{-0.10}$ \\ [0.1cm]
+$\bar{s}$&$0.42^{+0.12}_{-0.03}$&$0.45^{+0.11}_{-0.04}$&$0.49^{+0.09}_{-0.05}$&$0.52^{+0.10}_{-0.05}$&$0.56^{+0.10}_{-0.05}$&$0.59^{+0.11}_{-0.06}$ \\ [0.1cm]
+$\bar{T}$&$0.89^{+0.03}_{-0.08}$&$0.88^{+0.04}_{-0.12}$&$0.84^{+0.08}_{-0.23}$&$0.81^{+0.08}_{-0.29}$&$0.75^{+0.14}_{-0.25}$&$0.71^{+0.16}_{-0.19}$ \\ [0.1cm]
 
@@
 However, not much is said about its dependence with radius as these studies focus rather on the effects of baryons on the dynamics of the halo.
-Taking a look at some representative graphics similar to those presented before, \ref{fig:,fig:}, some things are noticeable: first, the halo is almost perfectly oblate around $\approx 10-30$Kpc and secong: its axial ratios start decreasing very slowly after $50$Kpce.
-Overall, our results are sumarized on table \ref{table:MHD}, where we included some extra measurement at twice the size of the stelar disk HalfRad.\\
+Taking a look at some representative graphics similar to those presented before, \ref{fig:,fig:}, some things are noticeable: first, the halo is almost perfectly oblate around $\approx 10-30$Kpc and second: its axial ratios start decreasing very slowly after $50$ and below $10Kpc$.
+Overall, our results are sumarized on table \ref{MHD table}, where we included some extra measurement at twice the size of the gas disk HalfRad.\\
+
+\begin{table}
+\setlength{\tabcolsep}{3pt}
+\begin{tabular}{l|ccccccc}
+ &$R_{1/16}$& $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R_1$ & $R_2$& $R_{Disk}$\\
+\hline \hline
+$\bar{q}$&$0.93^{+0.04}_{-0.04}$&$0.95^{+0.03}_{-0.03}$&$0.95^{+0.02}_{-0.05}$&$0.93^{+0.04}_{-0.06}$&$0.93^{+0.04}_{-0.10}$&$0.92^{+0.03}_{-0.09}$&$0.94^{+0.03}_{-0.09}$ \\[0.1cm]
+$\bar{s}$&$0.73^{+0.05}_{-0.09}$&$0.73^{+0.07}_{-0.10}$&$0.73^{+0.08}_{-0.10}$&$0.73^{+0.09}_{-0.08}$&$0.75^{+0.07}_{-0.11}$&$0.74^{+0.07}_{-0.10}$&$0.71^{+0.11}_{-0.06}$ \\[0.1cm]
+$\bar{T}$&$0.31^{+0.15}_{-0.22}$&$0.20^{+0.24}_{-0.12}$&$0.24^{+0.20}_{-0.12}$&$0.30^{+0.26}_{-0.16}$&$0.36^{+0.23}_{-0.23}$&$0.39^{+0.26}_{-0.13}$&$0.24^{+0.37}_{-0.10}$ \\[0.1cm]
+\hline
+\end{tabular}
+\caption{Median values of axial ratios $q,s$ and triaxiality parameter $T$ for DM halos in MHD simulations at different radii (columns). }
+\label{tabe:MHD table}
+\end{table}
+
+Talk about source of triaxiality at the inner parts of the halos (bar?).
+This source of triaxiality at the inner parts explains why the axial ratios are $\approx 0.95$ and not exactly $1$.
+We should also discuss that the decrease in the axial ratios for bigger radii may be actually bigger/steeper but it is dimmed by the contribution of inner parts.\\
 
@@
 Little discussion: Are our results congruent with observations? at which radii, does the DM halo shape vary that much?.\\
-
-\begin{figure}
-\centering
-\subfloat[halo 16]{\includegraphics[width=0.5\columnwidth]{./pics/halo16.png}}
-  \hfill
-  \subfloat[halo 27]{\includegraphics[width=0.5\columnwidth]{./pics/halo27.png}}
-\caption{Radial profile for axial ratios and the triaxiality parameter $T=\frac{1-b/a}{1-c/a}$ from halo 27 and halo 16.
-These halos have a clear radial tendence towards sphericity (for smaller radii until $\approx 3$Kpc), which can be confirmed with the triaxiality parameter.
-(Merged Column)}
-\label{fig:DM_MHD}
-\end{figure}
 
@@
 \subsection{The rounding effect of baryons}
-Now that we have characterize the shapes of DM-only and MHD halos at different radii
+
+\begin{figure}
+\centering
+{\includegraphics[width=0.8\columnwidth]{./pics/halo16.png}}
+\caption{Radial profile for axial ratios and the triaxiality parameter $T=\frac{1-b/a}{1-c/a}$ from halo 16 and halo 16.
+These halos have a clear radial tendence towards sphericity (for smaller radii until $\approx 3$Kpc), which can be confirmed with the triaxiality parameter.
+(Merged Column)}
+\label{fig:DM_MHD}
+\end{figure}
+
+It is expected etc. show an example? or compare statistics?
 
@@
 \subsection{The historical shape}
-Here we study the memory shape and how it can be deduced from the historic radial shapes. Also why it is lost for MHD even when radial profiles have the same historic tendencies.
+One of the principal motivations to study the radial dependence of the DM halo shape is that it may encode some clues about its formation history.
+We have already shown that DM-only halos seem to exhibit a steady and monotonous growth in its axial ratios when sampled at bigger radii.
+One similar effect can be found if we sample the shape at the virial radius, this time at varying redshift.
+It is easy to see that the axial ratios increase with decreasing redshift, which is expected by the continuous influence of the gravitational potential \cite{VeraCiro}.
+\\
+
+Interestingly, these two parametic plots i.e.
+$(b/a,c/a)(z=0,r)$ and $(b/a,c/a)(z,r=R_{vir})$ are very correlated for DM only halos \ref{fig:redshift correlation}.
+This means that, for DM-only halos, one can approximate its shape at the virial radius at higher redshift by simply sampling its current shape at a smaller radius.
+This relationship relies strongly on the steady and monotonous tendency of DM halos towards sphericity for bigger radii and smaller redshift.\\
 
@@
 
+MHD halos, on the other hand, do not exhibit tendency towards sphericity with bigger radii, but they do get sistematically rounder at lower redshift \ref{fig:MHD profile radius and redshift}.
+This effectively vanishes this correlation as seen from a DM halo \ref{fig:MHD Z Triax}.\\
+
+Discuss if this correlation may be recovered if compared for example at Disk radius in stead of virial radius.\\
+
 \subsection{The orientation of the principa axes}
@@
 We found that while the angular momentum tend to be aligned with the minor axis of the ellipsoid, this may not be the case all times.
-When there is an alignment it is usually within 20 degrees.
-When there is not an alignment, then there is no simple way to determine toward which axis it is oriented.
-Furthermore, the principal axes alignment usually change with radius (rotation, swap).
-This really questions the strong constrains on the MW DM halo models.
+When there is an alignment it is usually within 20 degrees (get a histogram of this.
+and an evolution of this histogram with time).
+When there is not an alignment, then there is no simple way to determine towards which axis it is oriented.
+Furthermore, the principal axes alignment usually change with radius (rotation, swap, verify).
+This ask for relaxation on the strong constrains on the MW DM halo models.
 

### 2018-08-11 Paper/mnras_template.tex
Add files via upload
Draft Paper

@@
 
-Although observations predict more symmetric halos than DM-only simulations, this may be an effect of not taking into account the gravitational effects of baryonic matter.
-The collapse of baryonic matter generate denser structures than those of DM only, whose potential may affect the kinematics that give shape to DM halos by making them more axisymmetrical.
-Regarding the specifics of this rounding effect and stability, there is much to be known as the simulation of baryonic dynamics in the whole cosmological context to galactic-scale resolution is not a trivial task and is usually subject to simplifications to analyze extreme cases as boundary constrains.
-Simple study the adiabatical growth of a disk potential in DM halos of different triaxiality and in different orientations \cite{Debattista-Moore,Debattista-Roskar}.
-While these studies are elucidating about dynamical aspects that may play important roles in the shape rounding, they neglect some important galactic properties that may also contribute to this rounding that can be only analyzed with more sophisticated hydrodynamical simulations with restricted models of feedback \cite{Abadi-Navarro,Bryan-Kay}.
-In this way, it can be demonstrated that the galaxy formation efficiency \cite{Abadi} and the history of formation may also determine the extent of this rounding.\\
+Although observations predict more symmetric halos than DM-only simulations, there is strong evidence claiming that the presence of baryons need/make more axisymmetrical halos.
+Some studies have shown that to ensure the stability of a hydrodynamical (numeric) disk artificially embeded in a static(non-changing) DM halo, its shape must be axisymmetrical \cite{}.
+Other works have studied this rounding effect by emulating a disk as an adiabatically growing potential inside an N-body triaxial DM halo \cite{Debattista-Moore,Debattista-Roskar, katzantzidis}, finding that (findings of this study -debattista-).
+Other works of this type?\\
 
-In this work, we analyze the Auriga simulations wich etc, where we can analyze the effect of dynamical properties of baryons together with galactic features, that are involved in the shaping of the DM halo shape of realistic MW-like galaxies.
+While these studies are elucidating about dynamical aspects that may play important roles in the rounding of the DM halo shape, they do not follow baryons in the whole cosmological context.
+Abadi-Navarro and Bryan-Kay studied the evolution of galaxies in hydrodynamical simulations with restricted models of feedback \cite{Abadi-Navarro,Bryan-Kay} finding that the galaxy formation efficiency \cite{Abadi} and the history of formation may also determine the extent of this rounding.\\
+
+In general, there is much to be known about the specifics of the rounding effec of baryons.
+(There are have been no realistic simulations of MW-like galaxies to a resolution/realism that allows us to obtain stronger conslusions)
+
+In this work, we analyze the Auriga simulations wich etc, where we can analyze the effect baryons together with galactic features, that are involved in the shaping of the DM halo shape of realistic MW-like galaxies.
 
@@
 To have a more complete picture about the effect of baryons on the DM halo shape, we begin by verifying/understanding the radial evolution (dependence?) of the shape.
-In the case of DM-only simulations, it is expected that halos get monotonically rounder at larger radii due to the gravitational effect of inner shells \citep{Vera-Ciro et al.
+In the case of DM-only simulations, it is expected that halos get monotonically rounder at larger radii due to (the gravitational effect of inner shells?) \citep{Vera-Ciro et al.
 2012}.
-A graphic example of this rounding can be checked on figure \ref{fig:DM_MHD}, where we plot the a projection of a DM-only halo aligned with the calculated minor axis at two different radius together with the estimated projected ellipsoidal.
+A graphic example of this rounding can be checked on figure \ref{fig:slices}, where we plot the a projection of a DM-only halo aligned with the calculated minor axis at two different radius together with the estimated projected ellipsoidal.
 Formally, this effect is reflected in the axial ratios $b/a,c/a$, which tend to unity on the outerskirts of the halo.
-As a representative sample of this relations, we show on figure \ref{fig:DM relation} the evolution of the axial ratios $b/a,c/a$ and the triaxiality parameter $T=\frac{a^2-b^2}{a^2-c^2}$ in a wide range of radii.\\
-
-In general, we find that DM-only halos are shaped with parameters in table \ref{table:DM table}.
-To show this relation is real and not a result of strong peculiarities of particular DM halos, we resume the results of the 30 auriga simulations on the figure \ref{fig: triaxial plane} where each shape represents a point in the triaxiality plane $c/a Vs b/a$.
-Check Vera-ciro onthis.\\
+As a representative sample of this relations, we show on figure \ref{fig:DM relation} the evolution, for a specific halo, of the axial ratios $b/a,c/a$ and the triaxiality parameter $T=\frac{a^2-b^2}{a^2-c^2}$ in a wide range of radii.\\
 
@@
   \label{fig:slices}
+\end{figure}
+
+We found that most halos exhibit a monotonically-increasing somewhat steady tendency of its axial ratios $b/a,c/a$  with radius, which is well exemplified on figure \ref{fig:DM_MHD}.
+There are some special cases in which fluctuations of the local DM density field affects this relation, but in average, this monotonic and steady tendency is clear and can be consulted on table \ref{table:DM table}.
+To ilustrate the average behavior, as well as some peculiarities, we resume the results of the 30 auriga simulations on the figure \ref{fig:Triax_DM} where each shape represents a point in the triaxiality plane $c/a$ Vs $b/a$.
+Check Vera-ciro onthis.\\
+
+\begin{figure}
+\centering
+{\includegraphics[width=0.8\columnwidth]{./pics/halo16.png}}
+\caption{Radial profile for axial ratios and the triaxiality parameter $T=\frac{1-b/a}{1-c/a}$ for halo 16.}
+\label{fig:DM_MHD}
+\end{figure}
+
+\begin{figure}
+  \centering
+ \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_DM.png}
+
+  \hfill
+  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. Errorbar shows median and errors for each sampled radii. }
+  \label{fig:Triax_DM}
 \end{figure}
@@
 
-Concerning MHD halos, the expected tendency is not clear.
-Some studies claim that the DM halo must be oblate, at least in the vicinities of the disk, to ensure its stability.
-However, not much is said about its dependence with radius as these studies focus rather on the effects of baryons on the dynamics of the halo.
-Taking a look at some representative graphics similar to those presented before, \ref{fig:,fig:}, some things are noticeable: first, the halo is almost perfectly oblate around $\approx 10-30$Kpc and second: its axial ratios start decreasing very slowly after $50$ and below $10Kpc$.
-Overall, our results are sumarized on table \ref{MHD table}, where we included some extra measurement at twice the size of the gas disk HalfRad.\\
+Concerning MHD halos, \textit{prescindible?(((the expected tendency is not clear.
+Some studies claim that the DM halo must be oblate, at least in the vicinities of the disk, to ensure its stability \cite{disk stability}.
+However,)))} not much is said about its dependence with radius as previous studies focus rather on the effects of baryons on the dynamics of the halo at fixed radii.
+Examining the representative behaviour of a MHD halo on figure \ref{fig:DM_MHD}, some things are noticeable: first, the DM halo is almost perfectly oblate around $\approx 10-30$Kpc, second, its axial ratio $b/a$ start decreasing very slowly after $50Kpc$ and below $10Kpc$ and third, its axial ratio $c/a$ does not exhibit noticeable change in the whole radial domain.
+(Pass from representative case to averaged values) These results are statistically supported and sumarized on table \ref{MHD table} and figure \ref{fig:Triax_MHD}\\
+
+\begin{figure}
+  \centering
+ \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_MHD.png}
+  \hfill
+  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. Errorbar shows median and errors for each sampled radii. }
+  \label{fig:Triax_MHD}
+\end{figure}
 
@@
 \setlength{\tabcolsep}{3pt}
-\begin{tabular}{l|ccccccc}
- &$R_{1/16}$& $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R_1$ & $R_2$& $R_{Disk}$\\
+\begin{tabular}{l|cccccc}
+ &$R_{1/16}$& $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R_1$ & $R_2$\\
 \hline \hline
-$\bar{q}$&$0.93^{+0.04}_{-0.04}$&$0.95^{+0.03}_{-0.03}$&$0.95^{+0.02}_{-0.05}$&$0.93^{+0.04}_{-0.06}$&$0.93^{+0.04}_{-0.10}$&$0.92^{+0.03}_{-0.09}$&$0.94^{+0.03}_{-0.09}$ \\[0.1cm]
-$\bar{s}$&$0.73^{+0.05}_{-0.09}$&$0.73^{+0.07}_{-0.10}$&$0.73^{+0.08}_{-0.10}$&$0.73^{+0.09}_{-0.08}$&$0.75^{+0.07}_{-0.11}$&$0.74^{+0.07}_{-0.10}$&$0.71^{+0.11}_{-0.06}$ \\[0.1cm]
-$\bar{T}$&$0.31^{+0.15}_{-0.22}$&$0.20^{+0.24}_{-0.12}$&$0.24^{+0.20}_{-0.12}$&$0.30^{+0.26}_{-0.16}$&$0.36^{+0.23}_{-0.23}$&$0.39^{+0.26}_{-0.13}$&$0.24^{+0.37}_{-0.10}$ \\[0.1cm]
+$\bar{q}$&$0.93^{+0.04}_{-0.04}$&$0.95^{+0.03}_{-0.03}$&$0.95^{+0.02}_{-0.05}$&$0.93^{+0.04}_{-0.06}$&$0.93^{+0.04}_{-0.10}$&$0.92^{+0.03}_{-0.09}$ \\[0.1cm]
+$\bar{s}$&$0.73^{+0.05}_{-0.09}$&$0.73^{+0.07}_{-0.10}$&$0.73^{+0.08}_{-0.10}$&$0.73^{+0.09}_{-0.08}$&$0.75^{+0.07}_{-0.11}$&$0.74^{+0.07}_{-0.10}$ \\[0.1cm]
+$\bar{T}$&$0.31^{+0.15}_{-0.22}$&$0.20^{+0.24}_{-0.12}$&$0.24^{+0.20}_{-0.12}$&$0.30^{+0.26}_{-0.16}$&$0.36^{+0.23}_{-0.23}$&$0.39^{+0.26}_{-0.13}$ \\[0.1cm]
 \hline
@@
 
-Talk about source of triaxiality at the inner parts of the halos (bar?).
-This source of triaxiality at the inner parts explains why the axial ratios are $\approx 0.95$ and not exactly $1$.
-We should also discuss that the decrease in the axial ratios for bigger radii may be actually bigger/steeper but it is dimmed by the contribution of inner parts.\\
+\subsection{Comparison with observational constraints}
+To be able to compare our results with observational values, we must relate the calculated quanties with their corresponding isopotential analogue, in which observational constraints are usually presented.
+For this purpose, we run a simple algorithm to find an approximation of the shape of the isopotential contour.
+Here, we calculate the mean and standard deviation of the potential over a spherical shell of width equals to $10\%$ of the radius at which it is sampled.
+Then, we calculate the inertia tensor of particles with potential within $1\sigma$ around the mean potential and calculate its triaxial characterization with the reduced inertia tensor.
+We repeat the process of calculating the potential mean and standard deviation until convergence is achieved with tolerance of $10^{-4}$.
+We repeat this process for the different radii from table \ref{tabe:isopotential}.
+\\
 
-If we compare with obervational values, we must at least take isodensity contours (). We present this comparison  at two different radii for MHD simulations on figure \ref{fig:}. \\
+\begin{table}
+\setlength{\tabcolsep}{3pt}
+\begin{tabular}{l|cccc}
+ & $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R_1$ \\
+\hline \hline
+$\bar{q}$&$0.98^{+0.01}_{-0.02}$&$0.97^{+0.01}_{-0.04}$&$0.96^{+0.03}_{-0.06}$&$0.94^{+0.03}_{-0.07}$ \\[0.1cm]
+$\bar{s}$&$0.89^{+0.04}_{-0.06}$&$0.88^{+0.04}_{-0.04}$&$0.87^{+0.05}_{-0.05}$&$0.85^{+0.05}_{-0.05}$ \\[0.1cm]
+$\bar{T}$&$0.18^{+0.23}_{-0.10}$&$0.36^{+0.19}_{-0.21}$&$0.40^{+0.26}_{-0.20}$&$0.48^{+0.23}_{-0.21}$ \\[0.1cm]
+\hline
+\end{tabular}
+\caption{Median values of isopotential axial ratios $q,s$ and triaxiality parameter $T$ for DM halos in MHD simulations at different radii (columns). }
+\label{tabe:isopotential}
+\end{table}
 
-Little discussion: Are our results congruent with observations? at which radii, does the DM halo shape vary that much?.\\
+As a check of consistency, we compare our new isopotential shape results with the analytic expression of the $(1-q_{\phi})\frac{1}{3}(1-q_{\rho})$ \citep[Binney and Tremaine year]{Binney and tremaine}, taking the volume-enclosed axial ratios as an approximation for the isodensity contour ratios $q_{\rho}$.
+Although this analytic expression if meant to be used for logarithmic axisymmetric halos, it works well as a first approximation for nearly axisymmetric halos as those produced by our disced galaxies.
+We find that the difference between the real and the analytic isopotential axial ratios is not bigger than $quantity percent$.
+With this, we may now present on table \ref{tabe:isopotential} our observationally-comparable results for MHD halos at two important radii one corresponding to the approximate regimes where the MW DM halo is usually constrained.\\
 
-\begin{figure}
-  \centering
- \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_DM.png}
-
-  \hfill
-  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. Errorbar shows median and errors for each sampled radii. }
-  \label{fig:Triax_DM}
-\end{figure}
+Little discussion: Are our results congruent with observations? at which radii, does the DM halo shape vary that much?. Which models are favored?\\
 
@@
 
-\begin{figure}
-\centering
-{\includegraphics[width=0.8\columnwidth]{./pics/halo16.png}}
-\caption{Radial profile for axial ratios and the triaxiality parameter $T=\frac{1-b/a}{1-c/a}$ from halo 16 and halo 16.
-These halos have a clear radial tendence towards sphericity (for smaller radii until $\approx 3$Kpc), which can be confirmed with the triaxiality parameter.
-(Merged Column)}
-\label{fig:DM_MHD}
-\end{figure}
+From the previous characterization of radial shapes it is clear that MHD halos are rounder than DM halos (i.e.
+axial ratios are bigger) at every sampled radii.
+This can be compared on tables \ref{tabe:DM table} and \ref{tabe:MHD table} or at the representative example on figure \ref{fig:DM_MHD}.
+From there, it is also noticeable that the rounding effect of baryons is stronger at the disk regime, where the DM halo is almost perfectly oblate.
+Furthermore, MHD halos tend towards more oblate shapes (T < 0.5) despite DM halos tendency towards more prolate shapes (T>0.5).\\
 
-It is expected etc. show an example? or compare statistics?
-
-\begin{figure}
-  \centering
-  \subfloat[Level4 MHD Vs DM at inner regions]{\includegraphics[width=0.5\columnwidth]{./pics/Triaxial_Plane/Triaxiality_Inner_lvl4.png}}
-  \hfill
-  \subfloat[Level4 MHD Vs DM at outer regions]{\includegraphics[width=0.5\columnwidth]{./pics/Triaxial_Plane/Triaxiality_Outter_lvl4.png}}
-  \hfill
-  \caption{Axial ratios as shown on $c/a$ Vs $b/a$.
-Each dot represents a halo shape at some radius.
-Some observational constraints are plotted alongside our results.
-Here, dots are clustered, proving the general tendence of halos to get rounder on the outer parts.(Optimize space.
-caption replaces title.
-Present constraints representation of density)}
-  \label{fig:Triaxiality_Inner_Outer}
-\end{figure}
+This rounding effect is expected from the gravitational effect of the flattened axisymmetric galactic disk.
+It is also reasonable that this effect is not as strong at $\approx 100$Kpc, where the disk potential is dimmer compared to the DM halo potential.
+Keeping this in mind, one would expect that the rounding effect of baryons is related to some galactic parameters such as its component masses and radii.
+However, even for the parameter of highest correlation with this rounding effect (the baryonic fraction), the relation is not clear nor conclusive due to the dispersion from galaxy peculiarities.
+In figure \ref{fig:Star_Density_effect} we plot the ratios $c/a$ compared to the baryonic fraction of each galaxy.
+Although some linear tendency is suggested qualitatively, the dispersion of the sample is very high to obtain some conclusive relation.
+This is an evidence that adiabatic-contraction models are not realistic as they may neglect some effects of the galaxy evolution in the whole cosmological context.
+\\
 
@@
 
+\textbf{Actually we have not examined the relation of c/a in MHD halos with some measure of c/a from the disk, that is something like Zdisk/Rdisk.
+This actually would make more sense from a physical point of view: effect of the potential.}
+
+Although the effect of the baryonic disk on the shape of the DM halo is a reasonable explanation for the rounding effect, it does not actually explain the deviation from oblateness of MHD halos at $r<10$Kpc.
+In other words, if the disk is perfectly axisymmetric, there must be some source of triaxiality at $r<10$Kpc to explain the low axial ratios.\\
+
+\textit{ Talk about source of triaxiality at the inner parts of the halos (bar?).
+This source of triaxiality at the inner parts explains why the axial ratios are $\approx 0.95$ and not exactly $1$.
+We should also discuss that the decrease in the axial ratios for bigger radii may actually be bigger/steeper but it is dimmed by the contribution of inner parts.}\\
+%
+%\begin{figure}
+%  \centering
+%  \subfloat[Level4 MHD Vs DM at inner regions]{\includegraphics[width=0.5\columnwidth]{./pics/Triaxial_Plane/Triaxiality_Inner_lvl4.png}}
+%  \hfill
+%  \subfloat[Level4 MHD Vs DM at outer regions]{\includegraphics[width=0.5\columnwidth]{./pics/Triaxial_Plane/Triaxiality_Outter_lvl4.png}}
+%  \hfill
+%  \caption{Axial ratios as shown on $c/a$ Vs $b/a$.
+Each dot represents a halo shape at some radius.
+Some observational constraints are plotted alongside our results.
+Here, dots are clustered, proving the general tendence of halos to get rounder on the outer parts.(Optimize space.
+caption replaces title.
+Present constraints representation of density)}
+%  \label{fig:Triaxiality_Inner_Outer}
+%\end{figure}
+
 \subsection{The historical shape}
@@
 It is easy to see that the axial ratios increase with decreasing redshift, which is expected by the continuous influence of the gravitational potential \cite{VeraCiro}.
+In figure \ref{fig:RedshiftGood} we present a representative example.
 \\
-
-Interestingly, these two parametic plots i.e.
-$(b/a,c/a)(z=0,r)$ and $(b/a,c/a)(z,r=R_{vir})$ are very correlated for DM only halos \ref{fig:redshift correlation}.
-This means that, for DM-only halos, one can approximate its shape at the virial radius at higher redshift by simply sampling its current shape at a smaller radius.
-This relationship relies strongly on the steady and monotonous tendency of DM halos towards sphericity for bigger radii and smaller redshift.\\
 
@@
 
-MHD halos, on the other hand, do not exhibit tendency towards sphericity with bigger radii, but they do get sistematically rounder at lower redshift \ref{fig:MHD profile radius and redshift}.
+Interestingly, these two parametic plots i.e.
+$(b/a,c/a)(z=0,r)$ and $(b/a,c/a)(z,r=R_{vir})$ are very correlated for DM-only halos \ref{fig:DM Z Triax}.
+This means that, for DM-only halos, one can approximate its shape at higher redshift by simply sampling its current shape at a smaller radius \textbf{wording}.
+This relationship relies strongly on the steady and monotonous tendency of DM halos towards sphericity for bigger radii and smaller redshift.\\
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{./pics/Redshift/halo_27_DM_Z_correlation.png}
+    \caption{Difference in asphericities between MHD and DM shapes Vs Star Density of the simulation.}
+    \label{fig:DM Z Triax}
+
+\end{figure}
+
+MHD halos, on the other hand, do not exhibit tendency towards sphericity with bigger radii, but they do get sistematically rounder at lower redshift as seen in figure \ref{fig:RedshiftGood}.
 This effectively vanishes this correlation as seen from a DM halo \ref{fig:MHD Z Triax}.\\
 
-Discuss if this correlation may be recovered if compared for example at Disk radius in stead of virial radius.\\
+\begin{figure}
+	\includegraphics[width=\columnwidth]{./pics/Redshift/halo_24_level3_MHD_Z_Triax.png}
+    \caption{Difference in asphericities between MHD and DM shapes Vs Star Density of the simulation.}
+    \label{fig:MHD Z Triax}
+
+\end{figure}
+
+Better graphics.
+
+%Discuss if this correlation may be recovered if compared for example at Disk radius in stead of virial radius.\\
 
 \subsection{The orientation of the principa axes}
-This is an important result of our study.
+
+One of the principal assumptions of observational models of the MW's DM halo is that its minor axis is perfectly aligned with the disk axis.
+Although this is a reasonable assumption to guarantee the stability of the galactic disk in simplified models of isolated galaxies, it may not be the case for galaxies evolved in the whole cosmological context nor at every radii at which the shape is sampled.\\
+
+Therefore, it is of special interest to us to examin the strength of this alignment assumption in the context of simulations.
+For this purpose, we sampled the shape at 5 different radii and plotted the axial directions, as well as the disk direction in the \textbf{name} diagrams \cite{} (explain diagrams).
+Explain disk direction calculation.\\
+
+We found that there is not a representative example of what happens in terms of alignments.
+We found that the majority of the disks are aligned with the minor axis of their DM halo within $\approx 30^o$; in some special cases, this alignment was almost perfect and in some other cases, the DM halo minor axis changed substantially to be able to determine an alignment.
+In figure \ref{fig:alignment} we present these three cases.
+\textbf{occurrencies for each case?}
+
+\textit{This is an important result of our study.
 We study the radial evolution of the principal axes, compared also to the angular momentum vector from the disk.
@@
 Furthermore, the principal axes alignment usually change with radius (rotation, swap, verify).
-This ask for relaxation on the strong constrains on the MW DM halo models.
+This ask for relaxation on the strong constrains on the MW DM halo models.}
 
@@
   \centering
-  \subfloat[Aligned Axes]{\includegraphics[width=1\columnwidth]{./pics/well_axes.png}}
+  \subfloat[Perfectly aligned Axes]{\includegraphics[width=1\columnwidth]{./pics/well_axes.png}}
   \hfill
-  \subfloat[Rotating Axes]{\includegraphics[width=1\columnwidth]{./pics/rotating_axes.png}}
+  \subfloat[Somewhat aligned Axes]{\includegraphics[width=1\columnwidth]{./pics/rotating_axes.png}}
   \hfill
@@
   \caption{Description of axes alignments }
-  \label{fig:slices}
+  \label{fig:alignment}
 \end{figure}
 
+\textbf{Discussion about the distribution of alignments and their evolution in time: Precesion or temporary instabilities?}
+
 \section{Conclusions}
-
-The last numbered section should briefly summarise what has been done, and describe
-the final conclusions which the authors draw from their work.
 
@@
 \section*{Acknowledgements}
-
-The Acknowledgements section is not numbered. Here you can thank helpful
-colleagues, acknowledge funding agencies, telescopes and facilities used etc.
-Try to keep it short.
+This project has received funding from the European Union’s Horizon 2020 Research and Innovation Programme under the Marie Sk\l{}odowska-Curie grant agreement No 734374
 

### 2018-09-10 Paper/paper.tex
updates

--- 2018-08-11 Paper/mnras_template.tex
@@
 \documentclass[a4paper,fleqn,usenatbib]{mnras}
-
-% MNRAS is set in Times font. If you don't have this installed (most LaTeX
-% installations will be fine) or prefer the old Computer Modern fonts, comment
-% out the following line
-\usepackage{newtxtext,newtxmath}
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
-%\usepackage{mathptmx}
-%\usepackage{txfonts}
-
-% Use vector fonts, so it zooms properly in on-screen viewing software
-% Don't change these lines unless you know what you are doing
 \usepackage[T1]{fontenc}
 \usepackage{ae,aecompl}
-
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
 
@@
 \begin{abstract}
-This is a simple template for authors to write new MNRAS papers.
-The abstract should briefly describe the aims, methods, and main results of the paper.
-It should be a single paragraph not more than 250 words (200 words for Letters).
-No references should appear in the abstract.This is a simple template for authors to write new MNRAS papers.
-The abstract should briefly describe the aims, methods, and main results of the paper.
-It should be a single paragraph not more than 250 words (200 words for Letters).
-No references should appear in the abstractThis is a simple template for authors to write new MNRAS papers.
-The abstract should briefly describe the aims, methods, and main results of the paper.
-It should be a single paragraph not more than 250 words (200 words for Letters).
-No references should appear in the abstract
+We measure the shape of the dark matter halos of Milky Way type galaxies.
 \end{abstract}
@@
 
-All papers should start with an Introduction section, which sets the work
-in context, cites relevant earlier studies in the field by \citet{Others2013},
-and describes the problem the authors aim to solve \citep[e.g.][]{Author2012}.\\
+\citep{2011MNRAS.416.1377V}
 
-Introduce/ Motivation simulations, sphereical top hat collapse.\\
+\bibliographystyle{mnras}
+\bibliography{references}
+
+\end{document}
 
@@
 
-%\bibliographystyle{mnras}
-%\bibliography{example} % if your bibtex file is called example.bib
-
 % Alternatively you could enter them by hand, like this:

### 2018-09-14 Paper/paper.tex
some references

@@
 One of the principal predictions of the CDM model is that DM halos are ellipsoidal and very well characterized by the principal axes $a>b>c$.
-This is due, among other causes, to the anisotropical and clumpy accretion of matter influenced by environmental structures \citep[see?][]{environment-shape}.
-The general concensus in numerical simulations \citep[e.g.][]{TriaxialHalos1,TriaxialHalos2,etc} is that halos tend to be prolate with axial ratios b/a ~ \textit{number}, c/a ~ \textit{number} and small differences may arise by the use different methods in numerical recipies for the simulations and the shape-calculation methods  \citep[see][]{Allgood et al.
+This is due, among other causes, to the anisotropical and clumpy accretion of matter influenced by environmental structures \citep[see?][]{Colberg et al.
+1999, Vera-Ciro et al.
+2011}.
+The general concensus in numerical simulations \citep[e.g.][]{Dubinski and Calberg 1991,Hayashi et al.
+2007} is that halos tend to be prolate with axial ratios $\left(b/a\right)_{\rho}$ ~ \textit{number}, $\left(c/a\right)_{\rho}$ ~ \textit{number} and small differences may arise by the use different methods in numerical recipies for the simulations and the shape-calculation methods  \citep[see][]{Allgood et al.
 2006}.
-Some studies have gone a step further as for analyzing the dependence of shape of the DM halo on the radius and redshift \citep[e.g.][]{Shape-radius-papers, including Allgood}, generally finding that halos are rounder at the outerskirts and at lower redshift.\\
+Some studies have gone a step further as for analyzing the dependence of shape of the DM halo on the radius and redshift \citep[e.g.][]{Allgood et al.
+2006,Vera-Ciro et al.
+2011}, generally finding that halos are rounder at the outerskirts and at lower redshift.\\
 
@@
 In the case of the Milky Way, where we have a three-dimensional view from the inside, there seems to be a general agreement for oblate (i.e.
-a=b>c) configurations at small distances around \~ <20kpc \citep[see][]{LM10,Bovy2016,Loebman,Vera-Ciro, RobOllingMerrifield,Bovy,BanerjeeChanda}, and more triaxial and prolate configurations on the outter distances \~>20kpc \citep[see][]{Vera-Ciro,LMJ09,Deg,BanerjeeChanda}.
-However, some studies are inclined towards prolate configurations even at the inner parts of the halo \citep[see][]{BowdenEvansWilliams,Findothers}, and although it previously seemed that a triaxial DM halo on the outerskirts would be necessary to fully explain the characterization of the Sagittarius stream \citep[see][]{LMJ09}, more recent studies put into doubt (question) this claim by reporting inconsistencies with narrow stellar streams \citet{PearsonKupperJohtnston, MoreLikeThis} or finding that the relaxation of other constraints may make this claim unnecessary (wording) \citet{IbataLewisMartin}.\\
+a=b>c) configurations at small distances around \~ <20kpc \citep[see][]{Law_and_Majewski_2010,Bovy2016,Loebman,Vera-Ciro, RobOllingMerrifield,Bovy,BanerjeeChanda}, and more triaxial and prolate configurations on the outter distances \~>20kpc \citep[see][]{Vera-Ciro,Law_and_Majewski_2009,Deg,BanerjeeChanda}.
+However, some studies are inclined towards prolate configurations even at the inner parts of the halo \citep[see][]{BowdenEvansWilliams,Findothers}, and although it previously seemed that a triaxial DM halo on the outerskirts would be necessary to fully explain the characterization of the Sagittarius stream \citep[see][]{Law_and_Majewski_2009}, more recent studies put into doubt (question) this claim by reporting inconsistencies with narrow stellar streams \citet{PearsonKupperJohtnston, MoreLikeThis} or finding that the relaxation of other constraints may make this claim unnecessary (wording) \citet{IbataLewisMartin}.\\
 
@@
 Some studies have shown that to ensure the stability of a hydrodynamical (numeric) disk artificially embeded in a static(non-changing) DM halo, its shape must be axisymmetrical \cite{}.
-Other works have studied this rounding effect by emulating a disk as an adiabatically growing potential inside an N-body triaxial DM halo \cite{Debattista-Moore,Debattista-Roskar, katzantzidis}, finding that (findings of this study -debattista-).
+Other works have studied this rounding effect by emulating a disk as an adiabatically growing potential inside an N-body triaxial DM halo \cite{Debattista_et_al._2008,Debattista-Roskar, katzantzidis}, finding that (findings of this study -debattista-).
 Other works of this type?\\

### 2018-09-17 Paper/paper.tex
More references

@@
 
-One of the principal predictions of the CDM model is that DM halos are ellipsoidal and very well characterized by the principal axes $a>b>c$.
-This is due, among other causes, to the anisotropical and clumpy accretion of matter influenced by environmental structures \citep[see?][]{Colberg et al.
-1999, Vera-Ciro et al.
-2011}.
-The general concensus in numerical simulations \citep[e.g.][]{Dubinski and Calberg 1991,Hayashi et al.
-2007} is that halos tend to be prolate with axial ratios $\left(b/a\right)_{\rho}$ ~ \textit{number}, $\left(c/a\right)_{\rho}$ ~ \textit{number} and small differences may arise by the use different methods in numerical recipies for the simulations and the shape-calculation methods  \citep[see][]{Allgood et al.
-2006}.
-Some studies have gone a step further as for analyzing the dependence of shape of the DM halo on the radius and redshift \citep[e.g.][]{Allgood et al.
-2006,Vera-Ciro et al.
-2011}, generally finding that halos are rounder at the outerskirts and at lower redshift.\\
+One of the principal predictions of the CDM model is that DM halos are ellipsoidal and very well characterized by the principal axes $a>b>c$ \citet{Frenk_et_al._1988}.
+This is due, among other causes, to the anisotropical and clumpy accretion of matter influenced by environmental structures \citep[see?][]{Colberg_et_al._1999,Vera-Ciro_et_al._2011}.
+The general concensus in numerical simulations \citep[e.g.][]{Dubinski_and_Calberg_1991,Hayashi_et_al._2007} is that halos tend to be prolate with axial ratios $\left(b/a\right)_{\rho}$ ~ \textit{number}, $\left(c/a\right)_{\rho}$ ~ \textit{number} and small differences may arise by the use different methods in numerical recipies for the simulations and the shape-calculation methods  \citep[see][]{Allgood_et_al._2006}.
+Some studies have gone a step further as for analyzing the dependence of shape of the DM halo on the radius and redshift \citep[e.g.][]{Allgood_et_al._2006,Vera-Ciro_et_al._2011}, generally finding that halos are rounder at the outerskirts and at lower redshift.\\
 
@@
 In the case of the Milky Way, where we have a three-dimensional view from the inside, there seems to be a general agreement for oblate (i.e.
-a=b>c) configurations at small distances around \~ <20kpc \citep[see][]{Law_and_Majewski_2010,Bovy2016,Loebman,Vera-Ciro, RobOllingMerrifield,Bovy,BanerjeeChanda}, and more triaxial and prolate configurations on the outter distances \~>20kpc \citep[see][]{Vera-Ciro,Law_and_Majewski_2009,Deg,BanerjeeChanda}.
-However, some studies are inclined towards prolate configurations even at the inner parts of the halo \citep[see][]{BowdenEvansWilliams,Findothers}, and although it previously seemed that a triaxial DM halo on the outerskirts would be necessary to fully explain the characterization of the Sagittarius stream \citep[see][]{Law_and_Majewski_2009}, more recent studies put into doubt (question) this claim by reporting inconsistencies with narrow stellar streams \citet{PearsonKupperJohtnston, MoreLikeThis} or finding that the relaxation of other constraints may make this claim unnecessary (wording) \citet{IbataLewisMartin}.\\
+a=b>c) configurations at small distances around \~ $<20kpc$ \citep[see][]{Olling_and_Merrifield_2000,Law_and_Majewski_2010,Loebman_et_al._2012,Vera-Ciro_and_Helmi_2013,Bovy_et_el._2016}, and more triaxial and prolate configurations on the outter distances \~>20kpc \citep[see][]{Law_and_Majewski_2009,Banerjee_and_Chanda_2011,Deg_and_Widrow_2013,Vera-Ciro_and_Helmi_2013}.
+However, some studies are inclined towards prolate configurations even at the inner parts of the halo \citep[see][]{Bowden_et_al._2016,Findothers}, and although it previously seemed that a triaxial DM halo on the outerskirts would be necessary to fully explain the characterization of the Sagittarius stream \citep[see][]{Law_and_Majewski_2009}, more recent studies put into doubt (question) this claim by reporting inconsistencies with narrow stellar streams \citet{Pearson_et_al._2015, MoreLikeThis} or finding that the relaxation of other constraints may make this claim unnecessary (wording) \citet{Ibata_et_al._2013}.\\
 
 Although observations predict more symmetric halos than DM-only simulations, there is strong evidence claiming that the presence of baryons need/make more axisymmetrical halos.
-Some studies have shown that to ensure the stability of a hydrodynamical (numeric) disk artificially embeded in a static(non-changing) DM halo, its shape must be axisymmetrical \cite{}.
+Some studies have shown that to ensure the stability of a hydrodynamical (numeric) disk artificially embeded in a static(non-changing) DM halo, its shape must be axisymmetrical \cite{Scannapieco_et_al._2009,Yurin_and_Springel_2015}.
 Other works have studied this rounding effect by emulating a disk as an adiabatically growing potential inside an N-body triaxial DM halo \cite{Debattista_et_al._2008,Debattista-Roskar, katzantzidis}, finding that (findings of this study -debattista-).

### 2018-09-18 Paper/paper.tex
Bib complete for now

@@
 Some studies have shown that to ensure the stability of a hydrodynamical (numeric) disk artificially embeded in a static(non-changing) DM halo, its shape must be axisymmetrical \cite{Scannapieco_et_al._2009,Yurin_and_Springel_2015}.
-Other works have studied this rounding effect by emulating a disk as an adiabatically growing potential inside an N-body triaxial DM halo \cite{Debattista_et_al._2008,Debattista-Roskar, katzantzidis}, finding that (findings of this study -debattista-).
+Other works have studied this rounding effect by emulating a disk as an adiabatically growing potential inside an N-body triaxial DM halo \cite{Debattista_et_al._2008,Kazantzidis_et_al._2010,Debattista_et_al._2013}, finding that (findings of this study -debattista-).
 Other works of this type?\\
@@
 While these studies are elucidating about dynamical aspects that may play important roles in the rounding of the DM halo shape, they do not follow baryons in the whole cosmological context.
-Abadi-Navarro and Bryan-Kay studied the evolution of galaxies in hydrodynamical simulations with restricted models of feedback \cite{Abadi-Navarro,Bryan-Kay} finding that the galaxy formation efficiency \cite{Abadi} and the history of formation may also determine the extent of this rounding.\\
+Abadi et al.
+and Bryan et al.
+studied the evolution of galaxies in hydrodynamical simulations with restricted models of feedback \cite{Abadi_et_al._2010,Bryan_et_al._2013} finding that the galaxy formation efficiency \cite{Abadi} and the history of formation may also determine the extent of this rounding.\\
 
@@
 There is no trivial way to calculate the DM halo shape at a determined radius due to the discretization of particles.
-For practical effects, observational models focus on the shape of the DM isopotential \cite{isopotential} or isodensity \cite{isodensity} contours.
+For practical effects, observational models focus on the shape of the DM isopotential \cite{Law_and_Majewski_2010} or isodensity \cite{Loebman_et_al._2012} contours.
 In cosmological simulations, it is preferred to work with the isodensity contours which is directly calculated from particle positions.
@@
 For this reason we determine the shape taking into account volume-enclosed particles, rather than shell-enclosed.
-While this approach allows the cumulative influence of outter shells on the outter shapes, it has been demonstrated for DM-only simulations that this effect becomes important only for big radii \cite{vera-Ciro aquarius}.
+While this approach allows the cumulative influence of outter shells on the outter shapes, it has been demonstrated for DM-only simulations that this effect becomes important only for big radii \cite{Vera-Ciro_et_al._2011}.
 We therefore follow the method of \cite[Allgood et al.
@@
 To have a more complete picture about the effect of baryons on the DM halo shape, we begin by verifying/understanding the radial evolution (dependence?) of the shape.
-In the case of DM-only simulations, it is expected that halos get monotonically rounder at larger radii due to (the gravitational effect of inner shells?) \citep{Vera-Ciro et al.
-2012}.
+In the case of DM-only simulations, it is expected that halos get monotonically rounder at larger radii due to (the gravitational effect of inner shells?) \citep{Vera-Ciro_et_al._2012}.
 A graphic example of this rounding can be checked on figure \ref{fig:slices}, where we plot the a projection of a DM-only halo aligned with the calculated minor axis at two different radius together with the estimated projected ellipsoidal.
@@
 
-As a check of consistency, we compare our new isopotential shape results with the analytic expression of the $(1-q_{\phi})\frac{1}{3}(1-q_{\rho})$ \citep[Binney and Tremaine year]{Binney and tremaine}, taking the volume-enclosed axial ratios as an approximation for the isodensity contour ratios $q_{\rho}$.
+As a check of consistency, we compare our new isopotential shape results with the analytic expression of the $(1-q_{\phi})\frac{1}{3}(1-q_{\rho})$ \citep[Binney and Tremaine 2008]{Binney_and_Tremaine_2008}, taking the volume-enclosed axial ratios as an approximation for the isodensity contour ratios $q_{\rho}$.
 Although this analytic expression if meant to be used for logarithmic axisymmetric halos, it works well as a first approximation for nearly axisymmetric halos as those produced by our disced galaxies.

### 2018-09-18 Paper/paper.tex
edit paper

--- 2018-09-14 Paper/paper.tex
@@
 
-%This is a simple template for authors to write new MNRAS papers.
-%See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
-%for a full user guide.
+A robust prediction of the Cold Dark Matter (CDM) model is that DM
+halos are ellipsoidal and can be characterized by the principal axes
+$a>b>c$.  
+The ellipsoidal shape is mostly due to the anisotropical and
+clumpy accretion of matter influenced by environmental structures.
 
-\citep{2011MNRAS.416.1377V}
+The general concensus in numerical simulations is that halos tend to
+be prolate with axial ratios b/a ~ \textit{number}, $c/a$
+~ \textit{number} and small differences may arise by the use different
+methods in numerical recipies for the simulations and the
+shape-calculation methods  \citep{Allgood_et_al._2006}. Some
+studies have gone a step further as for analyzing the dependence of
+shape of the DM halo on the radius and redshift
+\citep[e.g.][]{Allgood_et_al._2006}, generally
+finding that halos are rounder at the outerskirts and at lower
+redshift.
+
+\citep{Vera-Ciro_et_al._2011}
 
@@
 \end{document}
-
-One of the principal predictions of the CDM model is that DM halos are ellipsoidal and very well characterized by the principal axes $a>b>c$.
-This is due, among other causes, to the anisotropical and clumpy accretion of matter influenced by environmental structures \citep[see?][]{Colberg et al.
-1999, Vera-Ciro et al.
-2011}.
-The general concensus in numerical simulations \citep[e.g.][]{Dubinski and Calberg 1991,Hayashi et al.
-2007} is that halos tend to be prolate with axial ratios $\left(b/a\right)_{\rho}$ ~ \textit{number}, $\left(c/a\right)_{\rho}$ ~ \textit{number} and small differences may arise by the use different methods in numerical recipies for the simulations and the shape-calculation methods  \citep[see][]{Allgood et al.
-2006}.
-Some studies have gone a step further as for analyzing the dependence of shape of the DM halo on the radius and redshift \citep[e.g.][]{Allgood et al.
-2006,Vera-Ciro et al.
-2011}, generally finding that halos are rounder at the outerskirts and at lower redshift.\\
 
@@
 In the case of the Milky Way, where we have a three-dimensional view from the inside, there seems to be a general agreement for oblate (i.e.
-a=b>c) configurations at small distances around \~ <20kpc \citep[see][]{Law_and_Majewski_2010,Bovy2016,Loebman,Vera-Ciro, RobOllingMerrifield,Bovy,BanerjeeChanda}, and more triaxial and prolate configurations on the outter distances \~>20kpc \citep[see][]{Vera-Ciro,Law_and_Majewski_2009,Deg,BanerjeeChanda}.
-However, some studies are inclined towards prolate configurations even at the inner parts of the halo \citep[see][]{BowdenEvansWilliams,Findothers}, and although it previously seemed that a triaxial DM halo on the outerskirts would be necessary to fully explain the characterization of the Sagittarius stream \citep[see][]{Law_and_Majewski_2009}, more recent studies put into doubt (question) this claim by reporting inconsistencies with narrow stellar streams \citet{PearsonKupperJohtnston, MoreLikeThis} or finding that the relaxation of other constraints may make this claim unnecessary (wording) \citet{IbataLewisMartin}.\\
+a=b>c) configurations at small distances around \~ <20kpc \citep[see][]{LM10,Bovy2016,Loebman,Vera-Ciro, RobOllingMerrifield,Bovy,BanerjeeChanda}, and more triaxial and prolate configurations on the outter distances \~>20kpc \citep[see][]{Vera-Ciro,LMJ09,Deg,BanerjeeChanda}.
+However, some studies are inclined towards prolate configurations even at the inner parts of the halo \citep[see][]{BowdenEvansWilliams,Findothers}, and although it previously seemed that a triaxial DM halo on the outerskirts would be necessary to fully explain the characterization of the Sagittarius stream \citep[see][]{LMJ09}, more recent studies put into doubt (question) this claim by reporting inconsistencies with narrow stellar streams \citet{PearsonKupperJohtnston, MoreLikeThis} or finding that the relaxation of other constraints may make this claim unnecessary (wording) \citet{IbataLewisMartin}.\\
 
@@
 Some studies have shown that to ensure the stability of a hydrodynamical (numeric) disk artificially embeded in a static(non-changing) DM halo, its shape must be axisymmetrical \cite{}.
-Other works have studied this rounding effect by emulating a disk as an adiabatically growing potential inside an N-body triaxial DM halo \cite{Debattista_et_al._2008,Debattista-Roskar, katzantzidis}, finding that (findings of this study -debattista-).
+Other works have studied this rounding effect by emulating a disk as an adiabatically growing potential inside an N-body triaxial DM halo \cite{Debattista-Moore,Debattista-Roskar, katzantzidis}, finding that (findings of this study -debattista-).
 Other works of this type?\\

### 2018-09-18 Paper/paper.tex
edit

@@
 clumpy accretion of matter influenced by environmental structures. 
-
-The general concensus in numerical simulations is that halos tend to
-be prolate with axial ratios b/a ~ \textit{number}, $c/a$
-~ \textit{number} and small differences may arise by the use different
-methods in numerical recipies for the simulations and the
-shape-calculation methods  \citep{Allgood_et_al._2006}. Some
-studies have gone a step further as for analyzing the dependence of
-shape of the DM halo on the radius and redshift
-\citep[e.g.][]{Allgood_et_al._2006}, generally
-finding that halos are rounder at the outerskirts and at lower
-redshift.
-
-\citep{Vera-Ciro_et_al._2011}
+The shape has a strong mass dependence \citep{Allgood_et_al._2006}. 
+The general consensus from numerical studies is that Milky Way type
+halos tend to be prolate with axial ratios $b/a\approx X$ and  $c/a\approx X$, 
+Halos are also found to be rounder at the outerskirts and at lower
+redshifts.
 
@@
 
-Due to the evasive nature of DM, properly constraining the shape of DM halos is a very difficult endeavour.\\
-
-Better connector with observations of distant galaxies.
-Gravitational lensing and star tracers.
-(Talk about discrepancy with simulations, perhaps later) and state that the preference for axisymmetrical shapes may arise from the observational restrictions (projection) look for citations about this .\\
+Better connector with observations of distant galaxies. Gravitational
+lensing and star tracers. (Talk about discrepancy with simulations,
+perhaps later) and state that the preference for axisymmetrical shapes
+may arise from the observational restrictions (projection) look for
+citations about this .\\
 

### 2018-09-18 Paper/paper.tex
edit

@@
 
-A robust prediction of the Cold Dark Matter (CDM) model is that DM
+A robust prediction of the Cold Dark Matter (CDM) paradigm is that DM
 halos are ellipsoidal and can be characterized by the principal axes
 $a>b>c$.
-The ellipsoidal shape is mostly due to the anisotropical and
+This ellipsoidal shape is mostly due to the anisotropical and
 clumpy accretion of matter influenced by environmental structures. 
-The shape has a strong mass dependence \citep{Allgood_et_al._2006}. 
-The general consensus from numerical studies is that Milky Way type
-halos tend to be prolate with axial ratios $b/a\approx X$ and  $c/a\approx X$, 
-Halos are also found to be rounder at the outerskirts and at lower
-redshifts.
+Numerical studies how that the shape has a strong mass dependence
+\citep{Allgood_et_al._2006}, halos are also rounder at the outerskirts
+than at the inner part. Shape also evolves with cosmic time, halos get
+rounder as they evolve.
+
+In the case of the Milky Way, where we have a three-dimensional view
+from the inside, we do not have a clear agreement. 
+Some studies prefer oblate (i.e. a=b>c) configurations at small
+distances around $\leq 20$ kpc \citep[see][]{Law_and_Majewski_2010,Bovy_et_el._2016,Loebman_et_al._2012,Olling_and_Merrifield_2000,Banerjee_and_Chanda_2011}
+and more triaxial and prolate configurations on the outter distances
+$\geq 20$ kpc 
+\citep[see][]{Vera-Ciro_and_Helmi_2013,Law_and_Majewski_2009,Deg_and_Widrow_2013,Banerjee_and_Chanda_2011}.
+However,
+some 
+studies are inclined towards prolate configurations even at the inner
+parts of the halo \citep[see][]{Bowden_et_al._2016}, and
+although it previously seemed that a triaxial DM halo on the
+outerskirts would be necessary to fully explain the characterization
+of the Sagittarius stream \citep[see][]{LMJ09}, more recent studies
+put into doubt (question) this claim by reporting inconsistencies with
+narrow stellar streams \citet{PearsonKupperJohtnston, MoreLikeThis} or
+finding that the relaxation of other constraints may make this claim
+unnecessary (wording) \citet{IbataLewisMartin}.
+
+%Better connector with observations of distant galaxies. Gravitational
+%lensing and star tracers. (Talk about discrepancy with simulations,
+%perhaps later) and state that the preference for axisymmetrical shapes
+%may arise from the observational restrictions (projection) look for
+%citations about this.
 
@@
 \end{document}
-
-Better connector with observations of distant galaxies. Gravitational
-lensing and star tracers. (Talk about discrepancy with simulations,
-perhaps later) and state that the preference for axisymmetrical shapes
-may arise from the observational restrictions (projection) look for
-citations about this .\\
-
-In the case of the Milky Way, where we have a three-dimensional view from the inside, there seems to be a general agreement for oblate (i.e.
-a=b>c) configurations at small distances around \~ <20kpc \citep[see][]{LM10,Bovy2016,Loebman,Vera-Ciro, RobOllingMerrifield,Bovy,BanerjeeChanda}, and more triaxial and prolate configurations on the outter distances \~>20kpc \citep[see][]{Vera-Ciro,LMJ09,Deg,BanerjeeChanda}.
-However, some studies are inclined towards prolate configurations even at the inner parts of the halo \citep[see][]{BowdenEvansWilliams,Findothers}, and although it previously seemed that a triaxial DM halo on the outerskirts would be necessary to fully explain the characterization of the Sagittarius stream \citep[see][]{LMJ09}, more recent studies put into doubt (question) this claim by reporting inconsistencies with narrow stellar streams \citet{PearsonKupperJohtnston, MoreLikeThis} or finding that the relaxation of other constraints may make this claim unnecessary (wording) \citet{IbataLewisMartin}.\\
 

### 2018-09-18 Paper/paper.tex
edit

@@
 In the case of the Milky Way, where we have a three-dimensional view
-from the inside, we do not have a clear agreement. 
+from the inside, the community does not have a clear agreement. 
 Some studies prefer oblate (i.e. a=b>c) configurations at small
-distances around $\leq 20$ kpc \citep[see][]{Law_and_Majewski_2010,Bovy_et_el._2016,Loebman_et_al._2012,Olling_and_Merrifield_2000,Banerjee_and_Chanda_2011}
+distances around $\leq 20$ kpc
+\citep[see][]{Law_and_Majewski_2010,Bovy_et_el._2016,Loebman_et_al._2012,Olling_and_Merrifield_2000,Banerjee_and_Chanda_2011} 
 and more triaxial and prolate configurations on the outter distances
@@
 \citep[see][]{Vera-Ciro_and_Helmi_2013,Law_and_Majewski_2009,Deg_and_Widrow_2013,Banerjee_and_Chanda_2011}.
-However,
-some 
-studies are inclined towards prolate configurations even at the inner
+
+However, some  studies are inclined towards prolate configurations even at the inner
 parts of the halo \citep[see][]{Bowden_et_al._2016}, and
@@
 outerskirts would be necessary to fully explain the characterization
-of the Sagittarius stream \citep[see][]{LMJ09}, more recent studies
-put into doubt (question) this claim by reporting inconsistencies with
-narrow stellar streams \citet{PearsonKupperJohtnston, MoreLikeThis} or
-finding that the relaxation of other constraints may make this claim
-unnecessary (wording) \citet{IbataLewisMartin}.
+of the Sagittarius stream \citep{Law_and_Majewski_2009}, recent studies
+questioned this claim by reporting inconsistencies with narrow stellar
+streams \citet{Pearson_et_al._2015} or finding that
+the relaxation of other constraints may make this claim unnecessary
+\citet{Ibata_et_al._2013}.
 

### 2018-09-18 Paper/paper.tex
column width

@@
 
-Although observations predict more symmetric halos than DM-only simulations, there is strong evidence claiming that the presence of baryons need/make more axisymmetrical halos.
-Some studies have shown that to ensure the stability of a hydrodynamical (numeric) disk artificially embeded in a static(non-changing) DM halo, its shape must be axisymmetrical \cite{}.
-Other works have studied this rounding effect by emulating a disk as an adiabatically growing potential inside an N-body triaxial DM halo \cite{Debattista-Moore,Debattista-Roskar, katzantzidis}, finding that (findings of this study -debattista-).
-Other works of this type?\\
+Although observations predict more symmetric halos than DM-only
+simulations, there is strong evidence claiming that the presence of
+baryons need/make more axisymmetrical halos. Some studies have shown
+that to ensure the stability of a hydrodynamical (numeric) disk
+artificially embeded in a static(non-changing) DM halo, its shape must
+be axisymmetrical \cite{}. Other works have studied this rounding
+effect by emulating a disk as an adiabatically growing potential
+inside an N-body triaxial DM halo
+\cite{Debattista-Moore,Debattista-Roskar, katzantzidis}, finding that
+(findings of this study -debattista-). Other works of this type?
 
-While these studies are elucidating about dynamical aspects that may play important roles in the rounding of the DM halo shape, they do not follow baryons in the whole cosmological context.
-Abadi-Navarro and Bryan-Kay studied the evolution of galaxies in hydrodynamical simulations with restricted models of feedback \cite{Abadi-Navarro,Bryan-Kay} finding that the galaxy formation efficiency \cite{Abadi} and the history of formation may also determine the extent of this rounding.\\
+While these studies are elucidating about dynamical aspects that may
+play important roles in the rounding of the DM halo shape, they do not
+follow baryons in the whole cosmological context. Abadi-Navarro and
+Bryan-Kay studied the evolution of galaxies in hydrodynamical
+simulations with restricted models of feedback
+\cite{Abadi-Navarro,Bryan-Kay} finding that the galaxy formation
+efficiency \cite{Abadi} and the history of formation may also
+determine the extent of this rounding.
 
-In general, there is much to be known about the specifics of the rounding effec of baryons.
-(There are have been no realistic simulations of MW-like galaxies to a resolution/realism that allows us to obtain stronger conslusions)
+In general, there is much to be known about the specifics of the
+rounding effec of baryons. (There are have been no realistic
+simulations of MW-like galaxies to a resolution/realism that allows us
+to obtain stronger conslusions)
 
-In this work, we analyze the Auriga simulations wich etc, where we can analyze the effect baryons together with galactic features, that are involved in the shaping of the DM halo shape of realistic MW-like galaxies.
+In this work, we analyze the Auriga simulations wich etc, where we can
+analyze the effect baryons together with galactic features, that are
+involved in the shaping of the DM halo shape of realistic MW-like
+galaxies.
 
 \section{Numerical Simulations}
-In this work we use the results of the state-of-the art Auriga simulations \cite{auriga}.
-It selected a set of 30 isolated halos from the Evolution and Assembly of GaLaxies and their Environments (EAGLE) project \cite{Eagle}.
-Each halo was identified with the algorithm "Friend of Friends" (FOF) \cite{Davis_et_al._1985}, which recursively links particles if they are closer than some threshold distance referred as linking length.
-EAGLE follows the evolution of fixed-mass particles of $m_{\text{DM}} = 1.15\cdot 10^7\text{M}_{\odot}$ from $z=127$ to $z=0$, adopting the $\Lambda$CDM model from the \cite[Planck Collaboration et al.
-(2014)]{Planck_Collaboration_2014}, which is characterized by $\Omega_\Lambda=0.693$, $\Omega_\text{m}=0.307$, $\Omega_\text{b}=0.048$ \& $\text{H}_0=67.77\text{kms} ^{-1}\text{Mpc}^{-1}$.
+In this work we use the results of the state-of-the art Auriga
+simulations \cite{auriga}. It selected a set of 30 isolated halos from
+the Evolution and Assembly of GaLaxies and their Environments (EAGLE)
+project \cite{Eagle}. Each halo was identified with the algorithm
+"Friend of Friends" (FOF) \cite{Davis_et_al._1985}, which recursively
+links particles if they are closer than some threshold distance
+referred as linking length. EAGLE follows the evolution of fixed-mass
+particles of $m_{\text{DM}} = 1.15\cdot 10^7\text{M}_{\odot}$ from
+$z=127$ to $z=0$, adopting the $\Lambda$CDM model from the
+\cite[Planck Collaboration et al. (2014)]{Planck_Collaboration_2014},
+which is characterized by $\Omega_\Lambda=0.693$,
+$\Omega_\text{m}=0.307$, $\Omega_\text{b}=0.048$ \&
+$\text{H}_0=67.77\text{kms} ^{-1}\text{Mpc}^{-1}$.
 
-These halos were randomly selected from a sample of the most isolated quartile of halos whose virial mass $M_{200}$ varied between $10^{12}M_\odot$ and $2\cdot 10^{12}M_\odot$.
-\textbf{\tiny This mass is defined as the mass enclosed within the virial radius $R_{200}$ at which the density becomes 200 times the critical density of the universe.
-\huge FOOTNOTE \normalsize}.
-These halos were re-simulated with the (AREPOOO HERE) by increasing the mass resolution of the particles belonging to them and diminishing the resolution of the rest of the particles.\\
+These halos were randomly selected from a sample of the most isolated
+quartile of halos whose virial mass $M_{200}$ varied between
+$10^{12}M_\odot$ and $2\cdot 10^{12}M_\odot$. \textbf{\tiny This mass
+  is defined as the mass enclosed within the virial radius $R_{200}$
+  at which the density becomes 200 times the critical density of the
+  universe. \huge FOOTNOTE \normalsize}. These halos were re-simulated
+with the (AREPOOO HERE) by increasing the mass resolution of the
+particles belonging to them and diminishing the resolution of the rest
+of the particles.
 
-Various versions of each halo were modelled with different degrees of realism.
-All 30 halos were simulated within a level-4-degree of resolution defined for Aquarius simulations corresponding to $\tilde 3\cdot 10^6$ high resolution particles of $\tilde 2.5 \cdot 10^5 M_\odot$.
-The principal details of each of these halos are consigned on the table \ref{tab:level4}.
-From these halos, 6 of them where re-simulated at level 3 (higher) resolution taking into account a spatial factor of 2 in each dimension.
-For more information about level 3 halos, their details are printed on table \ref{tab:level3}.
-Furthermore, fore each halo in each level of resolution there are two versions of the simulation.
-One of tracks the evolution of DM-only particles while the remaining one evolves DM and baryions with magneto-hydrodynamical (MHD) physics, including DM.\\
+Various versions of each halo were modelled with different degrees of
+realism. All 30 halos were simulated within a level-4-degree of
+resolution defined for Aquarius simulations corresponding to $\tilde
+3\cdot 10^6$ high resolution particles of $\tilde 2.5 \cdot 10^5
+M_\odot$. The principal details of each of these halos are consigned
+on the table \ref{tab:level4}. From these halos, 6 of them where
+re-simulated at level 3 (higher) resolution taking into account a
+spatial factor of 2 in each dimension. For more information about
+level 3 halos, their details are printed on table
+\ref{tab:level3}. Furthermore, fore each halo in each level of
+resolution there are two versions of the simulation. One of tracks the
+evolution of DM-only particles while the remaining one evolves DM and
+baryions with magneto-hydrodynamical (MHD) physics, including DM.
 
@@
 
-There is no trivial way to calculate the DM halo shape at a determined radius due to the discretization of particles.
-For practical effects, observational models focus on the shape of the DM isopotential \cite{isopotential} or isodensity \cite{isodensity} contours.
-In cosmological simulations, it is preferred to work with the isodensity contours which is directly calculated from particle positions.
-However, these density contours are not smooth and are very sensitive to the presence of small satelites \cite{Springel Isodensity}.
-For this reason we determine the shape taking into account volume-enclosed particles, rather than shell-enclosed.
-While this approach allows the cumulative influence of outter shells on the outter shapes, it has been demonstrated for DM-only simulations that this effect becomes important only for big radii \cite{vera-Ciro aquarius}.
-We therefore follow the method of \cite[Allgood et al.
-2006]{Allgood_et_al._2006} that consits in the use of the reduced inertia tensor,   \\
+There is no trivial way to calculate the DM halo shape at a determined
+radius due to the discretization of particles. For practical effects,
+observational models focus on the shape of the DM isopotential
+\cite{isopotential} or isodensity \cite{isodensity} contours. In
+cosmological simulations, it is preferred to work with the isodensity
+contours which is directly calculated from particle
+positions. However, these density contours are not smooth and are very
+sensitive to the presence of small satelites \cite{Springel
+  Isodensity}. For this reason we determine the shape taking into
+account volume-enclosed particles, rather than shell-enclosed. While
+this approach allows the cumulative influence of outter shells on the
+outter shapes, it has been demonstrated for DM-only simulations that
+this effect becomes important only for big radii \cite{vera-Ciro
+  aquarius}.  We therefore follow the method of \cite[Allgood et
+  al. 2006]{Allgood_et_al._2006} that consits in the use of the
+reduced inertia tensor,
 
@@
 
-The diagonalization of this tensor yields the principal axes of the structure as well as the eigen-quantities which are proportional to the squared principal axes $a>b>c$.
-We start our calculations taking into account particles within a sphere of radius $R$ and then recharacterize the triaxial parameters by taking into account particles within an ellipsoid of semi-axes $r,r/q,r/s$ and weighted distance $d^2=x^2+(y/q)^2+(z/s)^2$, where ere $q = b/a$ and $s=c/a$ are the previously calculated axial ratios.
-We repeat this process until the average deviation of semi-axes is less than $10^{-6}$.\\
+The diagonalization of this tensor yields the principal axes of the
+structure as well as the eigen-quantities which are proportional to
+the squared principal axes $a>b>c$. We start our calculations taking
+into account particles within a sphere of radius $R$ and then
+recharacterize the triaxial parameters by taking into account
+particles within an ellipsoid of semi-axes $r,r/q,r/s$ and weighted
+distance $d^2=x^2+(y/q)^2+(z/s)^2$, where ere $q = b/a$ and $s=c/a$
+are the previously calculated axial ratios. We repeat this process
+until the average deviation of semi-axes is less than $10^{-6}$.
 
 \section{Results}
-For convergence reasons and seeking to make our results observation-comparable, we restrict the sampling of the ellipsoidal parameters to radii between $1/16 R_{vir} and 2R_{vir}$ of the virial radius $R_{500}$, defined as the (DEFINITION OF VIRIAL RADIUS).
-All our results make use of this reference radius unless strictly stated otherwise.\\
+For convergence reasons and seeking to make our results
+observation-comparable, we restrict the sampling of the ellipsoidal
+parameters to radii between $1/16 R_{vir} and 2R_{vir}$ of the virial
+radius $R_{500}$, defined as the (DEFINITION OF VIRIAL RADIUS). All
+our results make use of this reference radius unless strictly stated
+otherwise.
 
 \subsection{The radial tendency of axial ratios}
-To have a more complete picture about the effect of baryons on the DM halo shape, we begin by verifying/understanding the radial evolution (dependence?) of the shape.
-In the case of DM-only simulations, it is expected that halos get monotonically rounder at larger radii due to (the gravitational effect of inner shells?) \citep{Vera-Ciro et al.
-2012}.
-A graphic example of this rounding can be checked on figure \ref{fig:slices}, where we plot the a projection of a DM-only halo aligned with the calculated minor axis at two different radius together with the estimated projected ellipsoidal.
-Formally, this effect is reflected in the axial ratios $b/a,c/a$, which tend to unity on the outerskirts of the halo.
-As a representative sample of this relations, we show on figure \ref{fig:DM relation} the evolution, for a specific halo, of the axial ratios $b/a,c/a$ and the triaxiality parameter $T=\frac{a^2-b^2}{a^2-c^2}$ in a wide range of radii.\\
+To have a more complete picture about the effect of baryons on the DM
+halo shape, we begin by verifying/understanding the radial evolution
+(dependence?) of the shape. In the case of DM-only simulations, it is
+expected that halos get monotonically rounder at larger radii due to
+(the gravitational effect of inner shells?) \citep{Vera-Ciro et
+  al. 2012}. A graphic example of this rounding can be checked on
+figure \ref{fig:slices}, where we plot the a projection of a DM-only
+halo aligned with the calculated minor axis at two different radius
+together with the estimated projected ellipsoidal. Formally, this
+effect is reflected in the axial ratios $b/a,c/a$, which tend to unity
+on the outerskirts of the halo. As a representative sample of this
+relations, we show on figure \ref{fig:DM relation} the evolution, for
+a specific halo, of the axial ratios $b/a,c/a$ and the triaxiality
+parameter $T=\frac{a^2-b^2}{a^2-c^2}$ in a wide range of radii.
 
@@
 
-We found that most halos exhibit a monotonically-increasing somewhat steady tendency of its axial ratios $b/a,c/a$  with radius, which is well exemplified on figure \ref{fig:DM_MHD}.
-There are some special cases in which fluctuations of the local DM density field affects this relation, but in average, this monotonic and steady tendency is clear and can be consulted on table \ref{table:DM table}.
-To ilustrate the average behavior, as well as some peculiarities, we resume the results of the 30 auriga simulations on the figure \ref{fig:Triax_DM} where each shape represents a point in the triaxiality plane $c/a$ Vs $b/a$.
-Check Vera-ciro onthis.\\
+We found that most halos exhibit a monotonically-increasing somewhat
+steady tendency of its axial ratios $b/a,c/a$  with radius, which is
+well exemplified on figure \ref{fig:DM_MHD}. There are some special
+cases in which fluctuations of the local DM density field affects this
+relation, but in average, this monotonic and steady tendency is clear
+and can be consulted on table \ref{table:DM table}. To ilustrate the
+average behavior, as well as some peculiarities, we resume the results
+of the 30 auriga simulations on the figure \ref{fig:Triax_DM} where
+each shape represents a point in the triaxiality plane $c/a$ Vs
+$b/a$. Check Vera-ciro onthis.
 
@@
 
-Concerning MHD halos, \textit{prescindible?(((the expected tendency is not clear.
-Some studies claim that the DM halo must be oblate, at least in the vicinities of the disk, to ensure its stability \cite{disk stability}.
-However,)))} not much is said about its dependence with radius as previous studies focus rather on the effects of baryons on the dynamics of the halo at fixed radii.
-Examining the representative behaviour of a MHD halo on figure \ref{fig:DM_MHD}, some things are noticeable: first, the DM halo is almost perfectly oblate around $\approx 10-30$Kpc, second, its axial ratio $b/a$ start decreasing very slowly after $50Kpc$ and below $10Kpc$ and third, its axial ratio $c/a$ does not exhibit noticeable change in the whole radial domain.
-(Pass from representative case to averaged values) These results are statistically supported and sumarized on table \ref{MHD table} and figure \ref{fig:Triax_MHD}\\
+Concerning MHD halos, \textit{prescindible?(((the expected tendency is
+  not clear. Some studies claim that the DM halo must be oblate, at
+  least in the vicinities of the disk, to ensure its stability
+  \cite{disk stability}. However,)))} not much is said about its
+dependence with radius as previous studies focus rather on the effects
+of baryons on the dynamics of the halo at fixed radii. Examining the
+representative behaviour of a MHD halo on figure \ref{fig:DM_MHD},
+some things are noticeable: first, the DM halo is almost perfectly
+oblate around $\approx 10-30$Kpc, second, its axial ratio $b/a$ start
+decreasing very slowly after $50Kpc$ and below $10Kpc$ and third, its
+axial ratio $c/a$ does not exhibit noticeable change in the whole
+radial domain. (Pass from representative case to averaged values)
+These results are statistically supported and sumarized on table
+\ref{MHD table} and figure \ref{fig:Triax_MHD}
 
@@
   \hfill
-  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. Errorbar shows median and errors for each sampled radii. }
+  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. Errorbar
+    shows median and errors for each sampled radii. } 
   \label{fig:Triax_MHD}
@@
 
-As a check of consistency, we compare our new isopotential shape results with the analytic expression of the $(1-q_{\phi})\frac{1}{3}(1-q_{\rho})$ \citep[Binney and Tremaine year]{Binney and tremaine}, taking the volume-enclosed axial ratios as an approximation for the isodensity contour ratios $q_{\rho}$.
-Although this analytic expression if meant to be used for logarithmic axisymmetric halos, it works well as a first approximation for nearly axisymmetric halos as those produced by our disced galaxies.
-We find that the difference between the real and the analytic isopotential axial ratios is not bigger than $quantity percent$.
-With this, we may now present on table \ref{tabe:isopotential} our observationally-comparable results for MHD halos at two important radii one corresponding to the approximate regimes where the MW DM halo is usually constrained.\\
+As a check of consistency, we compare our new isopotential shape
+results with the analytic expression of the
+$(1-q_{\phi})\frac{1}{3}(1-q_{\rho})$ \citep[Binney and Tremaine
+  year]{Binney and tremaine}, taking the volume-enclosed axial ratios
+as an approximation for the isodensity contour ratios
+$q_{\rho}$. Although this analytic expression if meant to be used for
+logarithmic axisymmetric halos, it works well as a first approximation
+for nearly axisymmetric halos as those produced by our disced
+galaxies. We find that the difference between the real and the
+analytic isopotential axial ratios is not bigger than $quantity
+percent$. With this, we may now present on table
+\ref{tabe:isopotential} our observationally-comparable results for MHD
+halos at two important radii one corresponding to the approximate
+regimes where the MW DM halo is usually constrained.
 
-Little discussion: Are our results congruent with observations? at which radii, does the DM halo shape vary that much?. Which models are favored?\\
+Little discussion: Are our results congruent with observations? at
+which radii, does the DM halo shape vary that much?. Which models are
+favored?
 
@@
 
-From the previous characterization of radial shapes it is clear that MHD halos are rounder than DM halos (i.e.
-axial ratios are bigger) at every sampled radii.
-This can be compared on tables \ref{tabe:DM table} and \ref{tabe:MHD table} or at the representative example on figure \ref{fig:DM_MHD}.
-From there, it is also noticeable that the rounding effect of baryons is stronger at the disk regime, where the DM halo is almost perfectly oblate.
-Furthermore, MHD halos tend towards more oblate shapes (T < 0.5) despite DM halos tendency towards more prolate shapes (T>0.5).\\
+From the previous characterization of radial shapes it is clear that
+MHD halos are rounder than DM halos (i.e. axial ratios are bigger) at
+every sampled radii. This can be compared on tables \ref{tabe:DM
+  table} and \ref{tabe:MHD table} or at the representative example on
+figure \ref{fig:DM_MHD}. From there, it is also noticeable that the
+rounding effect of baryons is stronger at the disk regime, where the
+DM halo is almost perfectly oblate. Furthermore, MHD halos tend
+towards more oblate shapes (T < 0.5) despite DM halos tendency towards
+more prolate shapes (T>0.5).
 
-This rounding effect is expected from the gravitational effect of the flattened axisymmetric galactic disk.
-It is also reasonable that this effect is not as strong at $\approx 100$Kpc, where the disk potential is dimmer compared to the DM halo potential.
-Keeping this in mind, one would expect that the rounding effect of baryons is related to some galactic parameters such as its component masses and radii.
-However, even for the parameter of highest correlation with this rounding effect (the baryonic fraction), the relation is not clear nor conclusive due to the dispersion from galaxy peculiarities.
-In figure \ref{fig:Star_Density_effect} we plot the ratios $c/a$ compared to the baryonic fraction of each galaxy.
-Although some linear tendency is suggested qualitatively, the dispersion of the sample is very high to obtain some conclusive relation.
-This is an evidence that adiabatic-contraction models are not realistic as they may neglect some effects of the galaxy evolution in the whole cosmological context.
-\\
+This rounding effect is expected from the gravitational effect of the
+flattened axisymmetric galactic disk. It is also reasonable that this
+effect is not as strong at $\approx 100$Kpc, where the disk potential
+is dimmer compared to the DM halo potential. Keeping this in mind, one
+would expect that the rounding effect of baryons is related to some
+galactic parameters such as its component masses and radii. However,
+even for the parameter of highest correlation with this rounding
+effect (the baryonic fraction), the relation is not clear nor
+conclusive due to the dispersion from galaxy peculiarities. In figure
+\ref{fig:Star_Density_effect} we plot the ratios $c/a$ compared to the
+baryonic fraction of each galaxy. Although some linear tendency is
+suggested qualitatively, the dispersion of the sample is very high to
+obtain some conclusive relation. This is an evidence that
+adiabatic-contraction models are not realistic as they may neglect
+some effects of the galaxy evolution in the whole cosmological
+context.
 
@@
 
-\textbf{Actually we have not examined the relation of c/a in MHD halos with some measure of c/a from the disk, that is something like Zdisk/Rdisk.
-This actually would make more sense from a physical point of view: effect of the potential.}
+\textbf{Actually we have not examined the relation of c/a in MHD halos
+  with some measure of c/a from the disk, that is something like
+  Zdisk/Rdisk. This actually would make more sense from a physical
+  point of view: effect of the potential.}
 
-Although the effect of the baryonic disk on the shape of the DM halo is a reasonable explanation for the rounding effect, it does not actually explain the deviation from oblateness of MHD halos at $r<10$Kpc.
-In other words, if the disk is perfectly axisymmetric, there must be some source of triaxiality at $r<10$Kpc to explain the low axial ratios.\\
+Although the effect of the baryonic disk on the shape of the DM halo
+is a reasonable explanation for the rounding effect, it does not
+actually explain the deviation from oblateness of MHD halos at
+$r<10$Kpc. In other words, if the disk is perfectly axisymmetric,
+there must be some source of triaxiality at $r<10$Kpc to explain the
+low axial ratios.
 
-\textit{ Talk about source of triaxiality at the inner parts of the halos (bar?).
-This source of triaxiality at the inner parts explains why the axial ratios are $\approx 0.95$ and not exactly $1$.
-We should also discuss that the decrease in the axial ratios for bigger radii may actually be bigger/steeper but it is dimmed by the contribution of inner parts.}\\
+\textit{ Talk about source of triaxiality at the inner parts of the
+  halos (bar?). This source of triaxiality at the inner parts explains
+  why the axial ratios are $\approx 0.95$ and not exactly $1$. We
+  should also discuss that the decrease in the axial ratios for bigger
+  radii may actually be bigger/steeper but it is dimmed by the
+  contribution of inner parts.} 
 %
@@
 \subsection{The historical shape}
-One of the principal motivations to study the radial dependence of the DM halo shape is that it may encode some clues about its formation history.
-We have already shown that DM-only halos seem to exhibit a steady and monotonous growth in its axial ratios when sampled at bigger radii.
-One similar effect can be found if we sample the shape at the virial radius, this time at varying redshift.
-It is easy to see that the axial ratios increase with decreasing redshift, which is expected by the continuous influence of the gravitational potential \cite{VeraCiro}.
-In figure \ref{fig:RedshiftGood} we present a representative example.
-\\
+One of the principal motivations to study the radial dependence of the
+DM halo shape is that it may encode some clues about its formation
+history. We have already shown that DM-only halos seem to exhibit a
+steady and monotonous growth in its axial ratios when sampled at
+bigger radii. One similar effect can be found if we sample the shape
+at the virial radius, this time at varying redshift. It is easy to see
+that the axial ratios increase with decreasing redshift, which is
+expected by the continuous influence of the gravitational potential
+\cite{VeraCiro}. In figure \ref{fig:RedshiftGood} we present a
+representative example.
 
@@
 
-Interestingly, these two parametic plots i.e.
-$(b/a,c/a)(z=0,r)$ and $(b/a,c/a)(z,r=R_{vir})$ are very correlated for DM-only halos \ref{fig:DM Z Triax}.
-This means that, for DM-only halos, one can approximate its shape at higher redshift by simply sampling its current shape at a smaller radius \textbf{wording}.
-This relationship relies strongly on the steady and monotonous tendency of DM halos towards sphericity for bigger radii and smaller redshift.\\
+Interestingly, these two parametic plots i.e. $(b/a,c/a)(z=0,r)$ and
+$(b/a,c/a)(z,r=R_{vir})$ are very correlated for DM-only halos
+\ref{fig:DM Z Triax}. This means that, for DM-only halos, one can
+approximate its shape at higher redshift by simply sampling its
+current shape at a smaller radius \textbf{wording}. This relationship
+relies strongly on the steady and monotonous tendency of DM halos
+towards sphericity for bigger radii and smaller redshift.
 
@@
 
-MHD halos, on the other hand, do not exhibit tendency towards sphericity with bigger radii, but they do get sistematically rounder at lower redshift as seen in figure \ref{fig:RedshiftGood}.
-This effectively vanishes this correlation as seen from a DM halo \ref{fig:MHD Z Triax}.\\
+MHD halos, on the other hand, do not exhibit tendency towards
+sphericity with bigger radii, but they do get sistematically rounder
+at lower redshift as seen in figure \ref{fig:RedshiftGood}. This
+effectively vanishes this correlation as seen from a DM halo
+\ref{fig:MHD Z Triax}.
 
@@
 	\includegraphics[width=\columnwidth]{./pics/Redshift/halo_24_level3_MHD_Z_Triax.png}
-    \caption{Difference in asphericities between MHD and DM shapes Vs Star Density of the simulation.}
+    \caption{Difference in asphericities between MHD and DM shapes Vs
+      Star Density of the simulation.} 
     \label{fig:MHD Z Triax} 
-
 \end{figure}
@@
 
-One of the principal assumptions of observational models of the MW's DM halo is that its minor axis is perfectly aligned with the disk axis.
-Although this is a reasonable assumption to guarantee the stability of the galactic disk in simplified models of isolated galaxies, it may not be the case for galaxies evolved in the whole cosmological context nor at every radii at which the shape is sampled.\\
+One of the principal assumptions of observational models of the MW's
+DM halo is that its minor axis is perfectly aligned with the disk
+axis. Although this is a reasonable assumption to guarantee the
+stability of the galactic disk in simplified models of isolated
+galaxies, it may not be the case for galaxies evolved in the whole
+cosmological context nor at every radii at which the shape is
+sampled.
 
-Therefore, it is of special interest to us to examin the strength of this alignment assumption in the context of simulations.
-For this purpose, we sampled the shape at 5 different radii and plotted the axial directions, as well as the disk direction in the \textbf{name} diagrams \cite{} (explain diagrams).
-Explain disk direction calculation.\\
+Therefore, it is of special interest to us to examin the strength of
+this alignment assumption in the context of simulations. For this
+purpose, we sampled the shape at 5 different radii and plotted the
+axial directions, as well as the disk direction in the \textbf{name}
+diagrams \cite{} (explain diagrams). Explain disk direction
+calculation.
 
-We found that there is not a representative example of what happens in terms of alignments.
-We found that the majority of the disks are aligned with the minor axis of their DM halo within $\approx 30^o$; in some special cases, this alignment was almost perfect and in some other cases, the DM halo minor axis changed substantially to be able to determine an alignment.
-In figure \ref{fig:alignment} we present these three cases.
-\textbf{occurrencies for each case?}
+We found that there is not a representative example of what happens in
+terms of alignments. We found that the majority of the disks are
+aligned with the minor axis of their DM halo within $\approx 30^o$; in
+some special cases, this alignment was almost perfect and in some
+other cases, the DM halo minor axis changed substantially to be able
+to determine an alignment. In figure \ref{fig:alignment} we present
+these three cases. \textbf{occurrencies for each case?}
 
-\textit{This is an important result of our study.
-We study the radial evolution of the principal axes, compared also to the angular momentum vector from the disk.
-We found that while the angular momentum tend to be aligned with the minor axis of the ellipsoid, this may not be the case all times.
-When there is an alignment it is usually within 20 degrees (get a histogram of this.
-and an evolution of this histogram with time).
-When there is not an alignment, then there is no simple way to determine towards which axis it is oriented.
-Furthermore, the principal axes alignment usually change with radius (rotation, swap, verify).
-This ask for relaxation on the strong constrains on the MW DM halo models.}
+\textit{This is an important result of our study. We study the radial
+  evolution of the principal axes, compared also to the angular
+  momentum vector from the disk. We found that while the angular
+  momentum tend to be aligned with the minor axis of the ellipsoid,
+  this may not be the case all times. When there is an alignment it is
+  usually within 20 degrees (get a histogram of this. and an evolution
+  of this histogram with time). When there is not an alignment, then
+  there is no simple way to determine towards which axis it is
+  oriented. Furthermore, the principal axes alignment usually change
+  with radius (rotation, swap, verify). This ask for relaxation on the
+  strong constrains on the MW DM halo models.}
 
@@
 
-\textbf{Discussion about the distribution of alignments and their evolution in time: Precesion or temporary instabilities?}
+\textbf{Discussion about the distribution of alignments and their
+  evolution in time: Precesion or temporary instabilities?}
 
@@
 \section*{Acknowledgements}
-This project has received funding from the European Union’s Horizon 2020 Research and Innovation Programme under the Marie Sk\l{}odowska-Curie grant agreement No 734374
+This project has received funding from the European Union’s Horizon
+2020 Research and Innovation Programme under the Marie
+Sk\l{}odowska-Curie grant agreement No 734374.
 

### 2018-09-24 Paper/paper.tex
table progress

@@
 \usepackage{subfig}
+\usepackage{array}
+
+% Included by user
+\usepackage{multirow}
+\usepackage{multicol}
+\usepackage{blindtext}
+\newcolumntype{?}{!{\vrule width 1pt}}
+
+\newenvironment{Table}
+   {\par\bigskip\noindent\minipage{\columnwidth}\centering}
+   {\endminipage\par\bigskip}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \bibliography{references}
+
+\newpage
+%\begin{multicols}{2}
+\begin{Table}
+%\setlength{\tabcolsep}{3pt}
+\begin{tabular}{l|cc|cc|c|c|c}
+Refference&$q_{\rho}$&$s_{\rho}$&$q_{\phi}$&$s_{\phi}$&$R$&$\theta$&comment\\ \hline \hline
+\citet{Law_and_Majewski_2009}&&&$\mathbf{0.83}$&$\mathbf{0.67}$& $\lesssim 60$kpc&$90^{\circ}$&\multicolumn{1}{p{4.5cm}}{\raggedright Mid-axis orientation\\Method: Sagittarius stream}\\
+%
+\citet{Law_and_Majewski_2010}&&&$\mathbf{0.99}$&$\mathbf{0.72}$& $[20$kpc,$60$kpc$]$&$90^{\circ}$&\multicolumn{1}{p{4.5cm}}{\raggedright Mid-axis orientation \\ Method: Sagittarius stream}\\
+%
+\citet{Deg_and_Widrow_2013}&$0.72$&$0.28$&$0.82$&$0.40$&$[20$kpc,$60$kpc$]$&$90^{\circ}$&\multicolumn{1}{p{4.5cm}}{\raggedright Mid-axis orientation\\ Method: Sagittarius stream}\\
+%
+\citet{Olling_and_Merrifield_2000}&$\mathbf{1.00}$&$\mathbf{0.80}$&&&$\simeq 8$kpc&$0^{\circ}$&\multicolumn{1}{p{4.5cm}}{\raggedright Method: Stellar dynamics and HI density.}\\
+%
+\citet{Bovy_et_el._2016}&$\mathbf{0.95}$&$\mathbf{0.95}$&&&$\lesssim 20$kpc&$90^{\circ}$&\multicolumn{1}{p{4.5cm}}{\raggedright Method: Stellar streams}\\
+%
+\citet{Loebman_et_al._2012}&$\mathbf{1.00}$&$\mathbf{0.47}$&&&$\sim 20$kpc &$0^{\circ}$&\multicolumn{1}{p{4.5cm}}{\raggedright Method: SDSS statistics}\\
+%
+\multirow{2}{*}{\citet{Vera-Ciro_and_Helmi_2013}}&&&$\mathbf{1.00}$&$\mathbf{0.90}$&$\lesssim 10$kpc&$0^{\circ}$&\multicolumn{1}{p{4.5cm}}{\raggedright Method: Sagittarius stream \& LMC }\\
+&&&$\mathbf{0.90}$&$\mathbf{0.80}$&$\gtrsim 10$kpc&$90^{\circ}$&\multicolumn{1}{p{4.5cm}}{\raggedright Mid-axis orientation on the outside. }\\
+\end{tabular}
+\end{Table}
+%\end{multicols}
 

### 2018-09-25 Paper/paper.tex
edit table

--- 2018-09-18 Paper/paper.tex
@@
 \bibliography{references}
+
+\newpage
+%\begin{multicols}{2}
+\begin{Table}
+%\setlength{\tabcolsep}{3pt}
+\begin{tabular}{|c|cc|cc|c|c|p{4cm}|}\hline
+Reference&$q_{\rho}$&$s_{\rho}$&$q_{\phi}$&$s_{\phi}$&$R$&$\theta$&comment\\ \hline \hline
+\citet{Olling_and_Merrifield_2000}& $\mathbf{1.00}$ & $\mathbf{0.80}$ & & & $\simeq 8$kpc & $0^{\circ}$&Method: Stellar dynamics and HI density. \\\hline
+\citet{Law_and_Majewski_2009}&&&$\mathbf{0.83}$&$\mathbf{0.67}$& $\lesssim 60$kpc&$90^{\circ}$&Mid-axis orientation. Method: Sagittarius stream\\\hline
+%
+\citet{Law_and_Majewski_2010}&&&$\mathbf{0.99}$&$\mathbf{0.72}$& $[20$kpc,$60$kpc$]$&$90^{\circ}$&Mid-axis orientation, Method: Sagittarius stream\\\hline
+%
+\citet{Loebman_et_al._2012}&$\mathbf{1.00}$&$\mathbf{0.47}$&&&$\sim 20$kpc &$0^{\circ}$&Method: SDSS statistics\\\hline
+%
+\citet{Deg_and_Widrow_2013}&$0.72$&$0.28$&$0.82$&$0.40$&$[20$kpc,$60$kpc$]$&$90^{\circ}$& Mid-axis orientation. Method: Sagittarius stream\\\hline
+%
+\multirow{2}{*}{\citet{Vera-Ciro_and_Helmi_2013}}&&&$\mathbf{1.00}$&$\mathbf{0.90}$&$\lesssim 10$kpc&$0^{\circ}$ & Method: Sagittarius stream \& LMC \\
+&&&$\mathbf{0.90}$&$\mathbf{0.80}$&$\gtrsim 10$kpc&$90^{\circ}$& Mid-axis orientation on the outside. \\\hline
+%
+\citet{Bovy_et_el._2016}&$\mathbf{0.95}$&$\mathbf{0.95}$&&&$\lesssim 20$kpc&$90^{\circ}$ & Method: Stellar streams\\\hline
+
+\end{tabular}
+\end{Table}
+%\end{multicols}
 

### 2018-09-25 Paper/paper.tex
references

@@
 
+Although observations predict more symmetric halos than DM-only
+simulations,
+
+{\bf AQUI:Parrafo sobre las predicciones de DM only simulations.}
+
+There is strong evidence claiming that the presence of
+baryons produces axisymmetrical halos. 
+For instance, some studies have shown that the DM halo shape must be
+axisymmetrical to ensure the stability of a hydrodynamical disk
+embeded in a static DM halo. 
+Other have studied this rounding effect by simulating the disk as rigid
+potential inside an N-body triaxial DM
+halo \cite{Debattista_et_al._2008,Debattista_et_al._2013,Kazantzidis_et_al._2010}
+finding that the halo responds to the disk by becoming less triaxial.
+
+While these studies are elucidating about dynamical aspects that may
+play important roles in the rounding of the DM halo shape, they do not
+follow baryons in the whole cosmological context. Abadi-Navarro and
+Bryan-Kay studied the evolution of galaxies in hydrodynamical
+simulations with restricted models of feedback
+\cite{Abadi-Navarro,Bryan-Kay} finding that the galaxy formation
+efficiency \cite{Abadi} and the history of formation may also
+determine the extent of this rounding.
+
+In general, there is much to be known about the specifics of the
+rounding effec of baryons. (There are have been no realistic
+simulations of MW-like galaxies to a resolution/realism that allows us
+to obtain stronger conslusions)
+
+In this work, we analyze the Auriga simulations wich etc, where we can
+analyze the effect baryons together with galactic features, that are
+involved in the shaping of the DM halo shape of realistic MW-like
+galaxies.
+
 %Better connector with observations of distant galaxies. Gravitational
@@
 
-\bibliographystyle{mnras}
-\bibliography{references}
-
-\newpage
 %\begin{multicols}{2}
@@
 
+\bibliographystyle{mnras}
+\bibliography{references}
+
 \end{document}
-
-Although observations predict more symmetric halos than DM-only
-simulations, there is strong evidence claiming that the presence of
-baryons need/make more axisymmetrical halos. Some studies have shown
-that to ensure the stability of a hydrodynamical (numeric) disk
-artificially embeded in a static(non-changing) DM halo, its shape must
-be axisymmetrical \cite{}. Other works have studied this rounding
-effect by emulating a disk as an adiabatically growing potential
-inside an N-body triaxial DM halo
-\cite{Debattista-Moore,Debattista-Roskar, katzantzidis}, finding that
-(findings of this study -debattista-). Other works of this type?
-
-While these studies are elucidating about dynamical aspects that may
-play important roles in the rounding of the DM halo shape, they do not
-follow baryons in the whole cosmological context. Abadi-Navarro and
-Bryan-Kay studied the evolution of galaxies in hydrodynamical
-simulations with restricted models of feedback
-\cite{Abadi-Navarro,Bryan-Kay} finding that the galaxy formation
-efficiency \cite{Abadi} and the history of formation may also
-determine the extent of this rounding.
-
-In general, there is much to be known about the specifics of the
-rounding effec of baryons. (There are have been no realistic
-simulations of MW-like galaxies to a resolution/realism that allows us
-to obtain stronger conslusions)
-
-In this work, we analyze the Auriga simulations wich etc, where we can
-analyze the effect baryons together with galactic features, that are
-involved in the shaping of the DM halo shape of realistic MW-like
-galaxies.
 

### 2018-09-25 Paper/paper.tex
paper.tex

@@
 While these studies are elucidating about dynamical aspects that may
-play important roles in the rounding of the DM halo shape, they do not
-follow baryons in the whole cosmological context. Abadi-Navarro and
-Bryan-Kay studied the evolution of galaxies in hydrodynamical
-simulations with restricted models of feedback
-\cite{Abadi-Navarro,Bryan-Kay} finding that the galaxy formation
-efficiency \cite{Abadi} and the history of formation may also
-determine the extent of this rounding.
+play an important role in the rounding of the DM halo shape, they do not
+follow baryons in the whole cosmological context. 
+Other studies overcome this limitation by using resimulations 
+\citep{Abadi_et_al._2010,Bryan_et_al._2013} finding that the
+feeback related to star formation in the disk drives the strenght of
+the round effect.
 
-In general, there is much to be known about the specifics of the
-rounding effec of baryons. (There are have been no realistic
-simulations of MW-like galaxies to a resolution/realism that allows us
-to obtain stronger conslusions)
+If one wants to make a numerical study of the DM halo shape for the
+MW, there is the additinal challenge of making a simulation that
+resemble the observed properties of the MW disk.
+All these difficulties (enough numerical resolution, explicit
+cosmological context, appropriate feedback physics to produce
+realistic MW disks) have limited the studies that want to study the
+rounding effect of baryons in MW-like galaxies.
 
-In this work, we analyze the Auriga simulations wich etc, where we can
-analyze the effect baryons together with galactic features, that are
-involved in the shaping of the DM halo shape of realistic MW-like
-galaxies.
+In this work we overcome these three limitation by analyzing the
+Our objective is to quantify the DM halo shape and investigate the
+effect of baryons.
 
@@
 %\begin{multicols}{2}
-\begin{Table}
+\begin{table*}
 %\setlength{\tabcolsep}{3pt}
@@
 \end{tabular}
-\end{Table}
+\end{table*}
 %\end{multicols}

### 2018-09-27 Paper/paper.tex
references
edit

@@
 resemble the observed properties of the MW disk.
+Recently \cite{2018arXiv180907255C} made a study in a cosmological
+simulation to compare the effect of including baryons. They do find,
+on average, rounder halo shapes once hydrodynamic effects are
+included, but it is uncertain the strenght of this statistical effect
+on galaxies similar to the MW.
+
 All these difficulties (enough numerical resolution, explicit
@@
 rounding effect of baryons in MW-like galaxies.
-
 In this work we overcome these three limitation by analyzing the
-Our objective is to quantify the DM halo shape and investigate the
-effect of baryons.
-
-%Better connector with observations of distant galaxies. Gravitational
-%lensing and star tracers. (Talk about discrepancy with simulations,
-%perhaps later) and state that the preference for axisymmetrical shapes
-%may arise from the observational restrictions (projection) look for
-%citations about this.
+results of state-of-the-art hydrodynamical simulations of isolated
+halos that resemble the Milky Way.
 
@@
 
+\section{Numerical Simulations}
+
+In this work we use the results of the state-of-the art Auriga
+simulations \cite{auriga}. 
+The sample starts with a set of 30 isolated halos from the Evolution
+and Assembly of GaLaxies and their Environments (EAGLE) project \cite{Eagle}. 
+These halos were randomly selected from a sample of the most isolated
+quartile of halos whose virial mass $M_{200}$ (200 times the critical
+density of the Universe) varied between $10^{12}M_\odot$ and $2\cdot
+10^{12}M_\odot$.
+These halos were re-simulated with the moving mesh code AREPO
+\citep{arepo} using different degrees of resolution and physics.
+All 30 halos were simulated within a level-4-degree of
+resolution defined for Aquarius simulations corresponding to $\sim
+3\times 10^6$ high resolution particles of mass $\sim 2.5 \times 10^5
+M_\odot$. 
+%The principal details of each of these halos are consigned
+%on the table \ref{tab:level4}. 
+From these halos, 6 were re-simulated at a higher resolution (Level-3)
+by increasing the number of particles by a factor of $8$.
+For each ach halo in Level-3 and Level-4 there are two version: one
+only includes DM particles, while the other also includes baryons with
+magneto-hydrodynamicl (MHD) physics.
+%re-simulated at level 3 (higher) resolution taking into account a
+%spatial factor of 2 in each dimension. For more information about
+%level 3 halos, their details are printed on table
+%\ref{tab:level3}.
+
 \bibliographystyle{mnras}
@@
 \end{document}
-
-\section{Numerical Simulations}
-In this work we use the results of the state-of-the art Auriga
-simulations \cite{auriga}. It selected a set of 30 isolated halos from
-the Evolution and Assembly of GaLaxies and their Environments (EAGLE)
-project \cite{Eagle}. Each halo was identified with the algorithm
-"Friend of Friends" (FOF) \cite{Davis_et_al._1985}, which recursively
-links particles if they are closer than some threshold distance
-referred as linking length. EAGLE follows the evolution of fixed-mass
-particles of $m_{\text{DM}} = 1.15\cdot 10^7\text{M}_{\odot}$ from
-$z=127$ to $z=0$, adopting the $\Lambda$CDM model from the
-\cite[Planck Collaboration et al. (2014)]{Planck_Collaboration_2014},
-which is characterized by $\Omega_\Lambda=0.693$,
-$\Omega_\text{m}=0.307$, $\Omega_\text{b}=0.048$ \&
-$\text{H}_0=67.77\text{kms} ^{-1}\text{Mpc}^{-1}$.
-
-These halos were randomly selected from a sample of the most isolated
-quartile of halos whose virial mass $M_{200}$ varied between
-$10^{12}M_\odot$ and $2\cdot 10^{12}M_\odot$. \textbf{\tiny This mass
-  is defined as the mass enclosed within the virial radius $R_{200}$
-  at which the density becomes 200 times the critical density of the
-  universe. \huge FOOTNOTE \normalsize}. These halos were re-simulated
-with the (AREPOOO HERE) by increasing the mass resolution of the
-particles belonging to them and diminishing the resolution of the rest
-of the particles.
-
-Various versions of each halo were modelled with different degrees of
-realism. All 30 halos were simulated within a level-4-degree of
-resolution defined for Aquarius simulations corresponding to $\tilde
-3\cdot 10^6$ high resolution particles of $\tilde 2.5 \cdot 10^5
-M_\odot$. The principal details of each of these halos are consigned
-on the table \ref{tab:level4}. From these halos, 6 of them where
-re-simulated at level 3 (higher) resolution taking into account a
-spatial factor of 2 in each dimension. For more information about
-level 3 halos, their details are printed on table
-\ref{tab:level3}. Furthermore, fore each halo in each level of
-resolution there are two versions of the simulation. One of tracks the
-evolution of DM-only particles while the remaining one evolves DM and
-baryions with magneto-hydrodynamical (MHD) physics, including DM.
 

### 2018-10-02 Paper/paper.tex
looking for more references

--- 2018-09-25 Paper/paper.tex
@@
 %\setlength{\tabcolsep}{3pt}
-\begin{tabular}{|c|cc|cc|c|c|p{4cm}|}\hline
+\begin{tabular}{|l|cc|cc|c|c|p{4cm}|}\hline
 Reference&$q_{\rho}$&$s_{\rho}$&$q_{\phi}$&$s_{\phi}$&$R$&$\theta$&comment\\ \hline \hline
@@
 \citet{Bovy_et_el._2016}&$\mathbf{0.95}$&$\mathbf{0.95}$&&&$\lesssim 20$kpc&$90^{\circ}$ & Method: Stellar streams\\\hline
-
+%
+\citet{Bowden_et_al._2016}&&&$\mathbf{[0.5,0.66]}$&$\mathbf{[0.5,0.66]}$&$[5$kpc,$10$kpc$]$&$90^{\circ}$& Weak constraint on prolate halo. Method: SDSS stars dynamics.\\\hline
+%
+\multirow{2}{*}{\citet{Banerjee_and_Chanda_2011}}&$\mathbf{1}$&$\mathbf{1}$&&&$9$kpc&$0^{\circ}$&Method: HI gas. \\
+&$\mathbf{0.5}$&$\mathbf{0.5}$&&&$24$kpc&$0^{\circ}$&Monotonical change between radial regimes.\\\hline
+%
+\cite{Johnston_et_al._2005}&$\mathbf{1}$&$\mathbf{[0.83-0.92]}$&&&$\lesssim 60$kpc&$0^{\circ}$&Method: Sagittarius stream\\\hline\hline
 \end{tabular}
+\caption{Caption explaining table columns and bold meaning (TODO: compute analogues in isopotential or isodensity according to Binney and Tremaine)}
 \end{table*}
 %\end{multicols}
+
+\begin{table*}
+%\setlength{\tabcolsep}{3pt}
+\begin{tabular}{|l|cc|cc|c|p{4cm}|}\hline
+Reference&$q_{\rho}$&$s_{\rho}$&$q_{\phi}$&$s_{\phi}$&$R$&comment\\ \hline \hline
+\citet{Chua_et_al._2018}&$\mathbf{0.88\pm0.10}$&$\mathbf{0.70\pm0.11}$&&&$0.15R_{200}$& Illustris\\\hline
+%
+\citet{Bryan_et_al._2013}&$\mathbf{[0.84,0.86]}$&$\mathbf{[0.66,0.70]}$&&&$R_{200}$& For different cosmologies and feedback recipies. Calculated from a fit at $M_\odot=10^12$\\\hline
+%
+\multirow{2}{*}{\citet{Abadi_et_al._2010}}&&&$\mathbf{0.98}$&$\mathbf{0.85}$&-& Almost independent of radius. No feedback: boundary case\\\hline
+\end{tabular}
+\caption{Caption explaining table columns and bold meaning (TODO: compute analogues in isopotential or isodensity according to Binney and Tremaine)}
+\end{table*}
 

### 2018-10-12 Paper/paper.tex

@@
 
+\section{Numerical Simulations}
+
+In this work we use the results of the state-of-the art Auriga
+simulations \cite{auriga}. 
+The sample starts with a set of 30 isolated halos from the Evolution
+and Assembly of GaLaxies and their Environments (EAGLE) project \cite{Eagle}. 
+These halos were randomly selected from a sample of the most isolated
+quartile of halos whose virial mass $M_{200}$ (200 times the critical
+density of the Universe) varied between $10^{12}M_\odot$ and $2\cdot
+10^{12}M_\odot$.
+These halos were re-simulated with the moving mesh code AREPO
+\citep{arepo} using different degrees of resolution and physics.
+All 30 halos were simulated within a level-4-degree of
+resolution defined for Aquarius simulations corresponding to $\sim
+3\times 10^6$ high resolution particles of mass $\sim 2.5 \times 10^5
+M_\odot$. 
+%The principal details of each of these halos are consigned
+%on the table \ref{tab:level4}. 
+From these halos, 6 were re-simulated at a higher resolution (Level-3)
+by increasing the number of particles by a factor of $8$.
+For each ach halo in Level-3 and Level-4 there are two version: one
+only includes DM particles, while the other also includes baryons with
+magneto-hydrodynamicl (MHD) physics.
+%re-simulated at level 3 (higher) resolution taking into account a
+%spatial factor of 2 in each dimension. For more information about
+%level 3 halos, their details are printed on table
+%\ref{tab:level3}.
+
 \begin{table*}
@@
 \end{table*}
-
-\bibliographystyle{mnras}
-\bibliography{references}
-
-\end{document}
 
@@
 baryions with magneto-hydrodynamical (MHD) physics, including DM.
+
+ \bibliographystyle{mnras}
+ \bibliography{references}
+\end{document}
 
@@
 \label{lastpage}
+
 \end{document}

### 2018-10-12 Paper/paper.tex
edit

@@
 \section{Numerical Simulations}
+
 In this work we use the results of the state-of-the art Auriga
-simulations \cite{auriga}. It selected a set of 30 isolated halos from
+simulations \cite{auriga}. 
+The objects in those simulations were selected from a set of 30 isolated halos in
 the Evolution and Assembly of GaLaxies and their Environments (EAGLE)
-project \cite{Eagle}. Each halo was identified with the algorithm
-"Friend of Friends" (FOF) \cite{Davis_et_al._1985}, which recursively
-links particles if they are closer than some threshold distance
-referred as linking length. EAGLE follows the evolution of fixed-mass
-particles of $m_{\text{DM}} = 1.15\cdot 10^7\text{M}_{\odot}$ from
-$z=127$ to $z=0$, adopting the $\Lambda$CDM model from the
-\cite[Planck Collaboration et al. (2014)]{Planck_Collaboration_2014},
-which is characterized by $\Omega_\Lambda=0.693$,
-$\Omega_\text{m}=0.307$, $\Omega_\text{b}=0.048$ \&
-$\text{H}_0=67.77\text{kms} ^{-1}\text{Mpc}^{-1}$.
-
+project \cite{Eagle}. 
 These halos were randomly selected from a sample of the most isolated
 quartile of halos whose virial mass $M_{200}$ varied between
-$10^{12}M_\odot$ and $2\cdot 10^{12}M_\odot$. \textbf{\tiny This mass
-  is defined as the mass enclosed within the virial radius $R_{200}$
-  at which the density becomes 200 times the critical density of the
-  universe. \huge FOOTNOTE \normalsize}. These halos were re-simulated
-with the (AREPOOO HERE) by increasing the mass resolution of the
-particles belonging to them and diminishing the resolution of the rest
-of the particles.
+$10^{12}M_\odot$ and $2\cdot 10^{12}M_\odot$. 
+These halos were re-simulated with higher resolution an varying
+physical realism using the AREPO code \citep{codee}.
 
-Various versions of each halo were modelled with different degrees of
-realism. All 30 halos were simulated within a level-4-degree of
-resolution defined for Aquarius simulations corresponding to $\tilde
-3\cdot 10^6$ high resolution particles of $\tilde 2.5 \cdot 10^5
-M_\odot$. The principal details of each of these halos are consigned
-on the table \ref{tab:level4}. From these halos, 6 of them where
-re-simulated at level 3 (higher) resolution taking into account a
-spatial factor of 2 in each dimension. For more information about
-level 3 halos, their details are printed on table
-\ref{tab:level3}. Furthermore, fore each halo in each level of
+All 30 halos were simulated within resolution defined for Aquarius
+simulations corresponding to $\sim 3\time 10^6$ high resolution particles of $\sim 2.5 \time 10^5
+M_\odot$.  
+This resolution is labeled as Level 4, the main details for each halo
+are consigned in Table \ref{tab:level4}. 
+From these 30 halos, 6 of them where re-simulated at higher resolution
+(labeled as Level 3) taking into account a spatial factor of 2 in each
+dimension.   
+Details of Level 3 halos are in Table \ref{tab:level3}. 
+Furthermore, fore each halo in each level of
 resolution there are two versions of the simulation. One of tracks the

### 2018-10-12 Paper/paper.tex
edit paper

@@
 In this work we use the results of the state-of-the art Auriga
-simulations \cite{auriga}. 
+simulations \citep{auriga}. 
 The objects in those simulations were selected from a set of 30 isolated halos in
 the Evolution and Assembly of GaLaxies and their Environments (EAGLE)
-project \cite{Eagle}. 
+project \citep{Eagle}. 
 These halos were randomly selected from a sample of the most isolated
 quartile of halos whose virial mass $M_{200}$ varied between
-$10^{12}M_\odot$ and $2\cdot 10^{12}M_\odot$. 
+$10^{12}M_\odot$ and $2\times 10^{12}M_\odot$. 
 These halos were re-simulated with higher resolution an varying
-physical realism using the AREPO code \citep{codee}.
+physical realism using the AREPO code \citep{arepo}.
 
 All 30 halos were simulated within resolution defined for Aquarius
-simulations corresponding to $\sim 3\time 10^6$ high resolution particles of $\sim 2.5 \time 10^5
+simulations corresponding to $\sim 3\times 10^6$ high resolution particles of $\sim 2.5 \times 10^5
 M_\odot$.  
@@
 Details of Level 3 halos are in Table \ref{tab:level3}. 
-Furthermore, fore each halo in each level of
-resolution there are two versions of the simulation. One of tracks the
-evolution of DM-only particles while the remaining one evolves DM and
-baryions with magneto-hydrodynamical (MHD) physics, including DM.
+Furthermore, for each halo in each level of resolution there are two
+versions of the simulation. 
+One of tracks theevolution of DM-only particles while the remaining
+one evolves DM and baryons with magneto-hydrodynamical (MHD) physics.
 

### 2018-10-12 Paper/paper.tex
edit

@@
 
-\section{Numerical Simulations}
-
-In this work we use the results of the state-of-the art Auriga
-simulations \cite{auriga}. 
-The sample starts with a set of 30 isolated halos from the Evolution
-and Assembly of GaLaxies and their Environments (EAGLE) project \cite{Eagle}. 
-These halos were randomly selected from a sample of the most isolated
-quartile of halos whose virial mass $M_{200}$ (200 times the critical
-density of the Universe) varied between $10^{12}M_\odot$ and $2\cdot
-10^{12}M_\odot$.
-These halos were re-simulated with the moving mesh code AREPO
-\citep{arepo} using different degrees of resolution and physics.
-All 30 halos were simulated within a level-4-degree of
-resolution defined for Aquarius simulations corresponding to $\sim
-3\times 10^6$ high resolution particles of mass $\sim 2.5 \times 10^5
-M_\odot$. 
-%The principal details of each of these halos are consigned
-%on the table \ref{tab:level4}. 
-From these halos, 6 were re-simulated at a higher resolution (Level-3)
-by increasing the number of particles by a factor of $8$.
-For each ach halo in Level-3 and Level-4 there are two version: one
-only includes DM particles, while the other also includes baryons with
-magneto-hydrodynamicl (MHD) physics.
-%re-simulated at level 3 (higher) resolution taking into account a
-%spatial factor of 2 in each dimension. For more information about
-%level 3 halos, their details are printed on table
-%\ref{tab:level3}.
-
 \begin{table*}
@@
 
- \bibliographystyle{mnras}
- \bibliography{references}
-\end{document}
-
 \section{Determining the halo shape}
@@
 
-There is no trivial way to calculate the DM halo shape at a determined
-radius due to the discretization of particles. For practical effects,
-observational models focus on the shape of the DM isopotential
-\cite{isopotential} or isodensity \cite{isodensity} contours. In
-cosmological simulations, it is preferred to work with the isodensity
-contours which is directly calculated from particle
-positions. However, these density contours are not smooth and are very
-sensitive to the presence of small satelites \cite{Springel
-  Isodensity}. For this reason we determine the shape taking into
-account volume-enclosed particles, rather than shell-enclosed. While
-this approach allows the cumulative influence of outter shells on the
-outter shapes, it has been demonstrated for DM-only simulations that
-this effect becomes important only for big radii \cite{vera-Ciro
-  aquarius}.  We therefore follow the method of \cite[Allgood et
-  al. 2006]{Allgood_et_al._2006} that consits in the use of the
-reduced inertia tensor,
+There are two main ways to estimate the DM halo shape at a fixed
+radius: by computing isopotential or isodensity surfaces.
+Observational inference models estimate the shape from the
+isopotential contours, while simulations work with the isodensity
+contours which can be  directly calculated from particle positions.  
+However, the density contours are not smooth and are very 
+sensitive to the presence of small satelites.
+For this reason we choose to measure the shape by taking
+volume-enclosed particles, rather than shell-enclosed.
+
+We follow the shape measurement method presented by
+\cite{Allgood_et_al._2006} that consits in the using the reduced
+inertia tensor,
 
@@
 
-with components weighted by the k-th particle distance $d^2=x^2+y^2+z^2$.\\
+with the positions components weighted by the k-th particle distance
+$d_k^2=x_k^2+y_k^2+z_k^2$, the particle positions are measured from
+the minimum of the gravitational potential in each halo.
 
@@
 structure as well as the eigen-quantities which are proportional to
-the squared principal axes $a>b>c$. We start our calculations taking
+the squared principal axes $a>b>c$. 
+We start our calculations taking
 into account particles within a sphere of radius $R$ and then
@@
 particles within an ellipsoid of semi-axes $r,r/q,r/s$ and weighted
-distance $d^2=x^2+(y/q)^2+(z/s)^2$, where ere $q = b/a$ and $s=c/a$
-are the previously calculated axial ratios. We repeat this process
-until the average deviation of semi-axes is less than $10^{-6}$.
+distance $d^2=x^2+(y/q)^2+(z/s)^2$, where $q = b/a$ and $s=c/a$
+are the previously calculated axial ratios. 
+We repeat this process until the average deviation of semi-axes is
+less than $10^{-6}$.
+
+This is the same method used to estimate the halo shape in the DM-only
+Aquarius simulations \citep{Vera-Ciro_et_al._2011}.
+
+ \bibliographystyle{mnras}
+ \bibliography{references}
+\end{document}
 

### 2019-01-22 Paper/paper.tex
update intro

@@
 \citep{Allgood_et_al._2006}, halos are also rounder at the outerskirts
-than at the inner part. Shape also evolves with cosmic time, halos get
+than at the inner part. 
+Shape also evolves with cosmic time, halos get
 rounder as they evolve.
 
-In the case of the Milky Way, where we have a three-dimensional view
-from the inside, the community does not have a clear agreement. 
-Some studies prefer oblate (i.e. a=b>c) configurations at small
+There is however a high degree of uncertainty on what is the degree of
+uncertainty on the degree of ellipticity of the Milky Way DM halo.
+This problem has been addressed both by observations and simulations.
+The difficulty in making an observational measurement lies in the
+indirect nature of the effect; i.e. the ellipticity can only be
+constrained by its effects on quantities such as stellar radial
+velocities.
+In simulations the uncertainty on predicting the MW DM ellipticity is 
+driven by the different physical effects that should be modeled and
+its different possible numerical implementations.
+
+Observationally some studies prefer oblate (i.e. a=b>c) configurations at small
 distances around $\leq 20$ kpc
@@
 \citep[see][]{Vera-Ciro_and_Helmi_2013,Law_and_Majewski_2009,Deg_and_Widrow_2013,Banerjee_and_Chanda_2011}.
-
 However, some  studies are inclined towards prolate configurations even at the inner
@@
 
-Although observations predict more symmetric halos than DM-only
-simulations,
-
-{\bf AQUI:Parrafo sobre las predicciones de DM only simulations.}
-
-There is strong evidence claiming that the presence of
+In simulations there is strong evidence claiming that the presence of
 baryons produces axisymmetrical halos.  
@@
 
-While these studies are elucidating about dynamical aspects that may
-play an important role in the rounding of the DM halo shape, they do not
+The caveat of the studies mentioned above is that they do not
 follow baryons in the whole cosmological context. 
@@
 the round effect. 
-
-If one wants to make a numerical study of the DM halo shape for the
-MW, there is the additinal challenge of making a simulation that
-resemble the observed properties of the MW disk.
 Recently \cite{2018arXiv180907255C} made a study in a cosmological
@@
 rounding effect of baryons in MW-like galaxies.
-In this work we overcome these three limitation by analyzing the
+In this work we overcome all these limitations by analyzing the
 results of state-of-the-art hydrodynamical simulations of isolated
 halos that resemble the Milky Way.
+We also perform a convergence study with simulation performed at
+different resolution levels and explicitly compare the role of DM only
+vs. DM+hydro on the MW DM halo shape.
 

### 2019-01-22 Paper/paper.tex
results

@@
 % Keep the title short and informative.
-\title[Title]{The expected shape of the Milky Way's Dark Matter halo}
+\title[MW DM halo shape in AURIGA]{The expected shape of the Milky Way's Dark Matter halo}
 
@@
 \end{tabular}
-\caption{Caption explaining table columns and bold meaning (TODO: compute analogues in isopotential or isodensity according to Binney and Tremaine)}
+\caption{(TODO: compute analogues in isopotential or isodensity according to Binney and Tremaine)}
 \end{table*}
@@
 All 30 halos were simulated within resolution defined for Aquarius
-simulations corresponding to $\sim 3\times 10^6$ high resolution particles of $\sim 2.5 \times 10^5
-M_\odot$.  
+simulations corresponding to $\sim 3\times 10^6$ high resolution DM
+particles of $\sim 2.5 \times 10^5 M_\odot$.  
 This resolution is labeled as Level 4, the main details for each halo
@@
 Furthermore, for each halo in each level of resolution there are two
-versions of the simulation. 
-One of tracks theevolution of DM-only particles while the remaining
-one evolves DM and baryons with magneto-hydrodynamical (MHD) physics.
+versions of the simulation: DM-only and DM plus baryons with
+magneto-hydrodynamical (MHD) physics.
 
@@
 We follow the shape measurement method presented by
-\cite{Allgood_et_al._2006} that consits in the using the reduced
+\cite{Allgood_et_al._2006} that uses the reduced
 inertia tensor,
@@
 the minimum of the gravitational potential in each halo.
-
 The diagonalization of this tensor yields the principal axes of the
@@
 the squared principal axes $a>b>c$.
-We start our calculations taking
-into account particles within a sphere of radius $R$ and then
-recharacterize the triaxial parameters by taking into account
+
+We start the calculations taking into account particles within a
+sphere of radius $R$ and then  recharacterize the triaxial parameters by taking into account
 particles within an ellipsoid of semi-axes $r,r/q,r/s$ and weighted
@@
 less than $10^{-6}$.  
-
 This is the same method used to estimate the halo shape in the DM-only
 Aquarius simulations \citep{Vera-Ciro_et_al._2011}.
+
+We restrict the sampling of the ellipsoidal parameters to radii
+between $1/16 R_{vir}$ and $2R_{vir}$, where  $R_{vir}$ is taken as the
+radius enclosing a sphere with 500 times the average dark matter
+density of the Universe. All our results use of this reference radius
+unless strictly stated otherwise. 
+We peform the shape measurements both as a function of radius and
+redshift for all halos in the sample.
+
+\section{Results}
+
+\subsection{Radial trends}
+
+In DM-only simulations halos are monotonically rounder with increasing
+radius, this confirms results already reported in the literature
+\citep{Vera-Ciro_et_al._2011}. 
+Figure \ref{fig:slices} illustrates this effect.
+There we show the DM density of a DM-only halo at redshift zero.
+The halo is aligned with the minor axis. 
+The ellipsoid shows the outermost boundary of the estimated shape ellipsoid.
+Formally, this effect is reflected in the axial ratios $b/a,c/a$, which tend to unity
+on the outerskirts of the halo. As a representative sample of this
+relations, we show on figure \ref{fig:DM relation} the evolution, for
+a specific halo, of the axial ratios $b/a,c/a$ and the triaxiality
+parameter $T=\frac{a^2-b^2}{a^2-c^2}$ in a wide range of radii.
+
+\begin{figure*}
+  \centering
+  \subfloat[halo 27 DM shape at small radius]{\includegraphics[width=0.5\textwidth]{./pics/MHD_Vs_DM/level4_DM_halo_27_inner.png}}
+  \hfill
+  \subfloat[halo 27 DM shape at big radius]{\includegraphics[width=0.5\textwidth]{./pics/MHD_Vs_DM/level4_DM_halo_27_outter.png}}
+  \hfill
+  \caption{DM density for inner/outer (left/right panel) DM halo regions.}
+  \label{fig:slices}
+\end{figure*}
 
@@
 
-\section{Results}
-For convergence reasons and seeking to make our results
-observation-comparable, we restrict the sampling of the ellipsoidal
-parameters to radii between $1/16 R_{vir} and 2R_{vir}$ of the virial
-radius $R_{500}$, defined as the (DEFINITION OF VIRIAL RADIUS). All
-our results make use of this reference radius unless strictly stated
-otherwise.
-
 \subsection{The radial tendency of axial ratios}
-To have a more complete picture about the effect of baryons on the DM
-halo shape, we begin by verifying/understanding the radial evolution
-(dependence?) of the shape. In the case of DM-only simulations, it is
-expected that halos get monotonically rounder at larger radii due to
-(the gravitational effect of inner shells?) \citep{Vera-Ciro et
-  al. 2012}. A graphic example of this rounding can be checked on
-figure \ref{fig:slices}, where we plot the a projection of a DM-only
-halo aligned with the calculated minor axis at two different radius
-together with the estimated projected ellipsoidal. Formally, this
-effect is reflected in the axial ratios $b/a,c/a$, which tend to unity
-on the outerskirts of the halo. As a representative sample of this
-relations, we show on figure \ref{fig:DM relation} the evolution, for
-a specific halo, of the axial ratios $b/a,c/a$ and the triaxiality
-parameter $T=\frac{a^2-b^2}{a^2-c^2}$ in a wide range of radii.
-
-\begin{figure}
-  \centering
-  \subfloat[halo 27 DM shape at small radius]{\includegraphics[width=0.5\columnwidth]{./pics/MHD_Vs_DM/level4_DM_halo_27_inner.png}}
-  \hfill
-  \subfloat[halo 27 DM shape at big radius]{\includegraphics[width=0.5\columnwidth]{./pics/MHD_Vs_DM/level4_DM_halo_27_outter.png}}
-  \hfill
-  \caption{DM density for inner (outer) parts of the halo 27 on the left (right) part. The horizontal (vertical) axes are aligned to the major (medium) axes. (optimaze space and description) }
-  \label{fig:slices}
-\end{figure}
 

### 2019-01-27 Paper/paper.tex
graficas
Tablas informacion halos

@@
 
+\begin{table}[h]
+\centering
+\begin{tabular}{l?cc?cc?cc?cc}
+\hline
+\hline
+Halo & \multicolumn{2}{c?}{$N_P$/$10^6$} & \multicolumn{2}{c?}{$M_P$/$10^5M_\odot$} & \multicolumn{2}{c?}{$R_{vir}$/Kpc}&\multicolumn{2}{c}{$M_{vir}$/$10^{14}M_\odot$}  \\ \hdashline
+& DM & MHD& DM & MHD& DM & MHD& DM & MHD\\ \hline \hline
+halo 1&4.068&2.447&2.397&2.022&196.927&187.674&9.062&7.844\\
+halo 2&5.625&5.457&2.481&2.093&235.094&233.934&15.418&15.191\\
+halo 3&3.826&3.852&2.645&2.231&210.693&210.955&11.099&11.141\\
+halo 4&4.585&4.530&2.590&2.185&219.378&215.438&12.529&11.866\\
+halo 5&3.262&3.290&2.533&2.137&196.984&197.246&9.071&9.106\\ \hdashline
+\rowcolor{blue!30} halo 6&3.184&3.110&2.337&1.972&191.840&189.342&8.378&8.054\\ \hdashline
+halo 7&3.878&3.729&2.296&1.937&197.864&196.509&9.193&9.005\\
+halo 8&2.772&2.796&2.451&2.068&190.716&191.764&8.231&8.368\\
+halo 9&3.038&3.010&2.738&2.310&195.826&190.640&8.911&8.222\\
+halo 10&2.700&2.751&2.541&2.144&187.139&188.147&7.777&7.904\\
+halo 11&4.146&4.116&2.541&2.144&221.821&219.568&12.952&12.560\\
+halo 12&2.865&2.908&2.645&2.231&192.280&192.038&8.436&8.404\\
+halo 13&3.520&3.600&2.393&2.019&202.139&203.815&9.801&10.048\\
+halo 14&4.200&4.475&2.499&2.108&215.535&218.927&11.882&12.453\\
+halo 15&2.888&2.845&2.541&2.144&199.848&200.658&9.471&9.588\\ \hdashline
+\rowcolor{blue!30} halo 16&3.821&3.871&2.499&2.108&212.590&212.632&11.401&11.408\\ \hdashline
+halo 17&2.752&2.781&2.552&2.153&188.067&187.404&7.893&7.811\\
+halo 18&3.770&3.624&2.738&2.310&201.124&207.293&9.655&10.571\\
+halo 19&2.989&3.086&2.645&2.231&200.244&200.325&9.527&9.540\\
+halo 20&3.903&3.822&2.481&2.093&210.097&211.423&11.005&11.214\\ \hdashline
+\rowcolor{blue!30} halo 21&4.105&4.075&2.640&2.227&219.527&219.823&12.555&12.604\\ \hdashline
+halo 22&2.794&2.766&2.625&2.215&188.363&184.801&7.931&7.489\\ \hdashline
+\rowcolor{blue!30} halo 23&3.977&4.073&2.795&2.358&217.768&215.959&12.254&11.952\\\hdashline
+\rowcolor{blue!30} halo 24&4.466&4.426&2.522&2.127&217.440&215.147&12.199&11.817\\ \hdashline
+halo 25&2.902&2.806&2.645&2.231&199.922&198.299&9.482&9.254\\
+halo 26&4.610&4.716&2.506&2.115&219.984&218.939&12.633&12.454\\\hdashline
+\rowcolor{blue!30} halo 27&5.060&5.018&2.590&2.185&228.036&226.225&14.071&13.740\\ \hdashline
+halo 28&4.184&4.276&2.645&2.231&216.979&217.997&12.121&12.294\\
+halo 29&4.827&4.613&2.499&2.108&225.791&219.935&13.660&12.625\\
+halo 30&3.268&3.112&2.579&2.176&195.043&194.741&8.805&8.763\\
+\hline
+\hline
+\end{tabular}
+\caption{Specifications of each level 4 galaxy (halo).
+The DM and MHD versions of each parameters are presented together.
+The columns of this table indicate: (1) Halo name, (2,3) Number of (millions) of DM particles belonging to the halo, (4,5) Mass per particle in $10^5M_\odot$, (6,7) Virial radius (R TopHat 200) of the halo in Kpc, (8,9) Virial mass of the halo in $10^{14}M_\odot$.}
+\label{tab:level4}
+\end{table}
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{l?cc?cc?cc?cc}
+\hline
+\hline
+Halo & \multicolumn{2}{c?}{$N_P$/$10^6$} & \multicolumn{2}{c?}{$M_P$/$10^5M_\odot$} & \multicolumn{2}{c?}{$R_{vir}$/Kpc}&\multicolumn{2}{c}{$M_{vir}$/$10^{14}M_\odot$}  \\ \hdashline
+& DM & MHD& DM & MHD& DM & MHD& DM & MHD\\ \hline \hline
+halo 6&24.902&24.185&0.292&0.246&191.741&188.367&8.365&7.932\\
+halo 16&29.750&30.334&0.312&0.263&212.622&212.542&11.406&11.395\\
+halo 21&31.993&31.503&0.330&0.278&219.731&220.250&12.588&12.679\\
+halo 23&31.379&31.618&0.349&0.295&217.793&213.358&12.259&11.524\\
+halo 24&34.987&35.153&0.315&0.266&217.313&213.963&12.179&11.624\\
+halo 27&39.617&39.056&0.324&0.273&227.908&223.484&14.048&13.244\\
+\hline
+\hline
+\end{tabular}
+\caption{Specifications of each level 3 galaxy (halo).
+The DM and MHD versions of each parameters are presented together.
+The columns of this table indicate: (1) Halo name, (2,3) Number of (millions) of DM particles belonging to the halo, (4,5) Mass per particle in $10^5M_\odot$, (6,7) Virial radius (R TopHat 200) of the halo in Kpc, (8,9) Virial mass of the halo in $10^{14}M_\odot$.}
+\label{tab:level3}
+\end{table}
+
 \section{Determining the halo shape}
@@
 \end{figure*}
-
- \bibliographystyle{mnras}
- \bibliography{references}
-\end{document}
 
@@
 
+ \bibliographystyle{mnras}
+ \bibliography{references}
 \end{document}

### 2019-01-27 Paper/paper.tex
Quick Plot descriptions: To improve later

@@
   \hfill
-  \caption{DM density for inner/outer (left/right panel) DM halo regions.}
+  \caption{DM density for inner/outer (left/right panel) DM halo regions.
+
+  Slice 20 percent of the max-min range in the "z" position of particles belonging to the main structure, centered at halo defined position (calculated with most bounded particle) }
+  % definition of the input positions
+  % Gets the length of the main structure particles /// 0 - Principal halo, 1 - DM
+  %  cut = subSn.group.GroupLenType[0,1]
+  % graphs are calculated using the following YT command
+  % p = yt.ProjectionPlot(ds, 'z', nn_density, center=c, weight_field=nn_density, width=(0.2*(npos.max()-npos.min()), 'kpc'))
+
   \label{fig:slices}
@@
 {\includegraphics[width=0.8\columnwidth]{./pics/halo16.png}}
-\caption{Radial profile for axial ratios and the triaxiality parameter $T=\frac{1-b/a}{1-c/a}$ for halo 16.}
+\caption{Radial profile for axial ratios and the triaxiality parameter $T=\frac{1-b/a}{1-c/a}$ for halo 16.
+
+Radial profile was sampled at redshift 0 and there are two sets of lines showing MHD and DM-only versions of the axial ratios profile}
 \label{fig:DM_MHD}
@@
   \hfill
-  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. Errorbar shows median and errors for each sampled radii. }
+  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. (DM only)\\
+   Each dot represents the shape characterization of each halo at the 2 times the virial radius and a  1/16 fraction of the virial radius differentiated by color.\\   
+  Errorbar shows median and errors for each sampled radii.\\
+  Conclusion: DM halos are rounder on the outerskirts }
   \label{fig:Triax_DM}
@@
   \hfill
-  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. Errorbar
-    shows median and errors for each sampled radii. } 
+  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. (MHD only)\\
+   Each dot represents the shape characterization of each halo at the 2 times the virial radius and a  1/16 fraction of the virial radius differentiated by color.\\   
+  Errorbar shows median and errors for each sampled radii.\\
+  Conclusion: MHD halos are more oblate on the outer skirts: b/a changes while c/a remains practically constant (on average) } 
   \label{fig:Triax_MHD}
@@
 	\includegraphics[width=\columnwidth]{./pics/Delta asphericity Vs Star Density.png}
-    \caption{Difference in asphericities between MHD and DM shapes Vs Star Density of the simulation.}
+    \caption{Difference in asphericities between MHD and DM shapes Vs Star Density of the simulation.\\
+    Unsure about this graphic.\\
+    Take delta asphericity as the strength of the rounding effect of baryons.}
     \label{fig:Star_Density_effect}
@@
   \caption{Radial profile (comoving) of axial ratios for halo 16 in terms of redshift (color).
-This halo maintains its shape until $z\approx 1$ obviating the systematic rounding effect in time from asymmetric potentials.
-}
+This halo maintains its shape until $z\approx 1$ obviating the systematic rounding effect in time from asymmetric potentials.\\
+
+Each plot-line represents the radial profile at a determined redshift.\\
+Conclussion: Mainly for b/a, it increases for:\\ (1) for bigger radii (fixed redshift) \\
+												 (2) for lower redshift (fixed radius)\\
+
+It explains the correlation between radial profile and history, but does not require that curves match in the triaxial plane.  }
   \label{fig:RedshiftGood}
@@
 	\includegraphics[width=\columnwidth]{./pics/Redshift/halo_27_DM_Z_correlation.png}
-    \caption{Difference in asphericities between MHD and DM shapes Vs Star Density of the simulation.}
+    \caption{DM only\\
+    		 Radial profile at redshift 0 (dashed line)\\
+    		 Historical profile at virial radius R500 (colour line)\\
+    		 Example of a halo where there is some correlation between these two profiles, as usually happens for DM only simulations.\\
+    		 Conclusion: DM only halos usually (fraction?) have correlated shape profiles 
+    		 }
     \label{fig:DM Z Triax}
@@
 	\includegraphics[width=\columnwidth]{./pics/Redshift/halo_24_level3_MHD_Z_Triax.png}
-    \caption{Difference in asphericities between MHD and DM shapes Vs
-      Star Density of the simulation.} 
+    \caption{MHD\\
+    		 Radial profile at redshift 0 (dashed line)\\
+    		 Historical profile at virial radius R500 (colour line)\\
+    		 Example of a halo where there is no correlation between these two profiles, as usually happens in MHD\\
+    		 Conclusion: MHD halos usually (fraction?) have uncorrelated shape profiles 
+    		 } 
     \label{fig:MHD Z Triax} 
@@
   \hfill
-  \caption{Description of axes alignments }
+  \caption{Star: Minor Axis\\
+  		   Triangle: Medium Axis\\
+  		   Square: Major Axis\\
+  		   Color: Radii at which shape was sampled (show radii sampled)\\
+  		   Contour color: If orientation is above or below in this projection\\
+  		   Cross (black): Orientation of the stellar disk\\
+  		   Conclusion: Axes (minor) are not (generally) aligned with the stellar disk nor are they usually aligned with each other from different radii. We show some cases that may happen\\  }
   \label{fig:alignment}

### 2019-02-05 Paper/paper.tex
compila

--- 2019-01-22 Paper/paper.tex
@@
-% mnras_template.tex
-%
-% LaTeX template for creating an MNRAS paper
-%
-% v3.0 released 14 May 2015
-% (version numbers match those of mnras.cls)
-%
-% Copyright (C) Royal Astronomical Society 2015
-% Authors:
-% Keith T. Smith (Royal Astronomical Society)
-
-% Change log
-%
-% v3.0 May 2015
-%    Renamed to match the new package name
-%    Version number matches mnras.cls
-%    A few minor tweaks to wording
-% v1.0 September 2013
-%    Beta testing only - never publicly released
-%    First version: a simple (ish) template for creating an MNRAS paper
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Basic setup. Most papers should leave these options alone.
 \documentclass[a4paper,fleqn,usenatbib]{mnras}
@@
 
-% Only include extra packages if you really need them. Common packages are:
 \usepackage{graphicx}	% Including figure files
@@
 
-% Included by user
 \usepackage{multirow}
@@
    {\endminipage\par\bigskip}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
-
-% Please keep new commands to a minimum, and use \newcommand not \def to avoid
-% overwriting existing commands. Example:
-%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
-
-% Title of the paper, and the short title which is used in the headers.
-% Keep the title short and informative.
 \title[MW DM halo shape in AURIGA]{The expected shape of the Milky Way's Dark Matter halo}
 
-% The list of authors, and the short list which is used in the headers.
-% If you need two or more lines of authors, add an extra line using \newauthor
 \author[Jesus Prada,  Jaime E. Forero-Romero, Volker Springel ]{
@@
 simulations \citep{auriga}. 
-The objects in those simulations were selected from a set of 30 isolated halos in
-the Evolution and Assembly of GaLaxies and their Environments (EAGLE)
-project \citep{Eagle}. 
+The objects in those simulations were selected from a set of 30
+isolated halos in the Evolution and Assembly of GaLaxies and their
+Environments (EAGLE)  project \citep{Eagle}.   
 These halos were randomly selected from a sample of the most isolated
-quartile of halos whose virial mass $M_{200}$ varied between
-$10^{12}M_\odot$ and $2\times 10^{12}M_\odot$. 
+halos whose virial mass $M_{200}$ varied between $10^{12}M_\odot$ and
+$2\times 10^{12}M_\odot$. 
 These halos were re-simulated with higher resolution an varying
@@
 magneto-hydrodynamical (MHD) physics.
+
+\begin{table*}
+\centering
+\begin{tabular}{l|cc|cc|cc|cc}
+\hline
+\hline
+Halo & \multicolumn{2}{c}{$N_P$/$10^6$} & \multicolumn{2}{c}{$M_P$/$10^5M_\odot$} & 
+\multicolumn{2}{c}{$R_{vir}$/Kpc} & \multicolumn{2}{c}{$M_{vir}$/$10^{14} M_\odot$}  \\ \hline
+& DM & MHD& DM & MHD& DM & MHD& DM & MHD\\ \hline \hline
+halo 1&4.068&2.447&2.397&2.022&196.927&187.674&9.062&7.844\\
+halo 2&5.625&5.457&2.481&2.093&235.094&233.934&15.418&15.191\\
+halo 3&3.826&3.852&2.645&2.231&210.693&210.955&11.099&11.141\\
+halo 4&4.585&4.530&2.590&2.185&219.378&215.438&12.529&11.866\\
+halo 5&3.262&3.290&2.533&2.137&196.984&197.246&9.071&9.106\\ \hline
+halo 6&3.184&3.110&2.337&1.972&191.840&189.342&8.378&8.054\\ \hline
+halo 7&3.878&3.729&2.296&1.937&197.864&196.509&9.193&9.005\\
+halo 8&2.772&2.796&2.451&2.068&190.716&191.764&8.231&8.368\\
+halo 9&3.038&3.010&2.738&2.310&195.826&190.640&8.911&8.222\\
+halo 10&2.700&2.751&2.541&2.144&187.139&188.147&7.777&7.904\\
+halo 11&4.146&4.116&2.541&2.144&221.821&219.568&12.952&12.560\\
+halo 12&2.865&2.908&2.645&2.231&192.280&192.038&8.436&8.404\\
+halo 13&3.520&3.600&2.393&2.019&202.139&203.815&9.801&10.048\\
+halo 14&4.200&4.475&2.499&2.108&215.535&218.927&11.882&12.453\\
+halo 15&2.888&2.845&2.541&2.144&199.848&200.658&9.471&9.588\\ \hline
+halo 16&3.821&3.871&2.499&2.108&212.590&212.632&11.401&11.408\\ \hline
+halo 17&2.752&2.781&2.552&2.153&188.067&187.404&7.893&7.811\\
+halo 18&3.770&3.624&2.738&2.310&201.124&207.293&9.655&10.571\\
+halo 19&2.989&3.086&2.645&2.231&200.244&200.325&9.527&9.540\\
+halo 20&3.903&3.822&2.481&2.093&210.097&211.423&11.005&11.214\\ \hline
+halo 21&4.105&4.075&2.640&2.227&219.527&219.823&12.555&12.604\\ \hline
+halo 22&2.794&2.766&2.625&2.215&188.363&184.801&7.931&7.489\\ \hline
+halo 23&3.977&4.073&2.795&2.358&217.768&215.959&12.254&11.952\\\hline
+halo 24&4.466&4.426&2.522&2.127&217.440&215.147&12.199&11.817\\ \hline
+halo 25&2.902&2.806&2.645&2.231&199.922&198.299&9.482&9.254\\
+halo 26&4.610&4.716&2.506&2.115&219.984&218.939&12.633&12.454\\\hline
+halo 27&5.060&5.018&2.590&2.185&228.036&226.225&14.071&13.740\\ \hline
+halo 28&4.184&4.276&2.645&2.231&216.979&217.997&12.121&12.294\\
+halo 29&4.827&4.613&2.499&2.108&225.791&219.935&13.660&12.625\\
+halo 30&3.268&3.112&2.579&2.176&195.043&194.741&8.805&8.763\\
+\hline
+\hline
+\end{tabular}
+\caption{Specifications of each level 4 galaxy (halo).
+The DM and MHD versions of each parameters are presented together.
+The columns of this table indicate: (1) Halo name, (2,3) Number of (millions) of DM particles belonging to the halo, (4,5) Mass per particle in $10^5M_\odot$, (6,7) Virial radius (R TopHat 200) of the halo in Kpc, (8,9) Virial mass of the halo in $10^{14}M_\odot$.}
+\label{tab:level4}
+\end{table*}
+
+\begin{table*}
+\centering
+\begin{tabular}{l?cc?cc?cc?cc}
+\hline
+\hline
+Halo & \multicolumn{2}{c?}{$N_P$/$10^6$} & \multicolumn{2}{c?}{$M_P$/$10^5M_\odot$} & \multicolumn{2}{c?}{$R_{vir}$/Kpc}&\multicolumn{2}{c}{$M_{vir}$/$10^{14}M_\odot$}  \\ \hline
+& DM & MHD& DM & MHD& DM & MHD& DM & MHD\\ \hline \hline
+halo 6&24.902&24.185&0.292&0.246&191.741&188.367&8.365&7.932\\
+halo 16&29.750&30.334&0.312&0.263&212.622&212.542&11.406&11.395\\
+halo 21&31.993&31.503&0.330&0.278&219.731&220.250&12.588&12.679\\
+halo 23&31.379&31.618&0.349&0.295&217.793&213.358&12.259&11.524\\
+halo 24&34.987&35.153&0.315&0.266&217.313&213.963&12.179&11.624\\
+halo 27&39.617&39.056&0.324&0.273&227.908&223.484&14.048&13.244\\
+\hline
+\hline
+\end{tabular}
+\caption{Specifications of each level 3 galaxy (halo).
+The DM and MHD versions of each parameters are presented together.
+The columns of this table indicate: (1) Halo name, (2,3) Number of (millions) of DM particles belonging to the halo, (4,5) Mass per particle in $10^5M_\odot$, (6,7) Virial radius (R TopHat 200) of the halo in Kpc, (8,9) Virial mass of the halo in $10^{14}M_\odot$.}
+\label{tab:level3}
+\end{table*}
 
@@
   \hfill
-  \caption{DM density for inner/outer (left/right panel) DM halo regions.}
+  \caption{DM density for inner/outer (left/right panel) DM halo regions.  
+  Slice 20 percent of the max-min range in the "z" position of
+  particles belonging to the main structure, centered at halo defined
+  position (calculated with most bounded particle) }  
   \label{fig:slices}
 \end{figure*}
-
- \bibliographystyle{mnras}
- \bibliography{references}
-\end{document}
 
@@
 {\includegraphics[width=0.8\columnwidth]{./pics/halo16.png}}
-\caption{Radial profile for axial ratios and the triaxiality parameter $T=\frac{1-b/a}{1-c/a}$ for halo 16.}
+\caption{Radial profile for axial ratios and the triaxiality parameter $T=\frac{1-b/a}{1-c/a}$ for halo 16.
+Radial profile was sampled at redshift 0 and there are two sets of
+lines showing MHD and DM-only versions of the axial ratios profile}
 \label{fig:DM_MHD}
@@
 \begin{figure}
-  \centering
  \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_DM.png}
-
-  \hfill
-  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. Errorbar shows median and errors for each sampled radii. }
+  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. (DM only)
+   Each dot represents the shape characterization of each halo at the 2 times the virial radius and a  1/16 fraction of the virial radius differentiated by color.
+  Errorbar shows median and errors for each sampled radii.
+  Conclusion: DM halos are rounder on the outskirts}
   \label{fig:Triax_DM}
@@
   least in the vicinities of the disk, to ensure its stability
-  \cite{disk stability}. However,)))} not much is said about its
+  . However,)))} not much is said about its
 dependence with radius as previous studies focus rather on the effects
@@
 \begin{figure}
-  \centering
  \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_MHD.png}
-  \hfill
-  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. Errorbar
-    shows median and errors for each sampled radii. } 
+  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. (MHD only)
+   Each dot represents the shape characterization of each halo at the
+   2 times the virial radius and a  1/16 fraction of the virial radius
+   differentiated by color. 
+  Errorbar shows median and errors for each sampled radii.
+  Conclusion: MHD halos are more oblate on the outer skirts: b/a
+  changes while c/a remains practically constant (on average)}
   \label{fig:Triax_MHD}
@@
 results with the analytic expression of the
-$(1-q_{\phi})\frac{1}{3}(1-q_{\rho})$ \citep[Binney and Tremaine
-  year]{Binney and tremaine}, taking the volume-enclosed axial ratios
+$(1-q_{\phi})\frac{1}{3}(1-q_{\rho})$ \citep{Binney_and_Tremaine_2008}, taking the volume-enclosed axial ratios
 as an approximation for the isodensity contour ratios
@@
 \begin{figure}
-	% To include a figure from a file named example.*
-	% Allowable file formats are eps or ps if compiling using latex
-	% or pdf, png, jpg if compiling using pdflatex
   \includegraphics[width=\columnwidth]{./pics/Delta asphericity Vs Star Density.png}
-    \caption{Difference in asphericities between MHD and DM shapes Vs Star Density of the simulation.}
+  \caption{Difference in asphericities between MHD and DM shapes Vs
+    Star Density of the simulation. Unsure about this graphic. Take
+    delta asphericity as the strength of the rounding effect of
+    baryons.}  
   \label{fig:Star_Density_effect}
@@
 expected by the continuous influence of the gravitational potential
-\cite{VeraCiro}. In figure \ref{fig:RedshiftGood} we present a
-representative example.
+\cite{Vera-Ciro_et_al._2011}. In figure \ref{fig:RedshiftGood} we
+present a representative example.
 
 \begin{figure}
-  \centering
   \subfloat[halo 16 DM]{\includegraphics[width=0.5\columnwidth]{./pics/Redshift/halo_16_level3_DM_Z.png}}
-  \hfill
   \subfloat[halo 16 MHD]{\includegraphics[width=0.5\columnwidth]{./pics/Redshift/halo_16_level3_MHD_Z.png}}
-  \caption{Radial profile (comoving) of axial ratios for halo 16 in terms of redshift (color).
-This halo maintains its shape until $z\approx 1$ obviating the systematic rounding effect in time from asymmetric potentials.
-}
+  \caption{Radial profile (comoving) of axial ratios for halo 16 in
+    terms of redshift (color). This halo maintains its shape until
+    $z\approx 1$ obviating the systematic rounding effect in time from
+    asymmetric potentials. Each plot-line represents the radial
+    profile at a determined redshift. Conclussion: Mainly for b/a, it increases for:
+    (1) for bigger radii (fixed redshift)(2) for lower redshift (fixed
+    radius) It explains the correlation between radial profile and
+    history, but does not require that curves match in the triaxial
+    plane.}
   \label{fig:RedshiftGood}
@@
   \includegraphics[width=\columnwidth]{./pics/Redshift/halo_27_DM_Z_correlation.png}
-    \caption{Difference in asphericities between MHD and DM shapes Vs Star Density of the simulation.}
+  \caption{DM only Radial profile at redshift 0 (dashed line)
+    Historical profile at virial radius R500 (colour line). Example
+    of a halo where there is some correlation between these two
+    profiles, as usually happens for DM only
+    simulations. Conclusion: DM only halos usually (fraction?) have
+    correlated shape profiles.} 
   \label{fig:DM Z Triax}
-
 \end{figure}
@@
   \includegraphics[width=\columnwidth]{./pics/Redshift/halo_24_level3_MHD_Z_Triax.png}
-    \caption{Difference in asphericities between MHD and DM shapes Vs
-      Star Density of the simulation.} 
+  \caption{MHD. Radial profile at redshift 0 (dashed line)
+    Historical profile at virial radius R500 (colour line)
+    Example of a halo where there is no correlation
+    between these two profiles, as usually happens in
+    MHD. Conclusion: MHD halos usually (fraction?) have uncorrelated shape profiles.}
     \label{fig:MHD Z Triax} 
@@
   \hfill
-  \caption{Description of axes alignments }
+  \caption{Star: Minor Axis
+    Triangle: Medium Axis
+    Square: Major Axis
+    Color: Radii at which shape was sampled (show radii sampled)
+    Contour color: If orientation is above or below in this projection
+    Cross (black): Orientation of the stellar disk
+    Conclusion: Axes (minor) are not (generally) aligned with the
+    stellar disk nor are they usually aligned with each other from
+    different radii. We show some cases that may happen.} 
   \label{fig:alignment}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-
-% The best way to enter references is to use BibTeX:
-
-% Alternatively you could enter them by hand, like this:
-% This method is tedious and prone to error if you have lots of references
-\begin{thebibliography}{99}
-\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
-Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
-\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
-Others S., 2012, Journal of Interesting Stuff, 17, 198
-\end{thebibliography}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-\section{Some extra material}
-
-If you want to present additional material which would interrupt the flow of the main paper,
-it can be placed in an Appendix which appears after the list of references.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Don't change these lines
-\bsp	% typesetting comment
-\label{lastpage}
-
+ \bibliographystyle{mnras}
+ \bibliography{references}
 \end{document}
-
-% End of mnras_template.tex

### 2019-02-05 Paper/paper.tex
tablas corregidas

@@
 Halo & \multicolumn{2}{c}{$N_P$/$10^6$} & \multicolumn{2}{c}{$M_P$/$10^5M_\odot$} & 
-\multicolumn{2}{c}{$R_{vir}$/Kpc} & \multicolumn{2}{c}{$M_{vir}$/$10^{14} M_\odot$}  \\ \hline
+\multicolumn{2}{c}{$R_{vir}$/kpc} & \multicolumn{2}{c}{$M_{vir}$/$10^{14} M_\odot$}  \\ \hline
 & DM & MHD& DM & MHD& DM & MHD& DM & MHD\\ \hline \hline
@@
 halo 4&4.585&4.530&2.590&2.185&219.378&215.438&12.529&11.866\\
-halo 5&3.262&3.290&2.533&2.137&196.984&197.246&9.071&9.106\\ \hline
-halo 6&3.184&3.110&2.337&1.972&191.840&189.342&8.378&8.054\\ \hline
+halo 5&3.262&3.290&2.533&2.137&196.984&197.246&9.071&9.106\\ 
+halo 6 ($\star$)&3.184&3.110&2.337&1.972&191.840&189.342&8.378&8.054\\ 
 halo 7&3.878&3.729&2.296&1.937&197.864&196.509&9.193&9.005\\
@@
 halo 14&4.200&4.475&2.499&2.108&215.535&218.927&11.882&12.453\\
-halo 15&2.888&2.845&2.541&2.144&199.848&200.658&9.471&9.588\\ \hline
-halo 16&3.821&3.871&2.499&2.108&212.590&212.632&11.401&11.408\\ \hline
+halo 15&2.888&2.845&2.541&2.144&199.848&200.658&9.471&9.588\\ 
+halo 16 ($\star$)&3.821&3.871&2.499&2.108&212.590&212.632&11.401&11.408\\ 
 halo 17&2.752&2.781&2.552&2.153&188.067&187.404&7.893&7.811\\
@@
 halo 19&2.989&3.086&2.645&2.231&200.244&200.325&9.527&9.540\\
-halo 20&3.903&3.822&2.481&2.093&210.097&211.423&11.005&11.214\\ \hline
-halo 21&4.105&4.075&2.640&2.227&219.527&219.823&12.555&12.604\\ \hline
-halo 22&2.794&2.766&2.625&2.215&188.363&184.801&7.931&7.489\\ \hline
-halo 23&3.977&4.073&2.795&2.358&217.768&215.959&12.254&11.952\\\hline
-halo 24&4.466&4.426&2.522&2.127&217.440&215.147&12.199&11.817\\ \hline
+halo 20&3.903&3.822&2.481&2.093&210.097&211.423&11.005&11.214\\ 
+halo 21 ($\star$) &4.105&4.075&2.640&2.227&219.527&219.823&12.555&12.604\\ 
+halo 22&2.794&2.766&2.625&2.215&188.363&184.801&7.931&7.489\\ 
+halo 23 ($\star$) &3.977&4.073&2.795&2.358&217.768&215.959&12.254&11.952\\
+halo 24 ($\star$) &4.466&4.426&2.522&2.127&217.440&215.147&12.199&11.817\\ 
 halo 25&2.902&2.806&2.645&2.231&199.922&198.299&9.482&9.254\\
-halo 26&4.610&4.716&2.506&2.115&219.984&218.939&12.633&12.454\\\hline
-halo 27&5.060&5.018&2.590&2.185&228.036&226.225&14.071&13.740\\ \hline
-halo 28&4.184&4.276&2.645&2.231&216.979&217.997&12.121&12.294\\
-halo 29&4.827&4.613&2.499&2.108&225.791&219.935&13.660&12.625\\
-halo 30&3.268&3.112&2.579&2.176&195.043&194.741&8.805&8.763\\
+halo 26 &4.610&4.716&2.506&2.115&219.984&218.939&12.633&12.454\\
+halo 27 ($\star$) & 5.060&5.018&2.590&2.185&228.036&226.225&14.071&13.740\\ 
+halo 28 & 4.184&4.276&2.645&2.231&216.979&217.997&12.121&12.294\\
+halo 29 & 4.827&4.613&2.499&2.108&225.791&219.935&13.660&12.625\\
+halo 30 & 3.268&3.112&2.579&2.176&195.043&194.741&8.805&8.763\\
 \hline
@@
   The DM and MHD versions of each parameters are presented together. 
-The columns of this table indicate: (1) Halo name, (2,3) Number of (millions) of DM particles belonging to the halo, (4,5) Mass per particle in $10^5M_\odot$, (6,7) Virial radius (R TopHat 200) of the halo in Kpc, (8,9) Virial mass of the halo in $10^{14}M_\odot$.}
+  The columns correspond to: (1) Halo name, (2,3) Millions of DM
+  particles belonging to the halo, (4,5) DM particle mass in
+  $10^5M_\odot$, (6,7) Halo Virial radius in kpc and (8,9) halo virial
+  mass in $10^{14}M_\odot$. Halos marked with a star ($\star$) are
+  correspond to halos resimulated at higher resolution (level 3).}  
 \label{tab:level4}
@@
 \hline
-Halo & \multicolumn{2}{c?}{$N_P$/$10^6$} & \multicolumn{2}{c?}{$M_P$/$10^5M_\odot$} & \multicolumn{2}{c?}{$R_{vir}$/Kpc}&\multicolumn{2}{c}{$M_{vir}$/$10^{14}M_\odot$}  \\ \hline
+Halo & \multicolumn{2}{c?}{$N_P$/$10^6$} & \multicolumn{2}{c?}{$M_P$/$10^5M_\odot$} & \multicolumn{2}{c?}{$R_{vir}$/kpc}&\multicolumn{2}{c}{$M_{vir}$/$10^{14}M_\odot$}  \\ \hline
 & DM & MHD& DM & MHD& DM & MHD& DM & MHD\\ \hline \hline
@@
 \end{tabular}
-\caption{Specifications of each level 3 galaxy (halo).
-The DM and MHD versions of each parameters are presented together.
-The columns of this table indicate: (1) Halo name, (2,3) Number of (millions) of DM particles belonging to the halo, (4,5) Mass per particle in $10^5M_\odot$, (6,7) Virial radius (R TopHat 200) of the halo in Kpc, (8,9) Virial mass of the halo in $10^{14}M_\odot$.}
+\caption{Same layout Table \ref{tab:level3} for Level 3 simulations (higher
+  resolution than Level 4 simulations).}
 \label{tab:level3}
@@
 some things are noticeable: first, the DM halo is almost perfectly
-oblate around $\approx 10-30$Kpc, second, its axial ratio $b/a$ start
-decreasing very slowly after $50Kpc$ and below $10Kpc$ and third, its
+oblate around $\approx 10-30$kpc, second, its axial ratio $b/a$ start
+decreasing very slowly after $50kpc$ and below $10kpc$ and third, its
 axial ratio $c/a$ does not exhibit noticeable change in the whole
@@
 flattened axisymmetric galactic disk. It is also reasonable that this
-effect is not as strong at $\approx 100$Kpc, where the disk potential
+effect is not as strong at $\approx 100$kpc, where the disk potential
 is dimmer compared to the DM halo potential. Keeping this in mind, one
@@
 actually explain the deviation from oblateness of MHD halos at
-$r<10$Kpc. In other words, if the disk is perfectly axisymmetric,
-there must be some source of triaxiality at $r<10$Kpc to explain the
+$r<10$kpc. In other words, if the disk is perfectly axisymmetric,
+there must be some source of triaxiality at $r<10$kpc to explain the
 low axial ratios.

### 2019-02-13 Paper/paper.tex
edit

@@
 
-There are two main ways to estimate the DM halo shape at a fixed
-radius: by computing isopotential or isodensity surfaces.
-Observational inference models estimate the shape from the
-isopotential contours, while simulations work with the isodensity
-contours which can be  directly calculated from particle positions.  
-However, the density contours are not smooth and are very 
-sensitive to the presence of small satelites.
+The DM halo shape at a fixed radius is an estimate of either
+the isopotential or isodensity surfaces.  
+Observational inference models usually estimate the 
+isopotential contours which are probed by tracers (gas, stars), while
+simulations work with the isodensity contours which can be directly
+calculated from particle positions.
+
+However, in numerical simulations the density contours are not smooth
+and are sensitive to the presence of small satelites. 
 For this reason we choose to measure the shape by taking
 volume-enclosed particles, rather than shell-enclosed.  
-
 We follow the shape measurement method presented by
@@
 We start the calculations taking into account particles within a
-sphere of radius $R$ and then  recharacterize the triaxial parameters by taking into account
-particles within an ellipsoid of semi-axes $r,r/q,r/s$ and weighted
-distance $d^2=x^2+(y/q)^2+(z/s)^2$, where $q = b/a$ and $s=c/a$
-are the previously calculated axial ratios. 
+sphere of radius $R$ and then  recharacterize the triaxial parameters
+by taking into account particles within an ellipsoid of semi-axes
+$r,r/q,r/s$ and re-scaled distance $d^2=x^2+(y/q)^2+(z/s)^2$, where $q
+= b/a$ and $s=c/a$ are the previously calculated axial ratios. 
 We repeat this process until the average deviation of semi-axes is
@@
 radius enclosing a sphere with 500 times the average dark matter
-density of the Universe. All our results use of this reference radius
+density of the Universe. 
+All our results use of this reference radius
 unless strictly stated otherwise. 
@@
 
-\subsection{Radial trends}
-
-In DM-only simulations halos are monotonically rounder with increasing
-radius, this confirms results already reported in the literature
-\citep{Vera-Ciro_et_al._2011}. 
-Figure \ref{fig:slices} illustrates this effect.
-There we show the DM density of a DM-only halo at redshift zero.
-The halo is aligned with the minor axis. 
-The ellipsoid shows the outermost boundary of the estimated shape ellipsoid.
-Formally, this effect is reflected in the axial ratios $b/a,c/a$, which tend to unity
-on the outerskirts of the halo. As a representative sample of this
-relations, we show on figure \ref{fig:DM relation} the evolution, for
-a specific halo, of the axial ratios $b/a,c/a$ and the triaxiality
-parameter $T=\frac{a^2-b^2}{a^2-c^2}$ in a wide range of radii.
+\subsection{Radial trends at $z=0$}
 
@@
   \centering
-  \subfloat[halo 27 DM shape at small radius]{\includegraphics[width=0.5\textwidth]{./pics/MHD_Vs_DM/level4_DM_halo_27_inner.png}}
+  \subfloat[halo 27 DM shape at small
+    radius]{\includegraphics[width=0.5\textwidth]{./pics/MHD_Vs_DM/level4_DM_halo_27_inner.png}} 
   \hfill
-  \subfloat[halo 27 DM shape at big radius]{\includegraphics[width=0.5\textwidth]{./pics/MHD_Vs_DM/level4_DM_halo_27_outter.png}}
+  \subfloat[halo 27 DM shape at big
+    radius]{\includegraphics[width=0.5\textwidth]{./pics/MHD_Vs_DM/level4_DM_halo_27_outter.png}} 
   \hfill 
@@
 \end{figure*}
+
+We find that in DM-only simulations halos are monotonically rounder
+with increasing radius, confirming results already reported in the
+literature \citep{Vera-Ciro_et_al._2011}. 
+Figure \ref{fig:slices} illustrates this effect.
+There we show the density a DM-only halo at redshift zero in a thin
+slice passing through the halo's centre, each panel shows the halo at
+different radii.
+The ellipse plotted over the contours indicates the outermost
+boundary of the estimated shape ellipsoid. 
+Indeed, the ellipse panel on the right (outer halo) is rounder than
+the ellipse on the left (inner halo).
+
+We quantify this effect by plotting the axial ratios $b/a$, $c/a$,
+$c/b$ and the triaxiality $T\equiv \frac{1-b/a}{1-c/a}$ as a
+function of radius. 
+As a representative sample of this
+relations, we show on figure \ref{fig:triaxial_radius} the evolution, for
+a specific halo, of the axial ratios $b/a,c/a$ and the triaxiality
+parameter $T=\frac{a^2-b^2}{a^2-c^2}$ in a wide range of radii.
+
+\begin{figure}
+\centering
+{\includegraphics[width=0.8\columnwidth]{./pics/halo16.png}}
+\caption{Radial profile for the axial ratios and the triaxiality parameter
+  $T=\frac{1-b/a}{1-c/a}$ at redshift $z=0$. 
+  Radial profile was sampled at
+  redshift 0 and there are two sets of lines showing MHD and DM-only
+  versions of the axial ratios profile} \label{fig:triaxial_radius}
+\end{figure}
 
@@
 $b/a$. Check Vera-ciro onthis.
-
-\begin{figure}
-\centering
-{\includegraphics[width=0.8\columnwidth]{./pics/halo16.png}}
-\caption{Radial profile for axial ratios and the triaxiality parameter $T=\frac{1-b/a}{1-c/a}$ for halo 16.
-Radial profile was sampled at redshift 0 and there are two sets of
-lines showing MHD and DM-only versions of the axial ratios profile}
-\label{fig:DM_MHD}
-\end{figure}
 

### 2019-02-13 Paper/paper.tex
edit

@@
 
-We quantify this effect by plotting the axial ratios $b/a$, $c/a$,
-$c/b$ and the triaxiality $T\equiv \frac{1-b/a}{1-c/a}$ as a
-function of radius. 
-As a representative sample of this
-relations, we show on figure \ref{fig:triaxial_radius} the evolution, for
-a specific halo, of the axial ratios $b/a,c/a$ and the triaxiality
-parameter $T=\frac{a^2-b^2}{a^2-c^2}$ in a wide range of radii.
-
-\begin{figure}
+\begin{figure*}
 \centering
-{\includegraphics[width=0.8\columnwidth]{./pics/halo16.png}}
+{\includegraphics[width=0.6\textwidth]{./pics/halo16.png}}
 \caption{Radial profile for the axial ratios and the triaxiality parameter
@@
   versions of the axial ratios profile} \label{fig:triaxial_radius}
-\end{figure}
+\end{figure*}
+
+We quantify this effect by plotting the axial ratios $b/a$, $c/a$,
+$c/b$ and the triaxiality $T\equiv \frac{1-b/a}{1-c/a}$ as a
+function of radius. 
+As a representative sample of this relations we show on figure
+\ref{fig:triaxial_radius} the radial trends for an specific halo at
+the highest resolution both for DM and MHD simulations.
+The continouse lines corresponds to the DM simulation and shows how
+the inner part of the halo $r\approx 1$\kpch has values of 
+$b/a=0.5$, $c/a=0.5$ while at the virial radius the same
+quantities increase to $b/a=0.9$, $c/a=0.6$; in turn the triaxiality
+decrease from $T\approx 1.0$\kpch to $T\approx=0.4$.
 

### 2019-02-13 Paper/paper.tex
edit

--- 2019-02-13 Paper/paper.tex
@@
 \newcolumntype{?}{!{\vrule width 1pt}}
+\newcommand{\Mpch}{\,{\rm Mpc}\,\ifmmode h^{-1}\else $h^{-1}$\fi}
+\newcommand{\kpch}{\,{\rm kpc}\,\ifmmode h^{-1}\else $h^{-1}$\fi}
+\newcommand{\kpc}{\,{\rm kpc}\,}
 
@@
   versions of the axial ratios profile} \label{fig:triaxial_radius}
-\end{figure}
+\end{figure*}
+
+We quantify this effect by plotting the axial ratios $q$, $s$,
+$s/q$ and the triaxiality $T\equiv \frac{1-q}{1-s}$ as a
+function of radius. 
+As a representative sample of this relations we show on Figure
+\ref{fig:triaxial_radius} the radial trends for Halo 16 at
+the highest resolution both for DM and MHD simulations.
+The continous lines correspond to the DM simulation and shows how
+the inner part of the halo $r\approx 1$\kpch has values of 
+$q=0.5$, $s=0.5$ while at the virial radius the same
+quantities increase to $q=0.85$, $s=0.6$; in turn the triaxiality
+decreases from $T\approx 1.0$ to $T\approx0.4$.
+
+In the same Figure \ref{fig:triaxial_radius} we also find one of the
+main results of our study: halos in MHD simulations are systematically rounder, at
+every radius, than its DM-only counterparts.  
+The dashed line in Figure \ref{fig:triaxial_radius} shows that at
+$r\approx 1$\kpch  in the MHD simulation we have $q=0.85, s=0.8$
+($q=0.5, s=0.5$ in DM) and at the virial radius $q=0.95, s=0.75$
+($q=0.85, s=0.6$ in DM).  
+However, the triaxiality trend is not as monotonous for MHD halos is
+it is in DM halos. 
+The triaxiality goes almost to zero at an intermediate radius,
+$r\approx 10$\kpc in the case of Halo 16 in Figure
+\ref{fig:triaxial_radius}, to increase again. {\bf pasa lo mismo para
+  todos los halos? es lo mismo para baja y alta resolucion de MHD?}
 

### 2019-02-14 Paper/paper.tex
edit

@@
 
-\title[MW DM halo shape in AURIGA]{The expected shape of the Milky Way's Dark Matter halo}
-
+\title[Dark Matter halo shape in the AURIGA simulations]{The shape of dark matter
+  halos in the AURIGA simulations}  
 \author[Jesus Prada,  Jaime E. Forero-Romero, Volker Springel ]{
@@
 
-\subsection{The radial tendency of axial ratios}
+Figure \ref{fig:triax_DM} summarizes this comparizon for all 30 halos
+in the Level 3 simulations. 
+Measurements at $R_{\rm vir}/16$ are represented by circlse while squares 
+are measurements at $R_{\rm vir}$. 
+All halos, except two, show that outer regions rounder than inner
+regions.
+The exceptions are cases where a merging substructures near  the
+halo's center give rise to perturbed axial ratios measurments. 
+Figure \ref{fig:triax_HDM} shows the same information, this time for
+the MHD simulations. 
+The main radial trend continues to hold, albet less pronounced; halos
+in MHD simulations are in general rounder than their DM counterparts
+and the increased roundness in outer regions is less pronounced on
+average.
 
-We found that most halos exhibit a monotonically-increasing somewhat
-steady tendency of its axial ratios $b/a,c/a$  with radius, which is
-well exemplified on figure \ref{fig:DM_MHD}. There are some special
-cases in which fluctuations of the local DM density field affects this
-relation, but in average, this monotonic and steady tendency is clear
-and can be consulted on table \ref{table:DM table}. To ilustrate the
-average behavior, as well as some peculiarities, we resume the results
-of the 30 auriga simulations on the figure \ref{fig:Triax_DM} where
-each shape represents a point in the triaxiality plane $c/a$ Vs
-$b/a$. Check Vera-ciro onthis.
+This situation is summarized Table \ref{table:shape}
+We summarize these resulta in Table \ref{table:shape}
 
@@
 \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_DM.png}
-  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. (DM only)
+\caption{Axial ratios for the 30 halos in the Level 3 DM simulations.
    Each dot represents the shape characterization of each halo at the 2 times the virial radius and a  1/16 fraction of the virial radius differentiated by color.
   Errorbar shows median and errors for each sampled radii.
-  Conclusion: DM halos are rounder on the outskirts}
-  \label{fig:Triax_DM}
+  Conclusion: DM halos are rounder on the outskirts {\bf Esto necesita
+  correccion. Debe ser a R1/16 y R (no 2R!)}}
+  \label{fig:triax_DM}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_MHD.png}
+  \caption{Axial ratios for the 30 halos in the Level 3 MHD
+    simulations. DM halos are rounder at larger radii than small radii. {\bf Esto
+      necesita correccion para que tambien sea a 
+      R1/16 y R.}}
+  \label{fig:triax_MHD}
 \end{figure}
@@
 \ref{MHD table} and figure \ref{fig:Triax_MHD}
-
-\begin{figure}
- \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_MHD.png}
-  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. (MHD only)
-   Each dot represents the shape characterization of each halo at the
-   2 times the virial radius and a  1/16 fraction of the virial radius
-   differentiated by color. 
-  Errorbar shows median and errors for each sampled radii.
-  Conclusion: MHD halos are more oblate on the outer skirts: b/a
-  changes while c/a remains practically constant (on average)}
-  \label{fig:Triax_MHD}
-\end{figure}
 

### 2019-02-19 Paper/paper.tex
edit

@@
 the MHD simulations. 
-The main radial trend continues to hold, albet less pronounced; halos
+The main radial trend continues to hold, albeit less pronounced; halos
 in MHD simulations are in general rounder than their DM counterparts
@@
 
-This situation is summarized Table \ref{table:shape}
-We summarize these resulta in Table \ref{table:shape}
+In Table \ref{table:shape} we summarize the
 
@@
 \setlength{\tabcolsep}{3pt}
-\begin{tabular}{l|cccccc}
- &$R_{1/16}$& $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R_1$ & $R_2$\\
+\begin{center}
+\begin{tabular}{l|ccccc}
+ &$R_{1/16}$& $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R_1$\\
 \hline \hline
-$\bar{q}$&$0.55^{+0.07}_{-0.07}$&$0.57^{+0.09}_{-0.08}$&$0.61^{+0.15}_{-0.08}$&$0.65^{+0.18}_{-0.10}$&$0.70^{+0.13}_{-0.10}$&$0.75^{+0.10}_{-0.10}$ \\ [0.1cm]
-$\bar{s}$&$0.42^{+0.12}_{-0.03}$&$0.45^{+0.11}_{-0.04}$&$0.49^{+0.09}_{-0.05}$&$0.52^{+0.10}_{-0.05}$&$0.56^{+0.10}_{-0.05}$&$0.59^{+0.11}_{-0.06}$ \\ [0.1cm]
-$\bar{T}$&$0.89^{+0.03}_{-0.08}$&$0.88^{+0.04}_{-0.12}$&$0.84^{+0.08}_{-0.23}$&$0.81^{+0.08}_{-0.29}$&$0.75^{+0.14}_{-0.25}$&$0.71^{+0.16}_{-0.19}$ \\ [0.1cm]
-
+$\bar{q}$&$0.55^{+0.07}_{-0.07}$&$0.57^{+0.09}_{-0.08}$&$0.61^{+0.15}_{-0.08}$&$0.65^{+0.18}_{-0.10}$&$0.70^{+0.13}_{-0.10}$ \\ [0.1cm]
+$\bar{s}$&$0.42^{+0.12}_{-0.03}$&$0.45^{+0.11}_{-0.04}$&$0.49^{+0.09}_{-0.05}$&$0.52^{+0.10}_{-0.05}$&$0.56^{+0.10}_{-0.05}$\\ [0.1cm]
+$\bar{T}$&$0.89^{+0.03}_{-0.08}$&$0.88^{+0.04}_{-0.12}$&$0.84^{+0.08}_{-0.23}$&$0.81^{+0.08}_{-0.29}$&$0.75^{+0.14}_{-0.25}$\\ [0.1cm]
 \hline
 \end{tabular}
-\caption{Median values of axial ratios $q,s$ and triaxiality parameter $T$ for DM halos in DM-only simulations at different radii (columns). }
-\label{tabe:DM table}
+\end{center}
+\caption{Median values of axial ratios $q,s$ and triaxiality parameter
+  $T$ for DM halos in DM-only simulations at different radii. The
+  median is computed over the 30 halos in Level 3 simulations.}  
+\label{table:median_axial_ratio_DM}
+\end{table}
+
+\begin{table}
+\begin{center}
+\begin{tabular}{l|ccccc}
+ &$R_{1/16}$& $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R_1$\\
+\hline \hline
+$\bar{q}$&$0.93^{+0.04}_{-0.04}$&$0.95^{+0.03}_{-0.03}$&$0.95^{+0.02}_{-0.05}$&$0.93^{+0.04}_{-0.06}$&$0.93^{+0.04}_{-0.10}$\\[0.1cm]
+$\bar{s}$&$0.73^{+0.05}_{-0.09}$&$0.73^{+0.07}_{-0.10}$&$0.73^{+0.08}_{-0.10}$&$0.73^{+0.09}_{-0.08}$&$0.75^{+0.07}_{-0.11}$\\[0.1cm] 
+$\bar{T}$&$0.31^{+0.15}_{-0.22}$&$0.20^{+0.24}_{-0.12}$&$0.24^{+0.20}_{-0.12}$&$0.30^{+0.26}_{-0.16}$&$0.36^{+0.23}_{-0.23}$\\[0.1cm] 
+\hline
+\end{tabular}
+\end{center}
+\caption{
+Median values of axial ratios $q,s$ and triaxiality parameter $T$ for
+DM halos in MHD simulations at different radii (columns). }  
+\label{table:median_axial_ratio_MHD}
 \end{table}
@@
 \ref{MHD table} and figure \ref{fig:Triax_MHD}
-
-\begin{table}
-\setlength{\tabcolsep}{3pt}
-\begin{tabular}{l|cccccc}
- &$R_{1/16}$& $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R_1$ & $R_2$\\
-\hline \hline
-$\bar{q}$&$0.93^{+0.04}_{-0.04}$&$0.95^{+0.03}_{-0.03}$&$0.95^{+0.02}_{-0.05}$&$0.93^{+0.04}_{-0.06}$&$0.93^{+0.04}_{-0.10}$&$0.92^{+0.03}_{-0.09}$ \\[0.1cm]
-$\bar{s}$&$0.73^{+0.05}_{-0.09}$&$0.73^{+0.07}_{-0.10}$&$0.73^{+0.08}_{-0.10}$&$0.73^{+0.09}_{-0.08}$&$0.75^{+0.07}_{-0.11}$&$0.74^{+0.07}_{-0.10}$ \\[0.1cm]
-$\bar{T}$&$0.31^{+0.15}_{-0.22}$&$0.20^{+0.24}_{-0.12}$&$0.24^{+0.20}_{-0.12}$&$0.30^{+0.26}_{-0.16}$&$0.36^{+0.23}_{-0.23}$&$0.39^{+0.26}_{-0.13}$ \\[0.1cm]
-\hline
-\end{tabular}
-\caption{Median values of axial ratios $q,s$ and triaxiality parameter $T$ for DM halos in MHD simulations at different radii (columns). }
-\label{tabe:MHD table}
-\end{table}
 

### 2019-02-19 Paper/paper.tex
edit

@@
 
-In Table \ref{table:shape} we summarize the
+In Table \ref{table:median_axial_ratio_DM} and Table \ref{table:median_axial_ratio_MHD}
+we summarize the results for the median values of the axis ratio in
+the two sets of simulations (DM and MHD). 
+The lower/upper bounds correspond to the first/third quartiles. 
+The values in Table  \ref{table:median_axial_ratio_DM} shows how halos are
+monotonically rounder with increasing radius, while the comparison
+against Table \ref{table:median_axial_ratio_MHD} shows that halo are
+consistently rounder in MHD simulations at every radius.
 
@@
  &$R_{1/16}$& $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R_1$\\
-\hline \hline
-$\bar{q}$&$0.55^{+0.07}_{-0.07}$&$0.57^{+0.09}_{-0.08}$&$0.61^{+0.15}_{-0.08}$&$0.65^{+0.18}_{-0.10}$&$0.70^{+0.13}_{-0.10}$ \\ [0.1cm]
-$\bar{s}$&$0.42^{+0.12}_{-0.03}$&$0.45^{+0.11}_{-0.04}$&$0.49^{+0.09}_{-0.05}$&$0.52^{+0.10}_{-0.05}$&$0.56^{+0.10}_{-0.05}$\\ [0.1cm]
-$\bar{T}$&$0.89^{+0.03}_{-0.08}$&$0.88^{+0.04}_{-0.12}$&$0.84^{+0.08}_{-0.23}$&$0.81^{+0.08}_{-0.29}$&$0.75^{+0.14}_{-0.25}$\\ [0.1cm]
 \hline 
+$b/a$ &$0.55^{+0.07}_{-0.07}$&$0.57^{+0.09}_{-0.08}$&$0.61^{+0.15}_{-0.08}$&$0.65^{+0.18}_{-0.10}$&$0.70^{+0.13}_{-0.10}$ \\ [0.1cm]
+$c/a$ &$0.42^{+0.12}_{-0.03}$&$0.45^{+0.11}_{-0.04}$&$0.49^{+0.09}_{-0.05}$&$0.52^{+0.10}_{-0.05}$&$0.56^{+0.10}_{-0.05}$\\ [0.1cm]
+$T$ &$0.89^{+0.03}_{-0.08}$&$0.88^{+0.04}_{-0.12}$&$0.84^{+0.08}_{-0.23}$&$0.81^{+0.08}_{-0.29}$&$0.75^{+0.14}_{-0.25}$\\ [0.1cm]
 \end{tabular}
@@
 \begin{table}
+\setlength{\tabcolsep}{3pt}
 \begin{center}
@@
  &$R_{1/16}$& $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R_1$\\
-\hline \hline
-$\bar{q}$&$0.93^{+0.04}_{-0.04}$&$0.95^{+0.03}_{-0.03}$&$0.95^{+0.02}_{-0.05}$&$0.93^{+0.04}_{-0.06}$&$0.93^{+0.04}_{-0.10}$\\[0.1cm]
-$\bar{s}$&$0.73^{+0.05}_{-0.09}$&$0.73^{+0.07}_{-0.10}$&$0.73^{+0.08}_{-0.10}$&$0.73^{+0.09}_{-0.08}$&$0.75^{+0.07}_{-0.11}$\\[0.1cm] 
-$\bar{T}$&$0.31^{+0.15}_{-0.22}$&$0.20^{+0.24}_{-0.12}$&$0.24^{+0.20}_{-0.12}$&$0.30^{+0.26}_{-0.16}$&$0.36^{+0.23}_{-0.23}$\\[0.1cm] 
 \hline 
+$b/a$ &$0.93^{+0.04}_{-0.04}$&$0.95^{+0.03}_{-0.03}$&$0.95^{+0.02}_{-0.05}$&$0.93^{+0.04}_{-0.06}$&$0.93^{+0.04}_{-0.10}$\\[0.1cm]
+$c/a$ &$0.73^{+0.05}_{-0.09}$&$0.73^{+0.07}_{-0.10}$&$0.73^{+0.08}_{-0.10}$&$0.73^{+0.09}_{-0.08}$&$0.75^{+0.07}_{-0.11}$\\[0.1cm] 
+$T$ &$0.31^{+0.15}_{-0.22}$&$0.20^{+0.24}_{-0.12}$&$0.24^{+0.20}_{-0.12}$&$0.30^{+0.26}_{-0.16}$&$0.36^{+0.23}_{-0.23}$\\[0.1cm] 
 \end{tabular}
 \end{center}
-\caption{
-Median values of axial ratios $q,s$ and triaxiality parameter $T$ for
-DM halos in MHD simulations at different radii (columns). }  
+\caption{Median values of axial ratios $q,s$ and triaxiality parameter
+  $T$ for DM halos in MHD-only simulations at different radii. The
+  median is computed over the 30 halos in Level 3 simulations.}  
 \label{table:median_axial_ratio_MHD}

### 2019-02-19 Paper/paper.tex
edit

@@
 average.
+This average behaviour is more clear in the individual case of Halo 16
+in Figure \ref{fig:triaxial_ratios}. There, as we mentioned, at the virial radius the halo is
+rounder than its DM counterpart. 
+Going from $50$\kpch to
+$10$ \kpch radii the $b/a$ ratio is constant almost close to unity
+while it decreases to $0.5$ in DM-only simulation
+
+the DM halo is almost perfectly
+oblate around $\approx 10-30$kpc, second, its axial ratio $b/a$ start
+decreasing very slowly after $50kpc$ and below $10kpc$ and third, its
+axial ratio $c/a$ does not exhibit noticeable change in the whole
+radial domain. (Pass from representative case to averaged values)
+These results are statistically supported and sumarized on table
+\ref{MHD table} and figure \ref{fig:Triax_MHD}
 
 In Table \ref{table:median_axial_ratio_DM} and Table \ref{table:median_axial_ratio_MHD}
-we summarize the results for the median values of the axis ratio in
+we summarize these results for the median values of the axis ratio in
 the two sets of simulations (DM and MHD). 
 The lower/upper bounds correspond to the first/third quartiles. 
-The values in Table  \ref{table:median_axial_ratio_DM} shows how halos are
-monotonically rounder with increasing radius, while the comparison
-against Table \ref{table:median_axial_ratio_MHD} shows that halo are
-consistently rounder in MHD simulations at every radius.
+Summarizing: a) Table  \ref{table:median_axial_ratio_DM} shows how halos are
+monotonically rounder with increasing radius; b) the comparison
+against Table \ref{table:median_axial_ratio_MHD} shows  how DM halos
+are consistently rounder in MHD simulations than DM-only runs at every radius.
 
@@
 \end{table}
-
-Concerning MHD halos, \textit{prescindible?(((the expected tendency is
-  not clear. Some studies claim that the DM halo must be oblate, at
-  least in the vicinities of the disk, to ensure its stability
-  . However,)))} not much is said about its
-dependence with radius as previous studies focus rather on the effects
-of baryons on the dynamics of the halo at fixed radii. Examining the
-representative behaviour of a MHD halo on figure \ref{fig:DM_MHD},
-some things are noticeable: first, the DM halo is almost perfectly
-oblate around $\approx 10-30$kpc, second, its axial ratio $b/a$ start
-decreasing very slowly after $50kpc$ and below $10kpc$ and third, its
-axial ratio $c/a$ does not exhibit noticeable change in the whole
-radial domain. (Pass from representative case to averaged values)
-These results are statistically supported and sumarized on table
-\ref{MHD table} and figure \ref{fig:Triax_MHD}
-
-\subsection{Comparison with observational constraints}
-To be able to compare our results with observational values, we must relate the calculated quanties with their corresponding isopotential analogue, in which observational constraints are usually presented.
-For this purpose, we run a simple algorithm to find an approximation of the shape of the isopotential contour.
-Here, we calculate the mean and standard deviation of the potential over a spherical shell of width equals to $10\%$ of the radius at which it is sampled.
-Then, we calculate the inertia tensor of particles with potential within $1\sigma$ around the mean potential and calculate its triaxial characterization with the reduced inertia tensor.
-We repeat the process of calculating the potential mean and standard deviation until convergence is achieved with tolerance of $10^{-4}$.
-We repeat this process for the different radii from table \ref{tabe:isopotential}.
-\\
-
-\begin{table}
-\setlength{\tabcolsep}{3pt}
-\begin{tabular}{l|cccc}
- & $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R_1$ \\
-\hline \hline
-$\bar{q}$&$0.98^{+0.01}_{-0.02}$&$0.97^{+0.01}_{-0.04}$&$0.96^{+0.03}_{-0.06}$&$0.94^{+0.03}_{-0.07}$ \\[0.1cm]
-$\bar{s}$&$0.89^{+0.04}_{-0.06}$&$0.88^{+0.04}_{-0.04}$&$0.87^{+0.05}_{-0.05}$&$0.85^{+0.05}_{-0.05}$ \\[0.1cm]
-$\bar{T}$&$0.18^{+0.23}_{-0.10}$&$0.36^{+0.19}_{-0.21}$&$0.40^{+0.26}_{-0.20}$&$0.48^{+0.23}_{-0.21}$ \\[0.1cm]
-\hline
-\end{tabular}
-\caption{Median values of isopotential axial ratios $q,s$ and triaxiality parameter $T$ for DM halos in MHD simulations at different radii (columns). }
-\label{tabe:isopotential}
-\end{table}
-
-As a check of consistency, we compare our new isopotential shape
-results with the analytic expression of the
-$(1-q_{\phi})\frac{1}{3}(1-q_{\rho})$ \citep{Binney_and_Tremaine_2008}, taking the volume-enclosed axial ratios
-as an approximation for the isodensity contour ratios
-$q_{\rho}$. Although this analytic expression if meant to be used for
-logarithmic axisymmetric halos, it works well as a first approximation
-for nearly axisymmetric halos as those produced by our disced
-galaxies. We find that the difference between the real and the
-analytic isopotential axial ratios is not bigger than $quantity
-percent$. With this, we may now present on table
-\ref{tabe:isopotential} our observationally-comparable results for MHD
-halos at two important radii one corresponding to the approximate
-regimes where the MW DM halo is usually constrained.
-
-Little discussion: Are our results congruent with observations? at
-which radii, does the DM halo shape vary that much?. Which models are
-favored?
-
-\subsection{The rounding effect of baryons}
-
-From the previous characterization of radial shapes it is clear that
-MHD halos are rounder than DM halos (i.e. axial ratios are bigger) at
-every sampled radii. This can be compared on tables \ref{tabe:DM
-  table} and \ref{tabe:MHD table} or at the representative example on
-figure \ref{fig:DM_MHD}. From there, it is also noticeable that the
-rounding effect of baryons is stronger at the disk regime, where the
-DM halo is almost perfectly oblate. Furthermore, MHD halos tend
-towards more oblate shapes (T < 0.5) despite DM halos tendency towards
-more prolate shapes (T>0.5).
-
-This rounding effect is expected from the gravitational effect of the
-flattened axisymmetric galactic disk. It is also reasonable that this
-effect is not as strong at $\approx 100$kpc, where the disk potential
-is dimmer compared to the DM halo potential. Keeping this in mind, one
-would expect that the rounding effect of baryons is related to some
-galactic parameters such as its component masses and radii. However,
-even for the parameter of highest correlation with this rounding
-effect (the baryonic fraction), the relation is not clear nor
-conclusive due to the dispersion from galaxy peculiarities. In figure
-\ref{fig:Star_Density_effect} we plot the ratios $c/a$ compared to the
-baryonic fraction of each galaxy. Although some linear tendency is
-suggested qualitatively, the dispersion of the sample is very high to
-obtain some conclusive relation. This is an evidence that
-adiabatic-contraction models are not realistic as they may neglect
-some effects of the galaxy evolution in the whole cosmological
-context.
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{./pics/Delta asphericity Vs Star Density.png}
-  \caption{Difference in asphericities between MHD and DM shapes Vs
-    Star Density of the simulation. Unsure about this graphic. Take
-    delta asphericity as the strength of the rounding effect of
-    baryons.}  
-  \label{fig:Star_Density_effect}
-\end{figure}
-
-\textbf{Actually we have not examined the relation of c/a in MHD halos
-  with some measure of c/a from the disk, that is something like
-  Zdisk/Rdisk. This actually would make more sense from a physical
-  point of view: effect of the potential.}
-
-Although the effect of the baryonic disk on the shape of the DM halo
-is a reasonable explanation for the rounding effect, it does not
-actually explain the deviation from oblateness of MHD halos at
-$r<10$kpc. In other words, if the disk is perfectly axisymmetric,
-there must be some source of triaxiality at $r<10$kpc to explain the
-low axial ratios.
-
-\textit{ Talk about source of triaxiality at the inner parts of the
-  halos (bar?). This source of triaxiality at the inner parts explains
-  why the axial ratios are $\approx 0.95$ and not exactly $1$. We
-  should also discuss that the decrease in the axial ratios for bigger
-  radii may actually be bigger/steeper but it is dimmed by the
-  contribution of inner parts.} 
-%
-%\begin{figure}
-%  \centering
-%  \subfloat[Level4 MHD Vs DM at inner regions]{\includegraphics[width=0.5\columnwidth]{./pics/Triaxial_Plane/Triaxiality_Inner_lvl4.png}}
-%  \hfill
-%  \subfloat[Level4 MHD Vs DM at outer regions]{\includegraphics[width=0.5\columnwidth]{./pics/Triaxial_Plane/Triaxiality_Outter_lvl4.png}}
-%  \hfill
-%  \caption{Axial ratios as shown on $c/a$ Vs $b/a$.
-Each dot represents a halo shape at some radius.
-Some observational constraints are plotted alongside our results.
-Here, dots are clustered, proving the general tendence of halos to get rounder on the outer parts.(Optimize space.
-caption replaces title.
-Present constraints representation of density)}
-%  \label{fig:Triaxiality_Inner_Outer}
-%\end{figure}
 
@@
 
+\subsection{Comparison with observational constraints}
+To be able to compare our results with observational values, we must relate the calculated quanties with their corresponding isopotential analogue, in which observational constraints are usually presented.
+For this purpose, we run a simple algorithm to find an approximation of the shape of the isopotential contour.
+Here, we calculate the mean and standard deviation of the potential over a spherical shell of width equals to $10\%$ of the radius at which it is sampled.
+Then, we calculate the inertia tensor of particles with potential within $1\sigma$ around the mean potential and calculate its triaxial characterization with the reduced inertia tensor.
+We repeat the process of calculating the potential mean and standard deviation until convergence is achieved with tolerance of $10^{-4}$.
+We repeat this process for the different radii from table \ref{tabe:isopotential}.
+\\
+
+\begin{table}
+\setlength{\tabcolsep}{3pt}
+\begin{tabular}{l|cccc}
+ & $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R_1$ \\
+\hline \hline
+$\bar{q}$&$0.98^{+0.01}_{-0.02}$&$0.97^{+0.01}_{-0.04}$&$0.96^{+0.03}_{-0.06}$&$0.94^{+0.03}_{-0.07}$ \\[0.1cm]
+$\bar{s}$&$0.89^{+0.04}_{-0.06}$&$0.88^{+0.04}_{-0.04}$&$0.87^{+0.05}_{-0.05}$&$0.85^{+0.05}_{-0.05}$ \\[0.1cm]
+$\bar{T}$&$0.18^{+0.23}_{-0.10}$&$0.36^{+0.19}_{-0.21}$&$0.40^{+0.26}_{-0.20}$&$0.48^{+0.23}_{-0.21}$ \\[0.1cm]
+\hline
+\end{tabular}
+\caption{Median values of isopotential axial ratios $q,s$ and triaxiality parameter $T$ for DM halos in MHD simulations at different radii (columns). }
+\label{tabe:isopotential}
+\end{table}
+
+As a check of consistency, we compare our new isopotential shape
+results with the analytic expression of the
+$(1-q_{\phi})\frac{1}{3}(1-q_{\rho})$ \citep{Binney_and_Tremaine_2008}, taking the volume-enclosed axial ratios
+as an approximation for the isodensity contour ratios
+$q_{\rho}$. Although this analytic expression if meant to be used for
+logarithmic axisymmetric halos, it works well as a first approximation
+for nearly axisymmetric halos as those produced by our disced
+galaxies. We find that the difference between the real and the
+analytic isopotential axial ratios is not bigger than $quantity
+percent$. With this, we may now present on table
+\ref{tabe:isopotential} our observationally-comparable results for MHD
+halos at two important radii one corresponding to the approximate
+regimes where the MW DM halo is usually constrained.
+
+Little discussion: Are our results congruent with observations? at
+which radii, does the DM halo shape vary that much?. Which models are
+favored?
+
+\subsection{The rounding effect of baryons}
+
+From the previous characterization of radial shapes it is clear that
+MHD halos are rounder than DM halos (i.e. axial ratios are bigger) at
+every sampled radii. This can be compared on tables \ref{tabe:DM
+  table} and \ref{tabe:MHD table} or at the representative example on
+figure \ref{fig:DM_MHD}. From there, it is also noticeable that the
+rounding effect of baryons is stronger at the disk regime, where the
+DM halo is almost perfectly oblate. Furthermore, MHD halos tend
+towards more oblate shapes (T < 0.5) despite DM halos tendency towards
+more prolate shapes (T>0.5).
+
+This rounding effect is expected from the gravitational effect of the
+flattened axisymmetric galactic disk. It is also reasonable that this
+effect is not as strong at $\approx 100$kpc, where the disk potential
+is dimmer compared to the DM halo potential. Keeping this in mind, one
+would expect that the rounding effect of baryons is related to some
+galactic parameters such as its component masses and radii. However,
+even for the parameter of highest correlation with this rounding
+effect (the baryonic fraction), the relation is not clear nor
+conclusive due to the dispersion from galaxy peculiarities. In figure
+\ref{fig:Star_Density_effect} we plot the ratios $c/a$ compared to the
+baryonic fraction of each galaxy. Although some linear tendency is
+suggested qualitatively, the dispersion of the sample is very high to
+obtain some conclusive relation. This is an evidence that
+adiabatic-contraction models are not realistic as they may neglect
+some effects of the galaxy evolution in the whole cosmological
+context.
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{./pics/Delta asphericity Vs Star Density.png}
+  \caption{Difference in asphericities between MHD and DM shapes Vs
+    Star Density of the simulation. Unsure about this graphic. Take
+    delta asphericity as the strength of the rounding effect of
+    baryons.}  
+  \label{fig:Star_Density_effect}
+\end{figure}
+
+\textbf{Actually we have not examined the relation of c/a in MHD halos
+  with some measure of c/a from the disk, that is something like
+  Zdisk/Rdisk. This actually would make more sense from a physical
+  point of view: effect of the potential.}
+
+Although the effect of the baryonic disk on the shape of the DM halo
+is a reasonable explanation for the rounding effect, it does not
+actually explain the deviation from oblateness of MHD halos at
+$r<10$kpc. In other words, if the disk is perfectly axisymmetric,
+there must be some source of triaxiality at $r<10$kpc to explain the
+low axial ratios.
+
+\textit{ Talk about source of triaxiality at the inner parts of the
+  halos (bar?). This source of triaxiality at the inner parts explains
+  why the axial ratios are $\approx 0.95$ and not exactly $1$. We
+  should also discuss that the decrease in the axial ratios for bigger
+  radii may actually be bigger/steeper but it is dimmed by the
+  contribution of inner parts.} 
+%
+%\begin{figure}
+%  \centering
+%  \subfloat[Level4 MHD Vs DM at inner regions]{\includegraphics[width=0.5\columnwidth]{./pics/Triaxial_Plane/Triaxiality_Inner_lvl4.png}}
+%  \hfill
+%  \subfloat[Level4 MHD Vs DM at outer regions]{\includegraphics[width=0.5\columnwidth]{./pics/Triaxial_Plane/Triaxiality_Outter_lvl4.png}}
+%  \hfill
+%  \caption{Axial ratios as shown on $c/a$ Vs $b/a$.
+Each dot represents a halo shape at some radius.
+Some observational constraints are plotted alongside our results.
+Here, dots are clustered, proving the general tendence of halos to get rounder on the outer parts.(Optimize space.
+caption replaces title.
+Present constraints representation of density)}
+%  \label{fig:Triaxiality_Inner_Outer}
+%\end{figure}
+
 \section{Conclusions}

### 2019-02-19 Paper/paper.tex
edit

@@
 in the Level 3 simulations. 
-Measurements at $R_{\rm vir}/16$ are represented by circlse while squares 
+Measurements at $R_{\rm vir}/16$ are represented by circles while squares 
 are measurements at $R_{\rm vir}$. 
@@
 The exceptions are cases where a merging substructures near  the
-halo's center give rise to perturbed axial ratios measurments. 
-Figure \ref{fig:triax_HDM} shows the same information, this time for
+halo's center gives rise to perturbed axial ratio measurements. 
+Figure \ref{fig:triax_MHD} shows the same information, this time for
 the MHD simulations. 
-The main radial trend continues to hold, albeit less pronounced; halos
-in MHD simulations are in general rounder than their DM counterparts
-and the increased roundness in outer regions is less pronounced on
-average.
-This average behaviour is more clear in the individual case of Halo 16
-in Figure \ref{fig:triaxial_ratios}. There, as we mentioned, at the virial radius the halo is
-rounder than its DM counterpart. 
-Going from $50$\kpch to
-$10$ \kpch radii the $b/a$ ratio is constant almost close to unity
-while it decreases to $0.5$ in DM-only simulation
+In this case, the main radial trend continues to hold, albeit less
+pronounced.
+We also find that halos in MHD simulations are in general rounder than
+their DM counterparts
 
-the DM halo is almost perfectly
-oblate around $\approx 10-30$kpc, second, its axial ratio $b/a$ start
-decreasing very slowly after $50kpc$ and below $10kpc$ and third, its
-axial ratio $c/a$ does not exhibit noticeable change in the whole
-radial domain. (Pass from representative case to averaged values)
-These results are statistically supported and sumarized on table
-\ref{MHD table} and figure \ref{fig:Triax_MHD}
+This average behaviour of more round halos in MHD can be seen more
+clearly in the individual case of Halo 16, shown in Figure
+\ref{fig:triaxial_radius}.  
+At the virial radius the halo is rounder than its DM counterpart. 
+Going from the virial radius to $10$ \kpch the $b/a$ ratio is constant almost close to unity
+in the MHD simulation while it decreases to $0.5$ in DM-only
+simulation. 
+Between $2$-$10$ \kpc the triaxiality in the DM-only simulation is in
+the range $0.9-1.0$, while the MHD simulation has values between
+$0-0.5$.
 
 In Table \ref{table:median_axial_ratio_DM} and Table \ref{table:median_axial_ratio_MHD}
-we summarize these results for the median values of the axis ratio in
+we summarize these trends for the median values of the axis ratio in
 the two sets of simulations (DM and MHD). 

### 2019-02-20 Paper/paper.tex
edit

@@
 
-This average behaviour of more round halos in MHD can be seen more
-clearly in the individual case of Halo 16, shown in Figure
-\ref{fig:triaxial_radius}.  
-At the virial radius the halo is rounder than its DM counterpart. 
-Going from the virial radius to $10$ \kpch the $b/a$ ratio is constant almost close to unity
-in the MHD simulation while it decreases to $0.5$ in DM-only
-simulation. 
+This global behaviour can be also illustrated by the individual case
+of Halo 16, shown in Figure \ref{fig:triaxial_radius}.
+At the virial radius the halo is rounder than its DM counterpart as
+evidenced in the axis ratios $b/a$, $c/a$ and the triaxiality.
+In the MHD simulation, going from the virial radius to $10$ \kpch the
+$b/a$ ratio is constant almost close to unity while in the DM-only
+simulation it decreases to $0.5$.
 Between $2$-$10$ \kpc the triaxiality in the DM-only simulation is in
@@
 we summarize these trends for the median values of the axis ratio in
-the two sets of simulations (DM and MHD). 
+the DM and MHD simulations
 The lower/upper bounds correspond to the first/third quartiles. 
-Summarizing: a) Table  \ref{table:median_axial_ratio_DM} shows how halos are
-monotonically rounder with increasing radius; b) the comparison
+Table  \ref{table:median_axial_ratio_DM} shows how halos are
+monotonically rounder with increasing radius; while the comparison
 against Table \ref{table:median_axial_ratio_MHD} shows how DM halos
-are consistently rounder in MHD simulations than DM-only runs at every radius.
+are consistently rounder in MHD simulations than DM-only runs at every
+radius.
 
@@
 \caption{Axial ratios for the 30 halos in the Level 3 DM simulations.
-   Each dot represents the shape characterization of each halo at the 2 times the virial radius and a  1/16 fraction of the virial radius differentiated by color.
+   Each dot represents the shape characterization of each halo at the
+   2 times the virial radius and a  1/16 fraction of the virial radius
+   differentiated by color. 
    Errorbar shows median and errors for each sampled radii. 

### 2019-02-20 Paper/paper.tex
edit

@@
 
-\begin{figure}
+\begin{figure*}
 \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_DM.png}
+ \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_MHD.png}
 \caption{Axial ratios for the 30 halos in the Level 3 DM simulations.
@@
   correccion. Debe ser a R1/16 y R (no 2R!)}}
-  \label{fig:triax_DM}
-\end{figure}
-
-\begin{figure}
- \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_MHD.png}
-  \caption{Axial ratios for the 30 halos in the Level 3 MHD
-    simulations. DM halos are rounder at larger radii than small radii. {\bf Esto
-      necesita correccion para que tambien sea a 
-      R1/16 y R.}}
-  \label{fig:triax_MHD}
-\end{figure}
+  \label{fig:triax_DM_MHD}
+\end{figure*}
 
@@
 
-\subsection{The historical shape}
-One of the principal motivations to study the radial dependence of the
-DM halo shape is that it may encode some clues about its formation
-history. We have already shown that DM-only halos seem to exhibit a
-steady and monotonous growth in its axial ratios when sampled at
-bigger radii. One similar effect can be found if we sample the shape
-at the virial radius, this time at varying redshift. It is easy to see
-that the axial ratios increase with decreasing redshift, which is
-expected by the continuous influence of the gravitational potential
-\cite{Vera-Ciro_et_al._2011}. In figure \ref{fig:RedshiftGood} we
-present a representative example.
+\subsection{Shape evolution with cosmic time}
+
+We have now established that DM-only have a steady and monotonous
+trend towards larger sphericity with increasing radius. 
+This radial trend is mimicked when the shape is measured at the virial
+radius as a function of cosmic time.
+The halo should become rounder with decreasing redshift, this is
+expected by the continuous influence of the gravitational potential on
+a collisionless fluid \citep{Vera-Ciro_et_al._2011}.
+
+\begin{figure*}
+  \includegraphics[width=\columnwidth]{./pics/Redshift/halo_27_DM_Z_correlation.png}
+  \includegraphics[width=\columnwidth]{./pics/Redshift/halo_24_level3_MHD_Z_Triax.png}
+  \caption{Radial profile at $z=0$ (dashed line) and 
+    the istorical profile at virial radius R500 (colour line). Example
+    of a halo where there is some correlation between these two
+    profiles, as usually happens for DM only
+    simulations. Conclusion: DM only halos usually (fraction?) have
+    correlated shape profiles. {\bf Aqui la idea es mostrar el mismo
+      halo, no halos diferentes!}} 
+  \label{fig:DM Z Triax}
+\end{figure*}
 
@@
 
-\begin{figure}
-  \includegraphics[width=\columnwidth]{./pics/Redshift/halo_27_DM_Z_correlation.png}
-  \caption{DM only Radial profile at redshift 0 (dashed line)
-    Historical profile at virial radius R500 (colour line). Example
-    of a halo where there is some correlation between these two
-    profiles, as usually happens for DM only
-    simulations. Conclusion: DM only halos usually (fraction?) have
-    correlated shape profiles.} 
-  \label{fig:DM Z Triax}
-\end{figure}
-
 MHD halos, on the other hand, do not exhibit tendency towards
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{./pics/Redshift/halo_24_level3_MHD_Z_Triax.png}
+
   \caption{MHD. Radial profile at redshift 0 (dashed line)

### 2019-02-20 Paper/paper.tex
edit

@@
   redshift 0 and there are two sets of lines showing MHD and DM-only
-  versions of the axial ratios profile} \label{fig:triaxial_radius}
+  versions of the axial ratios profile. {\bf Aqui hay que quiar c/b,
+    no es relevante}} \label{fig:triaxial_radius}
 \end{figure*}
@@
 
-Figure \ref{fig:triax_DM} summarizes this comparizon for all 30 halos
+Figure \ref{fig:triax_DM_MHD} summarizes this comparizon for all 30 halos
 in the Level 3 simulations. 
@@
 halo's center gives rise to perturbed axial ratio measurements. 
-Figure \ref{fig:triax_MHD} shows the same information, this time for
+The right panel on Figure \ref{fig:triax_DM_MHD} shows the same information, this time for
 the MHD simulations. 
@@
 \begin{figure*}
+\begin{center}
 \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_DM.png}
  \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_MHD.png}
-\caption{Axial ratios for the 30 halos in the Level 3 DM simulations.
+\end{center}
+\caption{Axial ratios for the 30 halos in the Level 3 DM simulations
+  on the left and MHD simulations on the right.
    Each dot represents the shape characterization of each halo at the
@@
 
-We have now established that DM-only have a steady and monotonous
-trend towards larger sphericity with increasing radius. 
-This radial trend is mimicked when the shape is measured at the virial
-radius as a function of cosmic time.
-The halo should become rounder with decreasing redshift, this is
-expected by the continuous influence of the gravitational potential on
-a collisionless fluid \citep{Vera-Ciro_et_al._2011}.
-
 \begin{figure*}
@@
   \caption{Radial profile at $z=0$ (dashed line) and 
-    the istorical profile at virial radius R500 (colour line). Example
-    of a halo where there is some correlation between these two
-    profiles, as usually happens for DM only
-    simulations. Conclusion: DM only halos usually (fraction?) have
-    correlated shape profiles. {\bf Aqui la idea es mostrar el mismo
+    the historical profile at the virial radius (colour line). 
+    Results for DM simulations on the left, for MHD on the right.
+    {\bf Aqui la idea es mostrar el mismo
       halo, no halos diferentes!}} 
-  \label{fig:DM Z Triax}
+  \label{fig:redshift_triaxial}
 \end{figure*}
 
-\begin{figure}
-  \subfloat[halo 16 DM]{\includegraphics[width=0.5\columnwidth]{./pics/Redshift/halo_16_level3_DM_Z.png}}
-  \subfloat[halo 16 MHD]{\includegraphics[width=0.5\columnwidth]{./pics/Redshift/halo_16_level3_MHD_Z.png}}
+\begin{figure*}
+  \subfloat[halo 16 DM]{\includegraphics[width=\columnwidth]{./pics/Redshift/halo_16_level3_DM_Z.png}}
+  \subfloat[halo 16 MHD]{\includegraphics[width=\columnwidth]{./pics/Redshift/halo_16_level3_MHD_Z.png}}
   \caption{Radial profile (comoving) of axial ratios for halo 16 in
@@
     history, but does not require that curves match in the triaxial
-    plane.}
+    plane. {\bf En esta grafica el panel de abajo deberia ser la triaxialidad.}}
   \label{fig:RedshiftGood}
-\end{figure}
+\end{figure*}
 
-Interestingly, these two parametic plots i.e. $(b/a,c/a)(z=0,r)$ and
-$(b/a,c/a)(z,r=R_{vir})$ are very correlated for DM-only halos
-\ref{fig:DM Z Triax}. This means that, for DM-only halos, one can
-approximate its shape at higher redshift by simply sampling its
-current shape at a smaller radius \textbf{wording}. This relationship
-relies strongly on the steady and monotonous tendency of DM halos
-towards sphericity for bigger radii and smaller redshift.
+We know that DM-only have a steady and monotonous
+trend towards larger sphericity with increasing radius. 
+This radial trend is mimicked when the shape is measured at the virial
+radius as a function of cosmic time.
+The halo should become rounder with decreasing redshift, this is
+expected by the continuous influence of the gravitational potential on
+a collisionless fluid \citep{Vera-Ciro_et_al._2011}.
 
-MHD halos, on the other hand, do not exhibit tendency towards
-sphericity with bigger radii, but they do get sistematically rounder
-at lower redshift as seen in figure \ref{fig:RedshiftGood}. This
-effectively vanishes this correlation as seen from a DM halo
-\ref{fig:MHD Z Triax}.
+We show in the left panel of Figure \ref{fig:redshift_triaxial} an
+example with this effect in Halo 27 of the DM simulations:
+the radial triaxiality at $z=0$ and the historical triaxiality at
+$R_{\rm vir}$ are correlated. 
+The right panel on the same Figure \ref{fig:redshift_triaxial}
+illustrates how this correlation is absent in MHD simulations.
 
-\begin{figure}
-
-  \caption{MHD. Radial profile at redshift 0 (dashed line)
-    Historical profile at virial radius R500 (colour line)
-    Example of a halo where there is no correlation
-    between these two profiles, as usually happens in
-    MHD. Conclusion: MHD halos usually (fraction?) have uncorrelated shape profiles.}
-    \label{fig:MHD Z Triax} 
-\end{figure}
-
-Better graphics.
+This means that for DM-only halos one can approximate its shape at
+higher redshift by simply sampling its 
+current shape at a smaller radius. 
+This correlation seems to be prompted by the continous inside-out
+build-up of the dark matter halo; baryonic effects seem to jeopardize
+the apparent smoother growth in DM-only simulations.
 

### 2019-03-05 Paper/paper.tex
edit

@@
 
-%\begin{multicols}{2}
-\begin{table*}
-%\setlength{\tabcolsep}{3pt}
-\begin{tabular}{|l|cc|cc|c|c|p{4cm}|}\hline
-Reference&$q_{\rho}$&$s_{\rho}$&$q_{\phi}$&$s_{\phi}$&$R$&$\theta$&comment\\ \hline \hline
-\citet{Olling_and_Merrifield_2000}& $\mathbf{1.00}$ & $\mathbf{0.80}$ & & & $\simeq 8$kpc & $0^{\circ}$&Method: Stellar dynamics and HI density. \\\hline
-\citet{Law_and_Majewski_2009}&&&$\mathbf{0.83}$&$\mathbf{0.67}$& $\lesssim 60$kpc&$90^{\circ}$&Mid-axis orientation. Method: Sagittarius stream\\\hline
-%
-\citet{Law_and_Majewski_2010}&&&$\mathbf{0.99}$&$\mathbf{0.72}$& $[20$kpc,$60$kpc$]$&$90^{\circ}$&Mid-axis orientation, Method: Sagittarius stream\\\hline
-%
-\citet{Loebman_et_al._2012}&$\mathbf{1.00}$&$\mathbf{0.47}$&&&$\sim 20$kpc &$0^{\circ}$&Method: SDSS statistics\\\hline
-%
-\citet{Deg_and_Widrow_2013}&$0.72$&$0.28$&$0.82$&$0.40$&$[20$kpc,$60$kpc$]$&$90^{\circ}$& Mid-axis orientation. Method: Sagittarius stream\\\hline
-%
-\multirow{2}{*}{\citet{Vera-Ciro_and_Helmi_2013}}&&&$\mathbf{1.00}$&$\mathbf{0.90}$&$\lesssim 10$kpc&$0^{\circ}$ & Method: Sagittarius stream \& LMC \\
-&&&$\mathbf{0.90}$&$\mathbf{0.80}$&$\gtrsim 10$kpc&$90^{\circ}$& Mid-axis orientation on the outside. \\\hline
-%
-\citet{Bovy_et_el._2016}&$\mathbf{0.95}$&$\mathbf{0.95}$&&&$\lesssim 20$kpc&$90^{\circ}$ & Method: Stellar streams\\\hline
-%
-\citet{Bowden_et_al._2016}&&&$\mathbf{[0.5,0.66]}$&$\mathbf{[0.5,0.66]}$&$[5$kpc,$10$kpc$]$&$90^{\circ}$& Weak constraint on prolate halo. Method: SDSS stars dynamics.\\\hline
-%
-\multirow{2}{*}{\citet{Banerjee_and_Chanda_2011}}&$\mathbf{1}$&$\mathbf{1}$&&&$9$kpc&$0^{\circ}$&Method: HI gas. \\
-&$\mathbf{0.5}$&$\mathbf{0.5}$&&&$24$kpc&$0^{\circ}$&Monotonical change between radial regimes.\\\hline
-%
-\cite{Johnston_et_al._2005}&$\mathbf{1}$&$\mathbf{[0.83-0.92]}$&&&$\lesssim 60$kpc&$0^{\circ}$&Method: Sagittarius stream\\\hline\hline
-\end{tabular}
-\caption{(TODO: compute analogues in isopotential or isodensity according to Binney and Tremaine)}
-\end{table*}
-%\end{multicols}
-
-\begin{table*}
-%\setlength{\tabcolsep}{3pt}
-\begin{tabular}{|l|cc|cc|c|p{4cm}|}\hline
-Reference&$q_{\rho}$&$s_{\rho}$&$q_{\phi}$&$s_{\phi}$&$R$&comment\\ \hline \hline
-\citet{Chua_et_al._2018}&$\mathbf{0.88\pm0.10}$&$\mathbf{0.70\pm0.11}$&&&$0.15R_{200}$& Illustris\\\hline
-%
-\citet{Bryan_et_al._2013}&$\mathbf{[0.84,0.86]}$&$\mathbf{[0.66,0.70]}$&&&$R_{200}$& For different cosmologies and feedback recipies. Calculated from a fit at $M_\odot=10^12$\\\hline
-%
-\multirow{2}{*}{\citet{Abadi_et_al._2010}}&&&$\mathbf{0.98}$&$\mathbf{0.85}$&-& Almost independent of radius. No feedback: boundary case\\\hline
-\end{tabular}
-\caption{(TODO: compute analogues in isopotential or isodensity according to Binney and Tremaine)}
-\end{table*}
-
-\section{Numerical Simulations}
-
-In this work we use the results of the state-of-the art Auriga
-simulations \citep{auriga}. 
-The objects in those simulations were selected from a set of 30
-isolated halos in the Evolution and Assembly of GaLaxies and their
-Environments (EAGLE)  project \citep{Eagle}.   
-These halos were randomly selected from a sample of the most isolated
-halos whose virial mass $M_{200}$ varied between $10^{12}M_\odot$ and
-$2\times 10^{12}M_\odot$. 
-These halos were re-simulated with higher resolution an varying
-physical realism using the AREPO code \citep{arepo}.
-
-All 30 halos were simulated within resolution defined for Aquarius
-simulations corresponding to $\sim 3\times 10^6$ high resolution DM
-particles of $\sim 2.5 \times 10^5 M_\odot$.  
-This resolution is labeled as Level 4, the main details for each halo
-are consigned in Table \ref{tab:level4}. 
-From these 30 halos, 6 of them where re-simulated at higher resolution
-(labeled as Level 3) taking into account a spatial factor of 2 in each
-dimension.   
-Details of Level 3 halos are in Table \ref{tab:level3}. 
-Furthermore, for each halo in each level of resolution there are two
-versions of the simulation: DM-only and DM plus baryons with
-magneto-hydrodynamical (MHD) physics.
-
 \begin{table*}
@@
 
+\section{Numerical Simulations}
+
+In this work we use the results of the state-of-the art Auriga
+simulations \citep{auriga}. 
+The objects in those simulations were selected from a set of 30
+isolated halos in the Evolution and Assembly of GaLaxies and their
+Environments (EAGLE)  project \citep{Eagle}.   
+These halos were randomly selected from a sample of the most isolated
+halos whose virial mass $M_{200}$ varied between $10^{12}M_\odot$ and
+$2\times 10^{12}M_\odot$. 
+These halos were re-simulated with higher resolution an varying
+physical realism using the AREPO code \citep{arepo}.
+
+All 30 halos were simulated within resolution defined for Aquarius
+simulations corresponding to $\sim 3\times 10^6$ high resolution DM
+particles of $\sim 2.5 \times 10^5 M_\odot$.  
+This resolution is labeled as Level 4, the main details for each halo
+are consigned in Table \ref{tab:level4}. 
+From these 30 halos, 6 of them where re-simulated at higher resolution
+(labeled as Level 3) taking into account a spatial factor of 2 in each
+dimension.   
+Details of Level 3 halos are in Table \ref{tab:level3}. 
+Furthermore, for each halo in each level of resolution there are two
+versions of the simulation: DM-only and DM plus baryons with
+magneto-hydrodynamical (MHD) physics.
+
+\begin{figure*}
+  \centering
+  \subfloat[halo 27 DM shape at small
+    radius]{\includegraphics[width=0.5\textwidth]{./pics/MHD_Vs_DM/level4_DM_halo_27_inner.png}} 
+  \hfill
+  \subfloat[halo 27 DM shape at big
+    radius]{\includegraphics[width=0.5\textwidth]{./pics/MHD_Vs_DM/level4_DM_halo_27_outter.png}} 
+  \hfill 
+  \caption{DM density for inner/outer (left/right panel) DM halo regions.  
+  Slice 20 percent of the max-min range in the "z" position of
+  particles belonging to the main structure, centered at halo defined
+  position (calculated with most bounded particle) }  
+  \label{fig:slices}
+\end{figure*}
+
 \section{Determining the halo shape}
@@
 \subsection{Radial trends at $z=0$}
-
-\begin{figure*}
-  \centering
-  \subfloat[halo 27 DM shape at small
-    radius]{\includegraphics[width=0.5\textwidth]{./pics/MHD_Vs_DM/level4_DM_halo_27_inner.png}} 
-  \hfill
-  \subfloat[halo 27 DM shape at big
-    radius]{\includegraphics[width=0.5\textwidth]{./pics/MHD_Vs_DM/level4_DM_halo_27_outter.png}} 
-  \hfill 
-  \caption{DM density for inner/outer (left/right panel) DM halo regions.  
-  Slice 20 percent of the max-min range in the "z" position of
-  particles belonging to the main structure, centered at halo defined
-  position (calculated with most bounded particle) }  
-  \label{fig:slices}
-\end{figure*}
 
@@
 
-\subsection{The orientation of the principa axes}
+\subsection{DM halo - Stellar Disk Alignment}
 
-One of the principal assumptions of observational models of the MW's
-DM halo is that its minor axis is perfectly aligned with the disk
-axis. Although this is a reasonable assumption to guarantee the
+A common assumption in observational models of the MW DM halo is that
+its minor axis is perfectly aligned with the disk axis.
+Although it is a reasonable assumption to guarantee the
 stability of the galactic disk in simplified models of isolated
-galaxies, it may not be the case for galaxies evolved in the whole
-cosmological context nor at every radii at which the shape is
-sampled.
+galaxies, this might not hold in an explicit cosmological context.
 
-Therefore, it is of special interest to us to examin the strength of
-this alignment assumption in the context of simulations. For this
-purpose, we sampled the shape at 5 different radii and plotted the
-axial directions, as well as the disk direction in the \textbf{name}
-diagrams \cite{} (explain diagrams). Explain disk direction
-calculation.
+To examine the validity of this assumption  we sampled the shape at 5
+different radii and plotted  directions in a cartesiian coordinate
+system where the $z$-axis always corresponds to the minor axis
+measured at the virial radius.
 
-We found that there is not a representative example of what happens in
-terms of alignments. We found that the majority of the disks are
-aligned with the minor axis of their DM halo within $\approx 30^o$; in
-some special cases, this alignment was almost perfect and in some
+{\bf en Este caso hace falta la figura con la distribuci\'on integrada de cos theta}.
+Figure \ref{fig:alignment} is the cumulative distribution of $\cos\theta$, where $\theta$ is the 
+summarizes our results. 
+We find that the majority of the disks are aligned with the minor axis of their DM halo within $\approx 30^{\circ}$.
+in some special cases, this alignment was almost perfect and in some
 other cases, the DM halo minor axis changed substantially to be able
@@
 these three cases. \textbf{occurrencies for each case?}
+
+%---AVANCE
 
@@
 
-\begin{figure}
+\begin{figure*}
   \centering
-  \subfloat[Perfectly aligned Axes]{\includegraphics[width=1\columnwidth]{./pics/well_axes.png}}
+  \subfloat[Perfectly aligned Axes]{\includegraphics[width=0.6\columnwidth]{./pics/well_axes.png}}
   \hfill
-  \subfloat[Somewhat aligned Axes]{\includegraphics[width=1\columnwidth]{./pics/rotating_axes.png}}
+  \subfloat[Somewhat aligned Axes]{\includegraphics[width=0.6\columnwidth]{./pics/rotating_axes.png}}
   \hfill
-  \subfloat[Chaotic Axes]{\includegraphics[width=1\columnwidth]{./pics/chaotic_axes.png}}
+  \subfloat[Chaotic Axes]{\includegraphics[width=0.6\columnwidth]{./pics/chaotic_axes.png}}
   \hfill
@@
   \label{fig:alignment}
-\end{figure}
+\end{figure*}
 
@@
 \subsection{Comparison with observational constraints}
+
+\begin{table*}
+\begin{tabular}{|l|cc|cc|c|c|p{4cm}|}\hline
+Reference&$q_{\rho}$&$s_{\rho}$&$q_{\phi}$&$s_{\phi}$&$R$&$\theta$&comment\\ \hline \hline
+\citet{Olling_and_Merrifield_2000}& $\mathbf{1.00}$ & $\mathbf{0.80}$ & & & $\simeq 8$kpc & $0^{\circ}$&Method: Stellar dynamics and HI density. \\\hline
+\citet{Law_and_Majewski_2009}&&&$\mathbf{0.83}$&$\mathbf{0.67}$& $\lesssim 60$kpc&$90^{\circ}$&Mid-axis orientation. Method: Sagittarius stream\\\hline
+%
+\citet{Law_and_Majewski_2010}&&&$\mathbf{0.99}$&$\mathbf{0.72}$& $[20$kpc,$60$kpc$]$&$90^{\circ}$&Mid-axis orientation, Method: Sagittarius stream\\\hline
+%
+\citet{Loebman_et_al._2012}&$\mathbf{1.00}$&$\mathbf{0.47}$&&&$\sim 20$kpc &$0^{\circ}$&Method: SDSS statistics\\\hline
+%
+\citet{Deg_and_Widrow_2013}&$0.72$&$0.28$&$0.82$&$0.40$&$[20$kpc,$60$kpc$]$&$90^{\circ}$& Mid-axis orientation. Method: Sagittarius stream\\\hline
+%
+\multirow{2}{*}{\citet{Vera-Ciro_and_Helmi_2013}}&&&$\mathbf{1.00}$&$\mathbf{0.90}$&$\lesssim 10$kpc&$0^{\circ}$ & Method: Sagittarius stream \& LMC \\
+&&&$\mathbf{0.90}$&$\mathbf{0.80}$&$\gtrsim 10$kpc&$90^{\circ}$& Mid-axis orientation on the outside. \\\hline
+%
+\citet{Bovy_et_el._2016}&$\mathbf{0.95}$&$\mathbf{0.95}$&&&$\lesssim 20$kpc&$90^{\circ}$ & Method: Stellar streams\\\hline
+%
+\citet{Bowden_et_al._2016}&&&$\mathbf{[0.5,0.66]}$&$\mathbf{[0.5,0.66]}$&$[5$kpc,$10$kpc$]$&$90^{\circ}$& Weak constraint on prolate halo. Method: SDSS stars dynamics.\\\hline
+%
+\multirow{2}{*}{\citet{Banerjee_and_Chanda_2011}}&$\mathbf{1}$&$\mathbf{1}$&&&$9$kpc&$0^{\circ}$&Method: HI gas. \\
+&$\mathbf{0.5}$&$\mathbf{0.5}$&&&$24$kpc&$0^{\circ}$&Monotonical change between radial regimes.\\\hline
+%
+\cite{Johnston_et_al._2005}&$\mathbf{1}$&$\mathbf{[0.83-0.92]}$&&&$\lesssim 60$kpc&$0^{\circ}$&Method: Sagittarius stream\\\hline\hline
+\end{tabular}
+\caption{(TODO: compute analogues in isopotential or isodensity according to Binney and Tremaine)}
+\end{table*}
+%\end{multicols}
+
+\begin{table*}
+%\setlength{\tabcolsep}{3pt}
+\begin{tabular}{|l|cc|cc|c|p{4cm}|}\hline
+Reference&$q_{\rho}$&$s_{\rho}$&$q_{\phi}$&$s_{\phi}$&$R$&comment\\ \hline \hline
+\citet{Chua_et_al._2018}&$\mathbf{0.88\pm0.10}$&$\mathbf{0.70\pm0.11}$&&&$0.15R_{200}$& Illustris\\\hline
+%
+\citet{Bryan_et_al._2013}&$\mathbf{[0.84,0.86]}$&$\mathbf{[0.66,0.70]}$&&&$R_{200}$& For different cosmologies and feedback recipies. Calculated from a fit at $M_\odot=10^12$\\\hline
+%
+\multirow{2}{*}{\citet{Abadi_et_al._2010}}&&&$\mathbf{0.98}$&$\mathbf{0.85}$&-& Almost independent of radius. No feedback: boundary case\\\hline
+\end{tabular}
+\caption{(TODO: compute analogues in isopotential or isodensity according to Binney and Tremaine)}
+\end{table*}
+
 To be able to compare our results with observational values, we must relate the calculated quanties with their corresponding isopotential analogue, in which observational constraints are usually presented.

### 2019-03-05 Paper/paper.tex
edit

@@
 To examine the validity of this assumption  we sampled the shape at 5
-different radii and plotted  directions in a cartesiian coordinate
+different radii and plotted  directions in a cartesian coordinate
 system where the $z$-axis always corresponds to the minor axis
@@
 
-{\bf en Este caso hace falta la figura con la distribuci\'on integrada de cos theta}.
-Figure \ref{fig:alignment} is the cumulative distribution of $\cos\theta$, where $\theta$ is the 
-summarizes our results. 
-We find that the majority of the disks are aligned with the minor axis of their DM halo within $\approx 30^{\circ}$.
-in some special cases, this alignment was almost perfect and in some
-other cases, the DM halo minor axis changed substantially to be able
-to determine an alignment. In figure \ref{fig:alignment} we present
-these three cases. \textbf{occurrencies for each case?}
+{\bf En este caso hace falta la figura con la distribuci\'on integrada de cos theta}.
+Figure \ref{fig:alignment} shows the cumulative distribution of
+$\cos\theta$, where $\theta$ is the angle betwen the DM halo minor
+axis and the stellar disk angular momentum.  
+Each line shows the results at different radii.
+We find that the majority of the disks are aligned with the minor axis
+of their DM halo within $\approx 30^{\circ}$. 
+Furthermore, if there is a good alignment measured at the virial
+radius, this alignment is well conserved at smaller radii.
+However, there are some disks that show string missalignments.
 
-%---AVANCE
-
+{\bf En este caso hace falta la figura de la evoluci\'on de cos theta
+  como funci\'on del redshift}
+To better understand the missalignments we plot the evolution of
+$\cos\theta$ with the 
+Figure \ref{fig:alignment_history}
 \textit{This is an important result of our study. We study the radial

### 2019-03-05 Paper/paper.tex
edit

@@
 radius, this alignment is well conserved at smaller radii.
-However, there are some disks that show string missalignments.
 
@@
   como funci\'on del redshift}
+However, there are some disks that show strong missalignments. 
 To better understand the missalignments we plot the evolution of
-$\cos\theta$ with the 
-Figure \ref{fig:alignment_history}
-\textit{This is an important result of our study. We study the radial
-  evolution of the principal axes, compared also to the angular
-  momentum vector from the disk. We found that while the angular
-  momentum tend to be aligned with the minor axis of the ellipsoid,
-  this may not be the case all times. When there is an alignment it is
-  usually within 20 degrees (get a histogram of this. and an evolution
-  of this histogram with time). When there is not an alignment, then
-  there is no simple way to determine towards which axis it is
-  oriented. Furthermore, the principal axes alignment usually change
-  with radius (rotation, swap, verify). This ask for relaxation on the
-  strong constrains on the MW DM halo models.}
+$\cos\theta$ with time to find that the missalignment has been present
+for the last XXX Gyr.
+This trend is summarized in Figure \ref{fig:alignment_history}.
 

### 2019-03-05 Paper/paper.tex
edit

@@
 
-\subsection{Comparison with observational constraints}
+\section{Analysis}
+
+\subsection{Comparison against observational constraints}
 
 \begin{table*}
-\begin{tabular}{|l|cc|cc|c|c|p{4cm}|}\hline
-Reference&$q_{\rho}$&$s_{\rho}$&$q_{\phi}$&$s_{\phi}$&$R$&$\theta$&comment\\ \hline \hline
-\citet{Olling_and_Merrifield_2000}& $\mathbf{1.00}$ & $\mathbf{0.80}$ & & & $\simeq 8$kpc & $0^{\circ}$&Method: Stellar dynamics and HI density. \\\hline
-\citet{Law_and_Majewski_2009}&&&$\mathbf{0.83}$&$\mathbf{0.67}$& $\lesssim 60$kpc&$90^{\circ}$&Mid-axis orientation. Method: Sagittarius stream\\\hline
-%
-\citet{Law_and_Majewski_2010}&&&$\mathbf{0.99}$&$\mathbf{0.72}$& $[20$kpc,$60$kpc$]$&$90^{\circ}$&Mid-axis orientation, Method: Sagittarius stream\\\hline
-%
-\citet{Loebman_et_al._2012}&$\mathbf{1.00}$&$\mathbf{0.47}$&&&$\sim 20$kpc &$0^{\circ}$&Method: SDSS statistics\\\hline
-%
-\citet{Deg_and_Widrow_2013}&$0.72$&$0.28$&$0.82$&$0.40$&$[20$kpc,$60$kpc$]$&$90^{\circ}$& Mid-axis orientation. Method: Sagittarius stream\\\hline
-%
-\multirow{2}{*}{\citet{Vera-Ciro_and_Helmi_2013}}&&&$\mathbf{1.00}$&$\mathbf{0.90}$&$\lesssim 10$kpc&$0^{\circ}$ & Method: Sagittarius stream \& LMC \\
-&&&$\mathbf{0.90}$&$\mathbf{0.80}$&$\gtrsim 10$kpc&$90^{\circ}$& Mid-axis orientation on the outside. \\\hline
-%
-\citet{Bovy_et_el._2016}&$\mathbf{0.95}$&$\mathbf{0.95}$&&&$\lesssim 20$kpc&$90^{\circ}$ & Method: Stellar streams\\\hline
-%
-\citet{Bowden_et_al._2016}&&&$\mathbf{[0.5,0.66]}$&$\mathbf{[0.5,0.66]}$&$[5$kpc,$10$kpc$]$&$90^{\circ}$& Weak constraint on prolate halo. Method: SDSS stars dynamics.\\\hline
-%
-\multirow{2}{*}{\citet{Banerjee_and_Chanda_2011}}&$\mathbf{1}$&$\mathbf{1}$&&&$9$kpc&$0^{\circ}$&Method: HI gas. \\
-&$\mathbf{0.5}$&$\mathbf{0.5}$&&&$24$kpc&$0^{\circ}$&Monotonical change between radial regimes.\\\hline
-%
-\cite{Johnston_et_al._2005}&$\mathbf{1}$&$\mathbf{[0.83-0.92]}$&&&$\lesssim 60$kpc&$0^{\circ}$&Method: Sagittarius stream\\\hline\hline
+\begin{tabular}{|l|cc|c|c|p{7cm}|}\hline
+Reference&$q_{\phi}$&$s_{\phi}$&$R$&$\theta$&
+Methodology\\ \hline \hline
+
+\citet{Bowden_et_al._2016}& 0.5-0.66 &0.5-0.66& 5kpc - 10 kpc& $90^{\circ}$&
+Weak constraint on prolate halo. SDSS stars dynamics.\\\hline
+
+\multirow{2}{*}{\citet{Vera-Ciro_and_Helmi_2013}}&${1.00}$&${0.90}$&$\lesssim
+10$kpc&$0^{\circ}$ & Sagittarius stream \& LMC \\
+&${0.90}$&${0.80}$&$\gtrsim 10$kpc&$90^{\circ}$&
+Mid-axis orientation on the outside. \\\hline
+
+\citet{Law_and_Majewski_2009}&${0.83}$&${0.67}$&
+$\lesssim 60$kpc&$90^{\circ}$&Mid-axis orientation. Sagittarius
+stream\\\hline
+
+\citet{Law_and_Majewski_2010}&${0.99}$&${0.72}$&
+$20$kpc-$60$kpc$$&$90^{\circ}$&Mid-axis orientation, Sagittarius
+stream\\\hline
+
+\citet{Deg_and_Widrow_2013} & $0.82$&$0.40$&
+$20$kpc-$60$kpc$ $&$90^{\circ}$&
+Mid-axis orientation. Sagittarius stream\\\hline
+
 \end{tabular}
-\caption{(TODO: compute analogues in isopotential or isodensity according to Binney and Tremaine)}
+\caption{{\bf Cuales son las incertidumbres? Con respecto a que eje
+    esta medido theta?}}
 \end{table*}
@@
 \begin{table*}
-%\setlength{\tabcolsep}{3pt}
-\begin{tabular}{|l|cc|cc|c|p{4cm}|}\hline
-Reference&$q_{\rho}$&$s_{\rho}$&$q_{\phi}$&$s_{\phi}$&$R$&comment\\ \hline \hline
-\citet{Chua_et_al._2018}&$\mathbf{0.88\pm0.10}$&$\mathbf{0.70\pm0.11}$&&&$0.15R_{200}$& Illustris\\\hline
-%
-\citet{Bryan_et_al._2013}&$\mathbf{[0.84,0.86]}$&$\mathbf{[0.66,0.70]}$&&&$R_{200}$& For different cosmologies and feedback recipies. Calculated from a fit at $M_\odot=10^12$\\\hline
-%
-\multirow{2}{*}{\citet{Abadi_et_al._2010}}&&&$\mathbf{0.98}$&$\mathbf{0.85}$&-& Almost independent of radius. No feedback: boundary case\\\hline
+\begin{tabular}{|l|cc|c|c|p{7cm}|}\hline
+Reference&$q_{\rho}$&$s_{\rho}$&$R$&$\theta$&
+Methodology\\ 
+\hline \hline \citet{Olling_and_Merrifield_2000}& $1.00$
+& $0.80$ &  $\simeq 8$kpc & $0^{\circ}$&Stellar dynamics and HI
+density. \\\hline
+
+\multirow{2}{*}{\citet{Banerjee_and_Chanda_2011}}&${1}$&${1}$&$9$kpc&$0^{\circ}$&Method:
+HI
+gas. \\ &${0.5}$&${0.5}$&$24$kpc&$0^{\circ}$&Monotonical
+change between radial regimes.\\\hline
+
+\citet{Loebman_et_al._2012}&${1.00}$&${0.47}$&$\sim
+20$kpc &$0^{\circ}$&Method: SDSS statistics\\\hline
+
+\cite{Johnston_et_al._2005}&${1}$&$0.83-0.92$&$\lesssim
+60$kpc&$0^{\circ}$&Method: Sagittarius stream\\\hline
+
+\citet{Bovy_et_el._2016}&${0.95}$&${0.95}$&$\lesssim
+20$kpc&$90^{\circ}$ & Stellar streams\\\hline
+
+\citet{Deg_and_Widrow_2013}&$0.72$&$0.28$&
+$20$kpc-$60$kpc$ $&$90^{\circ}$&
+Mid-axis orientation. Sagittarius stream\\\hline
+
+\citet{Abadi_et_al._2010} &${0.98}$&${0.85}$& & & Simulations. Almost
+  independent of radius. No feedback: boundary case\\\hline
+
 \end{tabular}
-\caption{(TODO: compute analogues in isopotential or isodensity according to Binney and Tremaine)}
+\caption{{\bf Cuales son las incertidumbres? Con respecto a que eje
+    esta medido theta?}}
 \end{table*}
 
-To be able to compare our results with observational values, we must relate the calculated quanties with their corresponding isopotential analogue, in which observational constraints are usually presented.
-For this purpose, we run a simple algorithm to find an approximation of the shape of the isopotential contour.
-Here, we calculate the mean and standard deviation of the potential over a spherical shell of width equals to $10\%$ of the radius at which it is sampled.
-Then, we calculate the inertia tensor of particles with potential within $1\sigma$ around the mean potential and calculate its triaxial characterization with the reduced inertia tensor.
-We repeat the process of calculating the potential mean and standard deviation until convergence is achieved with tolerance of $10^{-4}$.
-We repeat this process for the different radii from table \ref{tabe:isopotential}.
-\\
+\begin{table*}
+\begin{tabular}{|l|cc|cc|c|p{4cm}|}\hline
+Reference&$q_{\rho}$&$s_{\rho}$&$q_{\phi}$&$s_{\phi}$&$R$& Methodology
+\\ \hline \hline
+\citet{Chua_et_al._2018}&${0.88\pm0.10}$&${0.70\pm0.11}$&&&$0.15R_{200}$& Illustris\\\hline
+
+\citet{Bryan_et_al._2013}&$0.84-0.86$&$0.66-0.70$&&&$R_{200}$&
+For different cosmologies and feedback recipies. Calculated from a fit
+at $M_\odot=10^12$\\\hline
+
+\multirow{2}{*}{\citet{Abadi_et_al._2010}}&&&${0.98}$&${0.85}$&-&
+Almost independent of radius. No feedback: boundary case\\\hline 
+\end{tabular}
+\caption{(TODO: compute analogues in isopotential or isodensity
+  according to Binney and Tremaine) {\bf Al final estos numeros son
+    isodensidad o isopotencial}}
+\end{table*}
+
+To compare our results against observational values have we to
+translate first the isodensity into the corresponding isopotential
+rations, in which observational constraints are usually presented.
+For this purpose, we run a simple algorithm to find an
+approximation of the shape of the isopotential contour.
+
+First, we calculate the mean and standard deviation of the potential over a
+spherical shell of width equals to $10\%$ of the radius at which it is
+sampled. 
+Then, we calculate the inertia tensor of particles with potential
+within $1\sigma$ around the mean potential and calculate its triaxial
+characterization with the reduced inertia tensor. 
+We repeat the
+process of calculating the potential mean and standard deviation until
+convergence is achieved with tolerance of $10^{-4}$.
+
+{\bf Aqui hace falta una grafica comparando explicitamente los
+  valores para q y para s, esto para diferentes radios.
+  Otro punto importante es que se tiene q, pero como se
+  relaciona s?
+  Ademas hay que calcularlos para los radius aproximados que se
+  presentan en las tablas observacionales y en las de simulaciones.
+  10-20kpc se acerca a 1/8Rvir, 20-25 1/4Rvir, 60kpc aproximadamente 1/2Rvir
+}
+
+As a consistency check we compare the isopotential results with the analytic expectation of the
+$(1-q_{\phi})\approx \frac{1}{3}(1-q_{\rho})$
+\citep{Binney_and_Tremaine_2008}, taking the volume-enclosed axial
+ratios  as an approximation for the isodensity contour ratios
+$q_{\rho}$. 
+Although this analytic expression if meant to be used on the outer
+regions of logarithmic axisymmetric halos, it works well as a first
+approximation for nearly axisymmetric halos as those produced by our
+simulations 
+We find that the difference between the measured and the
+approximated isopotential axial ratios is not bigger than $quantity
+percent$ {\bf }.
+
+Little discussion: Are our results congruent with observations? at
+which radii, does the DM halo shape vary that much?. Which models are
+favored?
+
+We repeat this process for the different radii from table
 
@@
 \end{table}
-
-As a check of consistency, we compare our new isopotential shape
-results with the analytic expression of the
-$(1-q_{\phi})\frac{1}{3}(1-q_{\rho})$ \citep{Binney_and_Tremaine_2008}, taking the volume-enclosed axial ratios
-as an approximation for the isodensity contour ratios
-$q_{\rho}$. Although this analytic expression if meant to be used for
-logarithmic axisymmetric halos, it works well as a first approximation
-for nearly axisymmetric halos as those produced by our disced
-galaxies. We find that the difference between the real and the
-analytic isopotential axial ratios is not bigger than $quantity
-percent$. With this, we may now present on table
-\ref{tabe:isopotential} our observationally-comparable results for MHD
-halos at two important radii one corresponding to the approximate
-regimes where the MW DM halo is usually constrained.
-
-Little discussion: Are our results congruent with observations? at
-which radii, does the DM halo shape vary that much?. Which models are
-favored?
 

### 2019-03-05 Paper/paper.tex
edit

@@
 \citet{Bowden_et_al._2016}& 0.5-0.66 &0.5-0.66& 5kpc - 10 kpc& $90^{\circ}$&
-Weak constraint on prolate halo. SDSS stars dynamics.\\\hline
+Weak constraint on prolate halo. SDSS stars dynamics.\\
 
@@
 &${0.90}$&${0.80}$&$\gtrsim 10$kpc&$90^{\circ}$&
-Mid-axis orientation on the outside. \\\hline
+Mid-axis orientation on the outside. \\
 
@@
 $\lesssim 60$kpc&$90^{\circ}$&Mid-axis orientation. Sagittarius
-stream\\\hline
+stream\\
 
@@
 $20$kpc-$60$kpc$$&$90^{\circ}$&Mid-axis orientation, Sagittarius
-stream\\\hline
+stream\\
 
@@
 $20$kpc-$60$kpc$ $&$90^{\circ}$&
-Mid-axis orientation. Sagittarius stream\\\hline
+Mid-axis orientation. Sagittarius stream\\\hline \hline
+
+\citet{Chua_et_al._2018}&${0.88\pm0.10}$&${0.70\pm0.11}$&$0.15R_{200}$&
+& Illustris\\
+
+\citet{Bryan_et_al._2013}&$0.84-0.86$&$0.66-0.70$&$R_{200}$& & 
+For different cosmologies and feedback recipies. Calculated from a fit
+at $M_\odot=10^12$\\\hline
 
@@
 & $0.80$ &  $\simeq 8$kpc & $0^{\circ}$&Stellar dynamics and HI
-density. \\\hline
+density. \\
 
@@
 gas. \\ &${0.5}$&${0.5}$&$24$kpc&$0^{\circ}$&Monotonical
-change between radial regimes.\\\hline
+change between radial regimes.\\
 
 \citet{Loebman_et_al._2012}&${1.00}$&${0.47}$&$\sim
-20$kpc &$0^{\circ}$&Method: SDSS statistics\\\hline
+20$kpc &$0^{\circ}$&Method: SDSS statistics\\
 
 \cite{Johnston_et_al._2005}&${1}$&$0.83-0.92$&$\lesssim
-60$kpc&$0^{\circ}$&Method: Sagittarius stream\\\hline
+60$kpc&$0^{\circ}$&Method: Sagittarius stream\\
 
 \citet{Bovy_et_el._2016}&${0.95}$&${0.95}$&$\lesssim
-20$kpc&$90^{\circ}$ & Stellar streams\\\hline
+20$kpc&$90^{\circ}$ & Stellar streams\\
 
@@
 $20$kpc-$60$kpc$ $&$90^{\circ}$&
-Mid-axis orientation. Sagittarius stream\\\hline
+Mid-axis orientation. Sagittarius stream\\\hline\hline
 
@@
 \\ \hline \hline
-\citet{Chua_et_al._2018}&${0.88\pm0.10}$&${0.70\pm0.11}$&&&$0.15R_{200}$& Illustris\\\hline
-
-\citet{Bryan_et_al._2013}&$0.84-0.86$&$0.66-0.70$&&&$R_{200}$&
-For different cosmologies and feedback recipies. Calculated from a fit
-at $M_\odot=10^12$\\\hline
 

### 2019-03-05 Paper/paper.tex
edit

@@
 
-\section{Analysis}
+\section{Discussion}
+
+\subsection{What drives the rounding effect?}
+
+From our characterization of radial shapes it is clear that
+MHD halos are rounder than DM halos every sampled radii. 
+It is also noticeable that the rounding effect of baryons is stronger
+at the disk regime, where the DM halo is almost perfectly oblate. 
+Furthermore, MHD halos tend towards more oblate shapes (T < 0.5)
+despite DM halos tendency towards more prolate shapes (T>0.5). 
+This rounding effect can be explained by gravitational effect of the
+flattened axisymmetric galactic disk. 
+It also explanes the weakness of this affect around $\approx 100$kpc,
+where the disk potential is weaker compared to the DM halo potential.
+
+{\bf Hace falta una grafica de la distribucion cumulativa de
+  triaxialidad para (R\_vir y R\_vir/16 por separado), en cada panel se
+  com para MHD vs DM.}
+
+Following that linea reasoning, one would also expect that the rounding
+effect of baryons is related to some  galactic parameters such as its
+component masses and radii. 
+We look for these kind of correlations and to find that the strongest
+can be found for the stellar density.
+However, the correlation is relatively low ({\bf cuanto vale el
+  coeficiente de correlation}) most likely due to the different
+formation histories.
+In other words, the effect of the baryonic disk on the shape of the DM halo
+does not fully explain the deviation from oblateness of MHD halos at
+$r<10$kpc.
+
+Figure  \ref{fig:Star_Density_effect} shows the
+{\bf que es es lo que muestra esta grafica? falta las unidades de la
+  densidad. y el eje vertical que es? es un cambio absoluto? fraccional?}
+
+{\bf Finalmente cuales son las cantidades disponibles en el disco?
+  cuales son las que muestran una mayor correlacion? Haria falta un
+  plot con todas las correlaciones y la mencion de alguna prueba de
+  machine learning del fit lineal para ver cuales son los parametros
+  mas importantes.}
+
+\textbf{Actually we have not examined the relation of c/a in MHD halos
+  with some measure of c/a from the disk, that is something like
+  Zdisk/Rdisk. This actually would make more sense from a physical
+  point of view: effect of the potential. }
+
+\textit{ Talk about source of triaxiality at the inner parts of the
+  halos (bar?). This source of triaxiality at the inner parts explains
+  why the axial ratios are $\approx 0.95$ and not exactly $1$. We
+  should also discuss that the decrease in the axial ratios for bigger
+  radii may actually be bigger/steeper but it is dimmed by the
+  contribution of inner parts.}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{./pics/Delta asphericity Vs Star Density.png}
+  \caption{Difference in asphericities between MHD and DM shapes Vs
+    Star Density of the simulation. Unsure about this graphic. Take
+    delta asphericity as the strength of the rounding effect of
+    baryons.}  
+  \label{fig:Star_Density_effect}
+\end{figure}
 
 \subsection{Comparison against observational constraints}
-
-\begin{table*}
-\begin{tabular}{|l|cc|c|c|p{7cm}|}\hline
-Reference&$q_{\phi}$&$s_{\phi}$&$R$&$\theta$&
-Methodology\\ \hline \hline
-
-\citet{Bowden_et_al._2016}& 0.5-0.66 &0.5-0.66& 5kpc - 10 kpc& $90^{\circ}$&
-Weak constraint on prolate halo. SDSS stars dynamics.\\
-
-\multirow{2}{*}{\citet{Vera-Ciro_and_Helmi_2013}}&${1.00}$&${0.90}$&$\lesssim
-10$kpc&$0^{\circ}$ & Sagittarius stream \& LMC \\
-&${0.90}$&${0.80}$&$\gtrsim 10$kpc&$90^{\circ}$&
-Mid-axis orientation on the outside. \\
-
-\citet{Law_and_Majewski_2009}&${0.83}$&${0.67}$&
-$\lesssim 60$kpc&$90^{\circ}$&Mid-axis orientation. Sagittarius
-stream\\
-
-\citet{Law_and_Majewski_2010}&${0.99}$&${0.72}$&
-$20$kpc-$60$kpc$$&$90^{\circ}$&Mid-axis orientation, Sagittarius
-stream\\
-
-\citet{Deg_and_Widrow_2013} & $0.82$&$0.40$&
-$20$kpc-$60$kpc$ $&$90^{\circ}$&
-Mid-axis orientation. Sagittarius stream\\\hline \hline
-
-\citet{Chua_et_al._2018}&${0.88\pm0.10}$&${0.70\pm0.11}$&$0.15R_{200}$&
-& Illustris\\
-
-\citet{Bryan_et_al._2013}&$0.84-0.86$&$0.66-0.70$&$R_{200}$& & 
-For different cosmologies and feedback recipies. Calculated from a fit
-at $M_\odot=10^12$\\\hline
-
-\end{tabular}
-\caption{{\bf Cuales son las incertidumbres? Con respecto a que eje
-    esta medido theta?}}
-\end{table*}
-%\end{multicols}
 
@@
 \begin{table*}
-\begin{tabular}{|l|cc|cc|c|p{4cm}|}\hline
-Reference&$q_{\rho}$&$s_{\rho}$&$q_{\phi}$&$s_{\phi}$&$R$& Methodology
-\\ \hline \hline
+\begin{tabular}{|l|cc|c|c|p{7cm}|}\hline
+Reference&$q_{\phi}$&$s_{\phi}$&$R$&$\theta$&
+Methodology\\ \hline \hline
 
-\multirow{2}{*}{\citet{Abadi_et_al._2010}}&&&${0.98}$&${0.85}$&-&
-Almost independent of radius. No feedback: boundary case\\\hline 
+\citet{Bowden_et_al._2016}& 0.5-0.66 &0.5-0.66& 5kpc - 10 kpc& $90^{\circ}$&
+Weak constraint on prolate halo. SDSS stars dynamics.\\
+
+\multirow{2}{*}{\citet{Vera-Ciro_and_Helmi_2013}}&${1.00}$&${0.90}$&$\lesssim
+10$kpc&$0^{\circ}$ & Sagittarius stream \& LMC \\
+&${0.90}$&${0.80}$&$\gtrsim 10$kpc&$90^{\circ}$&
+Mid-axis orientation on the outside. \\
+
+\citet{Law_and_Majewski_2009}&${0.83}$&${0.67}$&
+$\lesssim 60$kpc&$90^{\circ}$&Mid-axis orientation. Sagittarius
+stream\\
+
+\citet{Law_and_Majewski_2010}&${0.99}$&${0.72}$&
+$20$kpc-$60$kpc$$&$90^{\circ}$&Mid-axis orientation, Sagittarius
+stream\\
+
+\citet{Deg_and_Widrow_2013} & $0.82$&$0.40$&
+$20$kpc $60$kpc$ $&$90^{\circ}$&
+Mid-axis orientation. Sagittarius stream\\\hline \hline
+
+\citet{Chua_et_al._2018}&${0.88\pm0.10}$&${0.70\pm0.11}$&$0.15R_{200}$&
+& Illustris\\
+
+\citet{Bryan_et_al._2013}&$0.84-0.86$&$0.66-0.70$&$R_{200}$& & 
+For different cosmologies and feedback recipies. Calculated from a fit
+at $M_\odot=10^12$\\\hline
+
 \end{tabular}
-\caption{(TODO: compute analogues in isopotential or isodensity
-  according to Binney and Tremaine) {\bf Al final estos numeros son
-    isodensidad o isopotencial}}
+\caption{{\bf Cuales son las incertidumbres? Con respecto a que eje
+    esta medido theta?}}
 \end{table*}
+%\end{multicols}
 
-To compare our results against observational values have we to
-translate first the isodensity into the corresponding isopotential
-rations, in which observational constraints are usually presented.
-For this purpose, we run a simple algorithm to find an
+Half of the observational constraints are computed in terms of
+isodensity contours, the other half in terms of isopotential contours.
+To compare our results against the second kind we must either
+translate the isodensity results or recompute in terms of isopotential
+regions.
+For this purpose, we run a simple iterative algorithm to find an
 approximation of the shape of the isopotential contour.
@@
 
+In Figure \ref{fig:density_potential} we compare the two approaches to
+measure the axial rations and plot the analytic expectation for $q$, 
+$(1-q_{\phi})\approx \frac{1}{3}(1-q_{\rho})$
+\citep{Binney_and_Tremaine_2008}, taking the volume-enclosed axial
+ratios  as an approximation for the isodensity contour ratios
+$q_{\rho}$. 
+This plot is computed at four different radii.
+
+Although the analytic expression is meant to be used on the outer
+regions of logarithmic axisymmetric halos, it works well as a first
+approximation for nearly axisymmetric halos as those produced by our
+simulations 
+We find that the difference between the measured and the
+approximated isopotential axial ratios is not bigger than $quantity
+percent$ {\bf }.
+
 {\bf Aqui hace falta una grafica comparando explicitamente los
@@
 }
-
-As a consistency check we compare the isopotential results with the analytic expectation of the
-$(1-q_{\phi})\approx \frac{1}{3}(1-q_{\rho})$
-\citep{Binney_and_Tremaine_2008}, taking the volume-enclosed axial
-ratios  as an approximation for the isodensity contour ratios
-$q_{\rho}$. 
-Although this analytic expression if meant to be used on the outer
-regions of logarithmic axisymmetric halos, it works well as a first
-approximation for nearly axisymmetric halos as those produced by our
-simulations 
-We find that the difference between the measured and the
-approximated isopotential axial ratios is not bigger than $quantity
-percent$ {\bf }.
-
-Little discussion: Are our results congruent with observations? at
-which radii, does the DM halo shape vary that much?. Which models are
-favored?
-
-We repeat this process for the different radii from table
 
@@
 
-\subsection{The rounding effect of baryons}
-
-From the previous characterization of radial shapes it is clear that
-MHD halos are rounder than DM halos (i.e. axial ratios are bigger) at
-every sampled radii. This can be compared on tables \ref{tabe:DM
-  table} and \ref{tabe:MHD table} or at the representative example on
-figure \ref{fig:DM_MHD}. From there, it is also noticeable that the
-rounding effect of baryons is stronger at the disk regime, where the
-DM halo is almost perfectly oblate. Furthermore, MHD halos tend
-towards more oblate shapes (T < 0.5) despite DM halos tendency towards
-more prolate shapes (T>0.5).
-
-This rounding effect is expected from the gravitational effect of the
-flattened axisymmetric galactic disk. It is also reasonable that this
-effect is not as strong at $\approx 100$kpc, where the disk potential
-is dimmer compared to the DM halo potential. Keeping this in mind, one
-would expect that the rounding effect of baryons is related to some
-galactic parameters such as its component masses and radii. However,
-even for the parameter of highest correlation with this rounding
-effect (the baryonic fraction), the relation is not clear nor
-conclusive due to the dispersion from galaxy peculiarities. In figure
-\ref{fig:Star_Density_effect} we plot the ratios $c/a$ compared to the
-baryonic fraction of each galaxy. Although some linear tendency is
-suggested qualitatively, the dispersion of the sample is very high to
-obtain some conclusive relation. This is an evidence that
-adiabatic-contraction models are not realistic as they may neglect
-some effects of the galaxy evolution in the whole cosmological
-context.
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{./pics/Delta asphericity Vs Star Density.png}
-  \caption{Difference in asphericities between MHD and DM shapes Vs
-    Star Density of the simulation. Unsure about this graphic. Take
-    delta asphericity as the strength of the rounding effect of
-    baryons.}  
-  \label{fig:Star_Density_effect}
-\end{figure}
-
-\textbf{Actually we have not examined the relation of c/a in MHD halos
-  with some measure of c/a from the disk, that is something like
-  Zdisk/Rdisk. This actually would make more sense from a physical
-  point of view: effect of the potential.}
-
-Although the effect of the baryonic disk on the shape of the DM halo
-is a reasonable explanation for the rounding effect, it does not
-actually explain the deviation from oblateness of MHD halos at
-$r<10$kpc. In other words, if the disk is perfectly axisymmetric,
-there must be some source of triaxiality at $r<10$kpc to explain the
-low axial ratios.
-
-\textit{ Talk about source of triaxiality at the inner parts of the
-  halos (bar?). This source of triaxiality at the inner parts explains
-  why the axial ratios are $\approx 0.95$ and not exactly $1$. We
-  should also discuss that the decrease in the axial ratios for bigger
-  radii may actually be bigger/steeper but it is dimmed by the
-  contribution of inner parts.} 
-%
-%\begin{figure}
-%  \centering
-%  \subfloat[Level4 MHD Vs DM at inner regions]{\includegraphics[width=0.5\columnwidth]{./pics/Triaxial_Plane/Triaxiality_Inner_lvl4.png}}
-%  \hfill
-%  \subfloat[Level4 MHD Vs DM at outer regions]{\includegraphics[width=0.5\columnwidth]{./pics/Triaxial_Plane/Triaxiality_Outter_lvl4.png}}
-%  \hfill
-%  \caption{Axial ratios as shown on $c/a$ Vs $b/a$.
-Each dot represents a halo shape at some radius.
-Some observational constraints are plotted alongside our results.
-Here, dots are clustered, proving the general tendence of halos to get rounder on the outer parts.(Optimize space.
-caption replaces title.
-Present constraints representation of density)}
-%  \label{fig:Triaxiality_Inner_Outer}
-%\end{figure}
-
 \section{Conclusions}
 
-\section{Discussion}
-
 \section*{Acknowledgements}
-This project has received funding from the European Union’s Horizon
+This project has received funding from the European Union's Horizon
 2020 Research and Innovation Programme under the Marie
